---
title: "SiMBA Modelling"
output: html_notebook
---

# Libraries

```{r}
library(tidyverse)
library(kinfitr)
library(bloodstream)
library(brms)
library(rstan)
library(furrr)
library(ggcorrplot2)
#library(relfeas)
library(cmdstanr)
library(loo)
```

# Data

For the Yale data
```{r}
simba_modeldata <- readRDS("../DerivedData/Yale_simba_modeldata.rds") %>% 
  rename(pet = IDPET,
         genotype = Genotype,
         region = Region) %>% 
  select(-input) %>% 
  mutate(sub= str_extract(pet, "^[^_]+")) %>% 
  ungroup() %>% 
  #mutate(genotype = ifelse(is.na(genotype), "NA",genotype)) %>% 
  filter(!is.na(genotype)) %>% 
  mutate(region = factor(region) %>% 
           forcats::fct_relevel("Frontal"))
```


# STAN Models


## 3TC5K
* threetc5kND_log_stan : 
* threetc5kND_log_stan_BPp : 
* threetc5kND_log_stan_mix : Mixture model variant
* threetc5kND_log_stan_mix_BPp
* threetc5kND_log_stan_mix_BPp_k2 : with Vnddiff

for S and P the same
all included into one Stan block that i do not get issues with pointers in the wrong direction

```{r, fig.height=10, fig.width=6}
three_compartment_5k_fengconv_stan <- "

real Integral_Feng_3TC5K(real time, real A, real B, real C, 
                       real alpha, real beta, real gamma, 
                       real Th1, real Th2, real Ph1, real Ph2, real Ph3) {
     
    real integ;
    
    integ = (B*(1 - exp(-(alpha*time)))*Ph3)/alpha^2 + (C*(1 - exp(-(alpha*time)))*Ph3)/alpha^2 + (A*(-1 + exp(-(alpha*time)))*Ph3)/alpha^3 + 
  (B*(-1 + exp(-(beta*time)))*Ph3)/beta^2 + (C*(-1 + exp(-(gamma*time)))*Ph3)/gamma^2 + (A*Ph3*time)/alpha^2 - (B*Ph3*time)/alpha + (B*Ph3*time)/beta - 
  (C*Ph3*time)/alpha + (C*Ph3*time)/gamma - (A*Ph3*(1 - (1 + alpha*time)/exp(alpha*time)))/alpha^3 - (A*(1 - exp(-(alpha*time)))*Ph1)/(alpha*(alpha-Th1)^2) - 
  (A*Ph1*(1 - (1 + alpha*time)/exp(alpha*time)))/(alpha*(alpha-Th1)^2) + (B*(1 - exp(-(alpha*time)))*Ph1)/(alpha*(alpha - Th1)) + 
  (C*(1 - exp(-(alpha*time)))*Ph1)/(alpha*(alpha - Th1)) + (A*(1 - exp(-(time*Th1)))*Ph1)/((alpha-Th1)^2*Th1) - 
  (B*(1 - exp(-(time*Th1)))*Ph1)/((alpha - Th1)*Th1) - (C*(1 - exp(-(time*Th1)))*Ph1)/((alpha - Th1)*Th1) + (B*(1 - exp(-(time*Th1)))*Ph1)/((beta - Th1)*Th1) + 
  (C*(1 - exp(-(time*Th1)))*Ph1)/((gamma - Th1)*Th1) + (A*Ph1*(1 - (1 + alpha*time)/exp(alpha*time))*Th1)/(alpha^2*(alpha-Th1)^2) + 
  (B*(1 - exp(-(beta*time)))*Ph1)/(beta*(-beta + Th1)) + (C*(1 - exp(-(gamma*time)))*Ph1)/(gamma*(-gamma + Th1)) - 
  (A*(1 - exp(-(alpha*time)))*Ph2)/(alpha*(alpha-Th2)^2) - (A*Ph2*(1 - (1 + alpha*time)/exp(alpha*time)))/(alpha*(alpha-Th2)^2) + 
  (B*(1 - exp(-(alpha*time)))*Ph2)/(alpha*(alpha - Th2)) + (C*(1 - exp(-(alpha*time)))*Ph2)/(alpha*(alpha - Th2)) + 
  (A*(1 - exp(-(time*Th2)))*Ph2)/((alpha-Th2)^2*Th2) - (B*(1 - exp(-(time*Th2)))*Ph2)/((alpha - Th2)*Th2) - (C*(1 - exp(-(time*Th2)))*Ph2)/((alpha - Th2)*Th2) + 
  (B*(1 - exp(-(time*Th2)))*Ph2)/((beta - Th2)*Th2) + (C*(1 - exp(-(time*Th2)))*Ph2)/((gamma - Th2)*Th2) + 
  (A*Ph2*(1 - (1 + alpha*time)/exp(alpha*time))*Th2)/(alpha^2*(alpha-Th2)^2) + (B*(1 - exp(-(beta*time)))*Ph2)/(beta*(-beta + Th2)) + 
  (C*(1 - exp(-(gamma*time)))*Ph2)/(gamma*(-gamma + Th2));
   
   return(integ);
                       
}


real threetc5kND_log_stan_BPp(real logK1, real logVnd, real logBPp, 
                    real logk4, real logk5, real logvB, real time,
                    real t0, 
                    real A, real B, real C, 
                    real alpha, real beta, real gamma,
                    real ti, real bloodval) {

    real K1;
    real k2;
    real k3;
    real k4;
    real k5;
    real KI;
    real Vnd;
    real BPnd;
    real BPp;
    real vB;
    
    real Th1;
    real Th2;
    real Ph1;
    real Ph2;
    real Ph3;
    
    real tcorr;
    
    real pred;
    

    
    K1 = exp(logK1);
    Vnd = exp(logVnd);
    BPp = exp(logBPp);
    k4 = exp(logk4);
    vB = exp(logvB);
    k5 = exp(logk5);
    
    k2 = K1 / Vnd - k5;
    k3 = (k4 * (k2 + k5) * BPp)/K1;
    KI = K1 * k5 / (k2 + k5);

    Th1 = 0.5 * (k2 + k3 + k4 + k5 - sqrt((k2 + k3 + k4 + k5)^2 - 4 * k4 * (k2+k5)));
    Th2 = 0.5 * (k2 + k3 + k4 + k5 + sqrt((k2 + k3 + k4 + k5)^2 - 4 * k4 * (k2+k5)));

    Ph1 = (K1 * (k3 + k4 + k5 - Th1) - KI * Th2)/(Th2 - Th1);
    Ph2 = (K1 * (Th2 - k3 - k4 - k5) + KI * Th1)/(Th2 - Th1);
    Ph3 = KI;
    
    tcorr = time - t0;
  
  pred =  // 2TC contribution
          (1-vB) * (
            (tcorr > 0) * (             // Before t0 equal to 0
              
              // Before t0+ti
              (tcorr < ti)*(1/ti)*(     
                Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma, 
                                 Th1, Th2, Ph1, Ph2, Ph3)
              ) +
                
              // After t0+ti 
              (tcorr >= ti)*(1/ti)* (   
                Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma, 
                                 Th1, Th2, Ph1, Ph2, Ph3) -
                  Integral_Feng_3TC5K(tcorr - ti, A, B, C, alpha, beta, gamma, 
                                 Th1, Th2, Ph1, Ph2, Ph3)
              )
            )
          ) +
          // Blood contribution
          vB*bloodval;
       
  return(pred);
}

// S

real threetc5kS_log_stan_BPp(real logK1, real logVnd, real logBPp, 
                    real logk4, real logk5, real logvB, real time,
                    real t0, 
                    real A, real B, real C, 
                    real alpha, real beta, real gamma,
                    real ti, real bloodval) {

    real K1;
    real k2;
    real k3;
    real k4;
    real k5;
    real KI;
    real Vnd;
    real BPnd;
    real BPp;
    real vB;
    
    real Th1;
    real Th2;
    real Ph1;
    real Ph2;
    real Ph3;
    
    real tcorr;
    
    real pred;
    

    
    K1 = exp(logK1);
    Vnd = exp(logVnd);
    BPp = exp(logBPp);
    k4 = exp(logk4);
    vB = exp(logvB);
    k5 = exp(logk5);
    
    k2 = (K1 - k5 * BPp)/Vnd;
    k3 = BPp * (k4 + k5)/Vnd;
    KI = K1 * k3 * k5 / (k2 * k4 + k2 * k5 + k3 * k5);
  
    Th1 = 0.5 * (k2 + k3 + k4 + k5 + sqrt((k2 + k3 + k4 + k5)^2 - 4 * (k2 * k4 + k2 * k5 + k3 * k5)));
    Th2 = 0.5 * (k2 + k3 + k4 + k5 - sqrt((k2 + k3 + k4 + k5)^2 - 4 * (k2 * k4 + k2 * k5 + k3 * k5)));

    Ph1 = (K1 * (k3 + k4 + k5 - Th1) - KI * Th2)/(Th2 - Th1);
    Ph2 = (K1 * (Th2 - k3 - k4 - k5) + KI * Th1)/(Th2 - Th1);
    Ph3 = KI;
    
    tcorr = time - t0;
  
  pred =  // 2TC contribution
          (1-vB) * (
            (tcorr > 0) * (             // Before t0 equal to 0
              
              // Before t0+ti
              (tcorr < ti)*(1/ti)*(     
                Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma, 
                                 Th1, Th2, Ph1, Ph2, Ph3)
              ) +
                
              // After t0+ti 
              (tcorr >= ti)*(1/ti)* (   
                Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma, 
                                 Th1, Th2, Ph1, Ph2, Ph3) -
                  Integral_Feng_3TC5K(tcorr - ti, A, B, C, alpha, beta, gamma, 
                                 Th1, Th2, Ph1, Ph2, Ph3)
              )
            )
          ) +
          // Blood contribution
          vB*bloodval;
       
  return(pred);
}


// P

real threetc5kP_log_stan_BPp(real logK1, real logVnd, real logBPp, 
                    real logk4, real logk5, real logvB, real time,
                    real t0, 
                    real A, real B, real C, 
                    real alpha, real beta, real gamma,
                    real ti, real bloodval) {

    real K1;
    real k2;
    real k3;
    real k4;
    real k5;
    real KI;
    real Vnd;
    real BPnd;
    real BPp;
    real vB;
    
    real Th1;
    real Th2;
    real Ph1;
    real Ph2;
    real Ph3;
    
    real tcorr;
    
    real pred;
    

    
    K1 = exp(logK1);
    Vnd = exp(logVnd);
    BPp = exp(logBPp);
    k4 = exp(logk4);
    vB = exp(logvB);
    k5 = exp(logk5);
    
    k2 = K1 / Vnd;
    k3 = (k4 * BPp)/Vnd;
    KI = k5;
  
    Th1 = 0.5 * (k2 + k3 + k4 - sqrt((k2 + k3 + k4)^2 - 4 * k2 * k4));
    Th2 = 0.5 * (k2 + k3 + k4 + sqrt((k2 + k3 + k4)^2 - 4 * k2 * k4));

    Ph1 = (K1 * (k3 + k4 - Th1))/(Th2 - Th1);
    Ph2 = (K1 * (Th2 - k3 - k4))/(Th2 - Th1);
    Ph3 = KI;
    
    tcorr = time - t0;
  
  pred =  // 2TC contribution
          (1-vB) * (
            (tcorr > 0) * (             // Before t0 equal to 0
              
              // Before t0+ti
              (tcorr < ti)*(1/ti)*(     
                Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma, 
                                 Th1, Th2, Ph1, Ph2, Ph3)
              ) +
                
              // After t0+ti 
              (tcorr >= ti)*(1/ti)* (   
                Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma, 
                                 Th1, Th2, Ph1, Ph2, Ph3) -
                  Integral_Feng_3TC5K(tcorr - ti, A, B, C, alpha, beta, gamma, 
                                 Th1, Th2, Ph1, Ph2, Ph3)
              )
            )
          ) +
          // Blood contribution
          vB*bloodval;
       
  return(pred);
}
                    
//
//
//
//
//
//
//
//
//
//
//
//
//
// mixture models
//
//
//
//
//
//
//
//
//
//
//
//
//
//
real threetc5kND_log_stan_mix_BPp(real logK1, real logVnd, real logBPp, real logk4,
                    real logk5, real logvB,
                    real logBPpdiff, real logk4diff, real logk5diff,
                    real prophigh, real proplow,
                    real time,
                    real t0,
                    real A, real B, real C,
                    real alpha, real beta, real gamma,
                    real ti, real bloodval) {

    real K1;
    real k2;
    real k3;
    real k4;
    real k5;
    real KI;
    real Vnd;
    real BPp;
    real vB;

    real Th1;
    real Th2;
    real Ph1;
    real Ph2;
    real Ph3;
    
    real Th1low;
    real Th2low;
    real Ph1low;
    real Ph2low;
    real Ph3low;

    real tcorr;

    real predhigh;
    real predlow;
    real pred;
    
    real BPplow;
    real k4low;
    real k3low;
    real k5low;
    real KIlow;
    real k5mean;
    

    K1 = exp(logK1);
    Vnd = exp(logVnd);
    vB = exp(logvB);

    // High
    BPp = exp(logBPp);
    k4 = exp(logk4);
    k5 = exp(logk5);
    
    // Low
    BPplow = exp(logBPp + logBPpdiff);
    k4low = exp(logk4 + logk4diff);
    k5low = exp(logk5 + logk5diff);
    
    // Assumed to be indepenpendent of genotypes
    // note for myself: same no mather if mean(k5) or mean(k2)
    k5mean = (k5 +k5low)/2;
    k2 = K1 / Vnd - k5mean;

    // High
    k3 = (k4 * (k2 + k5) * BPp)/K1;
    KI = K1 * k5 / (k2 + k5);

    Th1 = 0.5 * (k2 + k3 + k4 + k5 - sqrt((k2 + k3 + k4 + k5)^2 - 4 * k4 * (k2+k5)));
    Th2 = 0.5 * (k2 + k3 + k4 + k5 + sqrt((k2 + k3 + k4 + k5)^2 - 4 * k4 * (k2+k5)));

    Ph1 = (K1 * (k3 + k4 + k5 - Th1) - KI * Th2)/(Th2 - Th1);
    Ph2 = (K1 * (Th2 - k3 - k4 - k5) + KI * Th1)/(Th2 - Th1);
    Ph3 = KI;
    
    
    // Low
    k3low = (k4low * (k2 + k5low) * BPplow)/K1;
    KIlow = K1 * k5low / (k2 + k5low);
    
    Th1low = 0.5 * (k2 + k3low + k4low + k5low - sqrt((k2 + k3low + k4low + k5low)^2 - 4 * k4low * (k2 + k5low)));
    Th2low = 0.5 * (k2 + k3low + k4low + k5low + sqrt((k2 + k3low + k4low + k5low)^2 - 4 * k4low * (k2 + k5low)));

    Ph1low = (K1 * (k3low + k4low + k5low - Th1low) - KIlow * Th2low)/(Th2low - Th1low);
    Ph2low = (K1 * (Th2low - k3low - k4low - k5low) + KIlow * Th1low)/(Th2low - Th1low);
    Ph3low = KIlow;
    

    tcorr = time - t0;

  predhigh =  
  (1-vB) * (
    (tcorr > 0) * (             // Before t0 equal to 0

      // 2TC off CND
      
        // Before t0+ti
        (tcorr < ti)*(1/ti)*(
          Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma,
                           Th1, Th2, Ph1, Ph2,Ph3)
        ) +

        // After t0+ti
        (tcorr >= ti)*(1/ti)* (
          Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma,
                           Th1, Th2, Ph1, Ph2, Ph3) -
            Integral_Feng_3TC5K(tcorr - ti, A, B, C, alpha, beta, gamma,
                           Th1, Th2, Ph1, Ph2, Ph3)
        )
      ) 
      
  ) +
  // Blood contribution
  vB *  bloodval;
  
  predlow =  
  (1-vB) * (
    (tcorr > 0) * (             // Before t0 equal to 0

      // 2TC
        // Before t0+ti
        (tcorr < ti)*(1/ti)*(
          Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma,
                           Th1low, Th2low, Ph1low, Ph2low, Ph3low)
        ) +

        // After t0+ti
        (tcorr >= ti)*(1/ti)* (
          Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma,
                           Th1low, Th2low, Ph1low, Ph2low, Ph3low) -
            Integral_Feng_3TC5K(tcorr - ti, A, B, C, alpha, beta, gamma,
                           Th1low, Th2low, Ph1low, Ph2low, Ph3low)
        )
      )
  ) +
  // Blood contribution
  vB *  bloodval;

  pred = ( prophigh * predhigh ) + ( proplow * predlow );

  return(pred);
}
                    
real threetc5kS_log_stan_mix_BPp(real logK1, real logVnd, real logBPp, real logk4,
                    real logk5, real logvB,
                    real logBPpdiff, real logk4diff, real logk5diff,
                    real prophigh, real proplow,
                    real time,
                    real t0,
                    real A, real B, real C,
                    real alpha, real beta, real gamma,
                    real ti, real bloodval) {

    real K1;
    real k2;
    real k3;
    real k4;
    real k5;
    real KI;
    real Vnd;
    real BPp;
    real vB;

    real Th1;
    real Th2;
    real Ph1;
    real Ph2;
    real Ph3;
    
    real Th1low;
    real Th2low;
    real Ph1low;
    real Ph2low;
    real Ph3low;

    real tcorr;

    real predhigh;
    real predlow;
    real pred;
    
    real BPplow;
    real k4low;
    real k3low;
    real k5low;
    real KIlow;
    
    real k5mean;
    real BPpmean;
    

    K1 = exp(logK1);
    Vnd = exp(logVnd);
    vB = exp(logvB);

    // High
    BPp = exp(logBPp);
    k4 = exp(logk4);
    k5 = exp(logk5);
    
    // Low
    BPplow = exp(logBPp + logBPpdiff);
    k4low = exp(logk4 + logk4diff);
    k5low = exp(logk5 + logk5diff);
    
    // Assumed to be indepenpendent of genotypes
    // note for myself: same no mather if mean(k5) or mean(k2)
    k5mean = (k5 + k5low)/2;
    BPpmean = (BPp + BPplow)/2;

    k2 = (K1 - k5mean * BPpmean)/Vnd;

    
    // High

    k3 = BPp * (k4 + k5)/Vnd;
    KI = K1 * k3 * k5 / (k2 * k4 + k2 * k5 + k3 * k5);
  
    Th1 = 0.5 * (k2 + k3 + k4 + k5 + sqrt((k2 + k3 + k4 + k5)^2 - 4 * (k2 * k4 + k2 * k5 + k3 * k5)));
    Th2 = 0.5 * (k2 + k3 + k4 + k5 - sqrt((k2 + k3 + k4 + k5)^2 - 4 * (k2 * k4 + k2 * k5 + k3 * k5)));

    Ph1 = (K1 * (k3 + k4 + k5 - Th1) - KI * Th2)/(Th2 - Th1);
    Ph2 = (K1 * (Th2 - k3 - k4 - k5) + KI * Th1)/(Th2 - Th1);
    Ph3 = KI;
    
    
    // Low
    
    k3low = BPplow * (k4low + k5low)/Vnd;
    KIlow = K1 * k3low * k5low / (k2 * k4low + k2 * k5low + k3low * k5low);
    
    Th1low = 0.5 * (k2 + k3low + k4low + k5low + sqrt((k2 + k3low + k4low + k5low)^2 - 4 * (k2 * k4low + k2 * k5low + k3low * k5low)));
    Th2low = 0.5 * (k2 + k3low + k4low + k5low - sqrt((k2 + k3low + k4low + k5low)^2 - 4 * (k2 * k4low + k2 * k5low + k3low * k5low)));

    Ph1low = (K1 * (k3low + k4low + k5low - Th1low) - KIlow * Th2low)/(Th2low - Th1low);
    Ph2low = (K1 * (Th2low - k3low - k4low - k5low) + KIlow * Th1low)/(Th2low - Th1low);
    Ph3low = KIlow;

    

    tcorr = time - t0;

  predhigh =  
  (1-vB) * (
    (tcorr > 0) * (             // Before t0 equal to 0

      // 2TC off CND
      
        // Before t0+ti
        (tcorr < ti)*(1/ti)*(
          Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma,
                           Th1, Th2, Ph1, Ph2,Ph3)
        ) +

        // After t0+ti
        (tcorr >= ti)*(1/ti)* (
          Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma,
                           Th1, Th2, Ph1, Ph2, Ph3) -
            Integral_Feng_3TC5K(tcorr - ti, A, B, C, alpha, beta, gamma,
                           Th1, Th2, Ph1, Ph2, Ph3)
        )
      ) 
      
  ) +
  // Blood contribution
  vB *  bloodval;
  
  predlow =  
  (1-vB) * (
    (tcorr > 0) * (             // Before t0 equal to 0

      // 2TC
        // Before t0+ti
        (tcorr < ti)*(1/ti)*(
          Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma,
                           Th1low, Th2low, Ph1low, Ph2low, Ph3low)
        ) +

        // After t0+ti
        (tcorr >= ti)*(1/ti)* (
          Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma,
                           Th1low, Th2low, Ph1low, Ph2low, Ph3low) -
            Integral_Feng_3TC5K(tcorr - ti, A, B, C, alpha, beta, gamma,
                           Th1low, Th2low, Ph1low, Ph2low, Ph3low)
        )
      )
  ) +
  // Blood contribution
  vB *  bloodval;

  pred = ( prophigh * predhigh ) + ( proplow * predlow );

  return(pred);
}

real threetc5kP_log_stan_mix_BPp(real logK1, real logVnd, real logBPp, real logk4,
                    real logk5, real logvB,
                    real logBPpdiff, real logk4diff, real logk5diff,
                    real prophigh, real proplow,
                    real time,
                    real t0,
                    real A, real B, real C,
                    real alpha, real beta, real gamma,
                    real ti, real bloodval) {

    real K1;
    real k2;
    real k3;
    real k4;
    real k5;
    real KI;
    real Vnd;
    real BPp;
    real vB;

    real Th1;
    real Th2;
    real Ph1;
    real Ph2;
    real Ph3;
    
    real Th1low;
    real Th2low;
    real Ph1low;
    real Ph2low;
    real Ph3low;

    real tcorr;

    real predhigh;
    real predlow;
    real pred;
    
    real BPplow;
    real k4low;
    real k3low;
    real k5low;
    real KIlow;
    

    K1 = exp(logK1);
    Vnd = exp(logVnd);
    vB = exp(logvB);

    // High
    BPp = exp(logBPp);
    k4 = exp(logk4);
    k5 = exp(logk5);


    k2 = K1 / Vnd;
    k3 = (k4 * BPp)/Vnd;
    KI = k5;
  
    Th1 = 0.5 * (k2 + k3 + k4 - sqrt((k2 + k3 + k4)^2 - 4 * k2 * k4));
    Th2 = 0.5 * (k2 + k3 + k4 + sqrt((k2 + k3 + k4)^2 - 4 * k2 * k4));

    Ph1 = (K1 * (k3 + k4 - Th1))/(Th2 - Th1);
    Ph2 = (K1 * (Th2 - k3 - k4))/(Th2 - Th1);
    Ph3 = KI;
    
    
    // Low
    BPplow = exp(logBPp + logBPpdiff);
    k4low = exp(logk4 + logk4diff);
    k5low = exp(logk5 + logk5diff);
    
    k3low = (k4low * BPplow)/Vnd;
    KIlow = k5low;
    
    Th1low = 0.5 * (k2 + k3low + k4low - sqrt((k2 + k3low + k4low)^2 - 4 * k4low * k2));
    Th2low = 0.5 * (k2 + k3low + k4low + sqrt((k2 + k3low + k4low)^2 - 4 * k4low * k2));

    Ph1low = (K1 * (k3low + k4low - Th1low))/(Th2low - Th1low);
    Ph2low = (K1 * (Th2low - k3low - k4low))/(Th2low - Th1low);
    Ph3low = KIlow;

    

    tcorr = time - t0;

  predhigh =  
  (1-vB) * (
    (tcorr > 0) * (             // Before t0 equal to 0

      // 2TC off CND
      
        // Before t0+ti
        (tcorr < ti)*(1/ti)*(
          Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma,
                           Th1, Th2, Ph1, Ph2,Ph3)
        ) +

        // After t0+ti
        (tcorr >= ti)*(1/ti)* (
          Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma,
                           Th1, Th2, Ph1, Ph2, Ph3) -
            Integral_Feng_3TC5K(tcorr - ti, A, B, C, alpha, beta, gamma,
                           Th1, Th2, Ph1, Ph2, Ph3)
        )
      ) 
      
  ) +
  // Blood contribution
  vB *  bloodval;
  
  predlow =  
  (1-vB) * (
    (tcorr > 0) * (             // Before t0 equal to 0

      // 2TC
        // Before t0+ti
        (tcorr < ti)*(1/ti)*(
          Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma,
                           Th1low, Th2low, Ph1low, Ph2low, Ph3low)
        ) +

        // After t0+ti
        (tcorr >= ti)*(1/ti)* (
          Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma,
                           Th1low, Th2low, Ph1low, Ph2low, Ph3low) -
            Integral_Feng_3TC5K(tcorr - ti, A, B, C, alpha, beta, gamma,
                           Th1low, Th2low, Ph1low, Ph2low, Ph3low)
        )
      )
  ) +
  // Blood contribution
  vB *  bloodval;

  pred = ( prophigh * predhigh ) + ( proplow * predlow );

  return(pred);
}

real threetc5kND_log_stan_mix_BPp_k2(real logK1, real logVnd, real logBPp, real logk4,
                    real logk5, real logvB,
                    real logBPpdiff, real logk4diff, real logk5diff, real logVnddiff,
                    real prophigh, real proplow,
                    real time,
                    real t0,
                    real A, real B, real C,
                    real alpha, real beta, real gamma,
                    real ti, real bloodval) {

    real K1;
    real k2;
    real k3;
    real k4;
    real k5;
    real KI;
    real Vnd;
    real BPp;
    real vB;

    real Th1;
    real Th2;
    real Ph1;
    real Ph2;
    real Ph3;
    
    real Th1low;
    real Th2low;
    real Ph1low;
    real Ph2low;
    real Ph3low;

    real tcorr;

    real predhigh;
    real predlow;
    real pred;
    
    real BPplow;
    real k4low;
    real k3low;
    real k5low;
    real KIlow;
    real k5mean;
    real Vndlow;
    real k2low;
    

    K1 = exp(logK1);
    vB = exp(logvB);

    // High
    BPp = exp(logBPp);
    k4 = exp(logk4);
    k5 = exp(logk5);
    Vnd = exp(logVnd);
    
    // Low
    BPplow = exp(logBPp + logBPpdiff);
    k4low = exp(logk4 + logk4diff);
    k5low = exp(logk5 + logk5diff);
    Vndlow = exp(logVnd + logVnddiff);
    
    // Assumed to be indepenpendent of genotypes
    // note for myself: same no mather if mean(k5) or mean(k2)
    // k5mean = (k5 +k5low)/2;
    // k2 = K1 / Vnd - k5mean;

    // High
    k2 = K1 / Vnd - k5;
    k3 = (k4 * (k2 + k5) * BPp)/K1;
    KI = K1 * k5 / (k2 + k5);

    Th1 = 0.5 * (k2 + k3 + k4 + k5 - sqrt((k2 + k3 + k4 + k5)^2 - 4 * k4 * (k2+k5)));
    Th2 = 0.5 * (k2 + k3 + k4 + k5 + sqrt((k2 + k3 + k4 + k5)^2 - 4 * k4 * (k2+k5)));

    Ph1 = (K1 * (k3 + k4 + k5 - Th1) - KI * Th2)/(Th2 - Th1);
    Ph2 = (K1 * (Th2 - k3 - k4 - k5) + KI * Th1)/(Th2 - Th1);
    Ph3 = KI;
    
    
    // Low
    k2low = K1 / Vndlow - k5low;
    k3low = (k4low * (k2low + k5low) * BPplow)/K1;
    KIlow = K1 * k5low / (k2low + k5low);
    
    Th1low = 0.5 * (k2low + k3low + k4low + k5low - sqrt((k2low + k3low + k4low + k5low)^2 - 4 * k4low * (k2low + k5low)));
    Th2low = 0.5 * (k2low + k3low + k4low + k5low + sqrt((k2low + k3low + k4low + k5low)^2 - 4 * k4low * (k2low + k5low)));

    Ph1low = (K1 * (k3low + k4low + k5low - Th1low) - KIlow * Th2low)/(Th2low - Th1low);
    Ph2low = (K1 * (Th2low - k3low - k4low - k5low) + KIlow * Th1low)/(Th2low - Th1low);
    Ph3low = KIlow;
    

    tcorr = time - t0;

  predhigh =  
  (1-vB) * (
    (tcorr > 0) * (             // Before t0 equal to 0

      // 2TC off CND
      
        // Before t0+ti
        (tcorr < ti)*(1/ti)*(
          Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma,
                           Th1, Th2, Ph1, Ph2,Ph3)
        ) +

        // After t0+ti
        (tcorr >= ti)*(1/ti)* (
          Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma,
                           Th1, Th2, Ph1, Ph2, Ph3) -
            Integral_Feng_3TC5K(tcorr - ti, A, B, C, alpha, beta, gamma,
                           Th1, Th2, Ph1, Ph2, Ph3)
        )
      ) 
      
  ) +
  // Blood contribution
  vB *  bloodval;
  
  predlow =  
  (1-vB) * (
    (tcorr > 0) * (             // Before t0 equal to 0

      // 2TC
        // Before t0+ti
        (tcorr < ti)*(1/ti)*(
          Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma,
                           Th1low, Th2low, Ph1low, Ph2low, Ph3low)
        ) +

        // After t0+ti
        (tcorr >= ti)*(1/ti)* (
          Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma,
                           Th1low, Th2low, Ph1low, Ph2low, Ph3low) -
            Integral_Feng_3TC5K(tcorr - ti, A, B, C, alpha, beta, gamma,
                           Th1low, Th2low, Ph1low, Ph2low, Ph3low)
        )
      )
  ) +
  // Blood contribution
  vB *  bloodval;

  pred = ( prophigh * predhigh ) + ( proplow * predlow );

  return(pred);
}
                    
real threetc5kS_log_stan_mix_BPp_k2(real logK1, real logVnd, real logBPp, real logk4,
                    real logk5, real logvB,
                    real logBPpdiff, real logk4diff, real logk5diff, real logVnddiff,
                    real prophigh, real proplow,
                    real time,
                    real t0,
                    real A, real B, real C,
                    real alpha, real beta, real gamma,
                    real ti, real bloodval) {

    real K1;
    real k2;
    real k3;
    real k4;
    real k5;
    real KI;
    real Vnd;
    real BPp;
    real vB;

    real Th1;
    real Th2;
    real Ph1;
    real Ph2;
    real Ph3;
    
    real Th1low;
    real Th2low;
    real Ph1low;
    real Ph2low;
    real Ph3low;

    real tcorr;

    real predhigh;
    real predlow;
    real pred;
    
    real BPplow;
    real k4low;
    real k3low;
    real k5low;
    real KIlow;
    real Vndlow;
    real k2low;
    
    // real k5mean;
    // real BPpmean;
    

    K1 = exp(logK1);
    vB = exp(logvB);

    // High
    BPp = exp(logBPp);
    k4 = exp(logk4);
    k5 = exp(logk5);
    Vnd = exp(logVnd);
    
    // Low
    BPplow = exp(logBPp + logBPpdiff);
    k4low = exp(logk4 + logk4diff);
    k5low = exp(logk5 + logk5diff);
    Vndlow = exp(logVnd + logVnddiff);
    
    // Assumed to be indepenpendent of genotypes
    // note for myself: same no mather if mean(k5) or mean(k2)
    // k5mean = (k5 + k5low)/2;
    // BPpmean = (BPp + BPplow)/2;

    
    // High

    k2 = (K1 - k5 * BPp)/Vnd;
    k3 = BPp * (k4 + k5)/Vnd;
    KI = K1 * k3 * k5 / (k2 * k4 + k2 * k5 + k3 * k5);
  
    Th1 = 0.5 * (k2 + k3 + k4 + k5 + sqrt((k2 + k3 + k4 + k5)^2 - 4 * (k2 * k4 + k2 * k5 + k3 * k5)));
    Th2 = 0.5 * (k2 + k3 + k4 + k5 - sqrt((k2 + k3 + k4 + k5)^2 - 4 * (k2 * k4 + k2 * k5 + k3 * k5)));

    Ph1 = (K1 * (k3 + k4 + k5 - Th1) - KI * Th2)/(Th2 - Th1);
    Ph2 = (K1 * (Th2 - k3 - k4 - k5) + KI * Th1)/(Th2 - Th1);
    Ph3 = KI;
    
    
    // Low
    
    k2low = (K1 - k5low * BPplow)/Vndlow;
    k3low = BPplow * (k4low + k5low)/Vndlow;
    KIlow = K1 * k3low * k5low / (k2low * k4low + k2low * k5low + k3low * k5low);
    
    Th1low = 0.5 * (k2low + k3low + k4low + k5low + sqrt((k2low + k3low + k4low + k5low)^2 - 4 * (k2low * k4low + k2low * k5low + k3low * k5low)));
    Th2low = 0.5 * (k2low + k3low + k4low + k5low - sqrt((k2low + k3low + k4low + k5low)^2 - 4 * (k2low * k4low + k2low * k5low + k3low * k5low)));

    Ph1low = (K1 * (k3low + k4low + k5low - Th1low) - KIlow * Th2low)/(Th2low - Th1low);
    Ph2low = (K1 * (Th2low - k3low - k4low - k5low) + KIlow * Th1low)/(Th2low - Th1low);
    Ph3low = KIlow;

    

    tcorr = time - t0;

  predhigh =  
  (1-vB) * (
    (tcorr > 0) * (             // Before t0 equal to 0

      // 2TC off CND
      
        // Before t0+ti
        (tcorr < ti)*(1/ti)*(
          Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma,
                           Th1, Th2, Ph1, Ph2,Ph3)
        ) +

        // After t0+ti
        (tcorr >= ti)*(1/ti)* (
          Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma,
                           Th1, Th2, Ph1, Ph2, Ph3) -
            Integral_Feng_3TC5K(tcorr - ti, A, B, C, alpha, beta, gamma,
                           Th1, Th2, Ph1, Ph2, Ph3)
        )
      ) 
      
  ) +
  // Blood contribution
  vB *  bloodval;
  
  predlow =  
  (1-vB) * (
    (tcorr > 0) * (             // Before t0 equal to 0

      // 2TC
        // Before t0+ti
        (tcorr < ti)*(1/ti)*(
          Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma,
                           Th1low, Th2low, Ph1low, Ph2low, Ph3low)
        ) +

        // After t0+ti
        (tcorr >= ti)*(1/ti)* (
          Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma,
                           Th1low, Th2low, Ph1low, Ph2low, Ph3low) -
            Integral_Feng_3TC5K(tcorr - ti, A, B, C, alpha, beta, gamma,
                           Th1low, Th2low, Ph1low, Ph2low, Ph3low)
        )
      )
  ) +
  // Blood contribution
  vB *  bloodval;

  pred = ( prophigh * predhigh ) + ( proplow * predlow );

  return(pred);
}

"
```


# Fitting


## 5. 3TC5k

### 5.1 Prep for all variants 

#### One TAC

```{r}
dat_i <- simba_modeldata %>% 
  filter(pet==pet[5426]) %>% 
  filter(region=="Frontal") %>% 
  mutate(sqrtinvw = sqrt(1/weights)) 

```

##### Functions

```{r}
Integral_Feng_3TC5K <- function(t, A, B, C, alpha, beta, gamma, 
                                 Th1, Th2, Ph1, Ph2, Ph3) {

  (B*(1 - exp(-(alpha*t)))*Ph3)/alpha^2 + (C*(1 - exp(-(alpha*t)))*Ph3)/alpha^2 + (A*(-1 + exp(-(alpha*t)))*Ph3)/alpha^3 + 
  (B*(-1 + exp(-(beta*t)))*Ph3)/beta^2 + (C*(-1 + exp(-(gamma*t)))*Ph3)/gamma^2 + (A*Ph3*t)/alpha^2 - (B*Ph3*t)/alpha + (B*Ph3*t)/beta - 
  (C*Ph3*t)/alpha + (C*Ph3*t)/gamma - (A*Ph3*(1 - (1 + alpha*t)/exp(alpha*t)))/alpha^3 - (A*(1 - exp(-(alpha*t)))*Ph1)/(alpha*(alpha-Th1)^2) - 
  (A*Ph1*(1 - (1 + alpha*t)/exp(alpha*t)))/(alpha*(alpha-Th1)^2) + (B*(1 - exp(-(alpha*t)))*Ph1)/(alpha*(alpha - Th1)) + 
  (C*(1 - exp(-(alpha*t)))*Ph1)/(alpha*(alpha - Th1)) + (A*(1 - exp(-(t*Th1)))*Ph1)/((alpha-Th1)^2*Th1) - 
  (B*(1 - exp(-(t*Th1)))*Ph1)/((alpha - Th1)*Th1) - (C*(1 - exp(-(t*Th1)))*Ph1)/((alpha - Th1)*Th1) + (B*(1 - exp(-(t*Th1)))*Ph1)/((beta - Th1)*Th1) + 
  (C*(1 - exp(-(t*Th1)))*Ph1)/((gamma - Th1)*Th1) + (A*Ph1*(1 - (1 + alpha*t)/exp(alpha*t))*Th1)/(alpha^2*(alpha-Th1)^2) + 
  (B*(1 - exp(-(beta*t)))*Ph1)/(beta*(-beta + Th1)) + (C*(1 - exp(-(gamma*t)))*Ph1)/(gamma*(-gamma + Th1)) - 
  (A*(1 - exp(-(alpha*t)))*Ph2)/(alpha*(alpha-Th2)^2) - (A*Ph2*(1 - (1 + alpha*t)/exp(alpha*t)))/(alpha*(alpha-Th2)^2) + 
  (B*(1 - exp(-(alpha*t)))*Ph2)/(alpha*(alpha - Th2)) + (C*(1 - exp(-(alpha*t)))*Ph2)/(alpha*(alpha - Th2)) + 
  (A*(1 - exp(-(t*Th2)))*Ph2)/((alpha-Th2)^2*Th2) - (B*(1 - exp(-(t*Th2)))*Ph2)/((alpha - Th2)*Th2) - (C*(1 - exp(-(t*Th2)))*Ph2)/((alpha - Th2)*Th2) + 
  (B*(1 - exp(-(t*Th2)))*Ph2)/((beta - Th2)*Th2) + (C*(1 - exp(-(t*Th2)))*Ph2)/((gamma - Th2)*Th2) + 
  (A*Ph2*(1 - (1 + alpha*t)/exp(alpha*t))*Th2)/(alpha^2*(alpha-Th2)^2) + (B*(1 - exp(-(beta*t)))*Ph2)/(beta*(-beta + Th2)) + 
  (C*(1 - exp(-(gamma*t)))*Ph2)/(gamma*(-gamma + Th2))
  
}
```

Function to prepare the data for plotting (see nls fit for single TACs):

```{r}
plot_fit <- function(pet, region, data, fit) {
  
  preddata <- tibble(
    frame_mid = seq(min(data$frame_mid),
                max(data$frame_mid),
                length.out=1000)
  ) %>% 
    mutate(meanblood = approx(data$frame_mid, data$meanblood, xout = .$frame_mid)$y) %>% 
    mutate(TAC = predict(fit, newdata=list(frame_mid = .$frame_mid,
                                           meanblood = .$meanblood)))

  
  ggplot(data, aes(x=frame_mid, y=TAC)) +
    geom_point(aes(size=weights)) +
    geom_line(colour="red", data=preddata) +
    labs(title = paste0(pet, ": ", region,",Type: ", data$genotype))
  
}
```

#### Fixed priors

```{r}
simba_prior_threetc5k_fixed <- c(
  
  set_prior("normal(-2, 0.5)", nlpar = "logK1"),
  set_prior("normal(-0.3, 0.5)", nlpar = "logVnd"),
  set_prior("normal(0.7, 0.5)", nlpar = "logBPp"),
  set_prior("normal(-3, 0.5)", nlpar = "logk4"),
  set_prior("normal(-4, 1)", nlpar = "logk5"),
  set_prior("normal(-3, 0.25)", nlpar = "logvB", ub = -2.5), # upper limit
  
  set_prior("normal(0, 0.3)", nlpar = "logK1", class = "sd", group="sub"),
  set_prior("normal(0, 0.2)", nlpar = "logVnd", class = "sd", group="sub"),
  set_prior("normal(0, 0.5)", nlpar = "logBPp", class = "sd", group="sub"),
  set_prior("normal(0, 0.2)", nlpar = "logk4", class = "sd", group="sub"),
  set_prior("normal(0, 0.5)", nlpar = "logk5", class = "sd", group="sub"), # increased here
  set_prior("normal(0, 0.1)", nlpar = "logvB", class = "sd", group="sub"),
  
  set_prior("normal(0, 0.05)", nlpar = "logK1", class = "sd", group="pet:region"),
  set_prior("normal(0, 0.05)", nlpar = "logVnd", class = "sd", group="pet:region"),
  set_prior("normal(0, 0.05)", nlpar = "logBPp", class = "sd", group="pet:region"),
  set_prior("normal(0, 0.05)", nlpar = "logk4", class = "sd", group="pet:region"),
  set_prior("normal(0, 0.05)", nlpar = "logk5", class = "sd", group="pet:region"),
  
  set_prior("normal(0, 0.1)", nlpar = "logVnd", class = "sd", group="region"),
  set_prior("normal(0, 0.1)", nlpar = "logk4", class = "sd", group="region"),
  set_prior("normal(0, 0.1)", nlpar = "logk5", class = "sd", group="region"),
  set_prior("normal(0, 0.1)", nlpar = "logvB", class = "sd", group="region"),
  
  set_prior("normal(0, 0.2)", nlpar = "logvB", class = "sd", group="pet"),
  
  #set_prior("normal(0, 0.3)", coef="regionAccumbens",    nlpar="logK1"),
  set_prior("normal(0, 0.3)", coef="regionAmygdala",     nlpar="logK1"),
  #set_prior("normal(0, 0.3)", coef="regionCaudate",      nlpar="logK1"),
  set_prior("normal(0, 0.3)", coef="regionCerebellum",   nlpar="logK1"),
  #set_prior("normal(0, 0.3)", coef="regionFrontal",      nlpar="logK1"),
  set_prior("normal(0, 0.3)", coef="regionHippocampus",  nlpar="logK1"),
  #set_prior("normal(0, 0.3)", coef="regionInsula",       nlpar="logK1"),
  #set_prior("normal(0, 0.3)", coef="regionPCC",          nlpar="logK1"),
  set_prior("normal(0, 0.3)", coef="regionPutamen",      nlpar="logK1"),
  set_prior("normal(0, 0.3)", coef="regionTemporal",     nlpar="logK1"),
  set_prior("normal(0, 0.3)", coef="regionThalamus",     nlpar="logK1"),
  set_prior("normal(0, 0.3)", coef="regionOccipital",     nlpar="logK1"),
  set_prior("normal(0, 0.3)", coef="regionParietal",     nlpar="logK1"),
  
  #set_prior("normal(0, 0.3)", coef="regionAccumbens",    nlpar="logBPnd"),
  set_prior("normal(0, 0.3)", coef="regionAmygdala",     nlpar="logBPp"),
  #set_prior("normal(0, 0.3)", coef="regionCaudate",      nlpar="logBPnd"),
  set_prior("normal(0, 0.3)", coef="regionCerebellum",   nlpar="logBPp"),
  #set_prior("normal(0, 0.3)", coef="regionFrontal",      nlpar="logBPp"),
  set_prior("normal(0, 0.3)", coef="regionHippocampus",  nlpar="logBPp"),
  #set_prior("normal(0, 0.3)", coef="regionInsula",       nlpar="logBPnd"),
  #set_prior("normal(0, 0.3)", coef="regionPCC",          nlpar="logBPnd"),
  set_prior("normal(0, 0.3)", coef="regionPutamen",      nlpar="logBPp"),
  set_prior("normal(0, 0.3)", coef="regionTemporal",     nlpar="logBPp"),
  set_prior("normal(0, 0.3)", coef="regionThalamus",     nlpar="logBPp"),
  set_prior("normal(0, 0.3)", coef="regionOccipital",     nlpar="logBPp"),
  set_prior("normal(0, 0.3)", coef="regionParietal",     nlpar="logBPp"),
  
  set_prior("normal(0, 0.1)", coef="Age_dec_c", nlpar="logK1"),
  set_prior("normal(0, 0.1)", coef="Age_dec_c", nlpar="logBPp"),
  set_prior("normal(0, 0.1)", coef="Age_dec_c", nlpar="logVnd"),
  set_prior("normal(0, 0.1)", coef="Age_dec_c", nlpar="logk5"),
  
  set_prior("normal(0, 1)", coef="LPSpost", nlpar="logBPp"),
  set_prior("normal(0, 1)", coef="LPSpost", nlpar="logk5"),
  set_prior("normal(0, 0.2)", coef="LPSpost", nlpar="logK1"),
  #set_prior("normal(0, 0.2)", coef="LPSpost", nlpar="logVnd"),
  
  set_prior("normal(-0.5, 0.5)", coef="genotypeMAB", nlpar="logBPp"),
  #set_prior("normal(-1, 0.5)", coef="genotypeLAB", nlpar="logBPp"),
  
  set_prior("normal(0.5, 0.5)", coef="genotypeMAB", nlpar="logk4"),
  #set_prior("normal(1, 0.5)", coef="genotypeLAB", nlpar="logk4"),
  
  set_prior("normal(-0.5, 0.5)", coef="genotypeMAB", nlpar="logk5"),
  #set_prior("normal(-1, 0.5)", coef="genotypeLAB", nlpar="logk5"),

  set_prior("normal(-1, 0.2)", dpar = "sigma"),
  set_prior("normal(0, 0.3)", dpar = "sigma", class="sd", group="pet"),
  set_prior("normal(0, 0.1)", dpar = "sigma", class="sd", group="region"),
  
  set_prior("normal(0, 0.3)", coef="logRegSize_c", dpar = "sigma", class="b"),
  set_prior("normal(0, 0.5)", coef="logInjRad_c", dpar = "sigma", class="b"),
  set_prior("normal(0, 0.3)", coef="logdur_c", dpar = "sigma", class="b"),
  
  set_prior("student_t(3, 0, 2.5)", coef="sframe_mid_1", dpar = "sigma", class="b"),
  set_prior("student_t(3, 0, 2.5)", dpar = "sigma", class="sds")#,
  
  #set_prior("lkj(1)", class="cor", group = "sub"),
  #set_prior("lkj(2)", class="cor", group = "region"),
  #set_prior("lkj(2)", class="cor", group = "pet:region")
  )

```

#### Mixed

```{r}
simba_prior_threetc5k <- c(
  
  set_prior("normal(-2, 0.5)", nlpar = "logK1"),
  set_prior("normal(-0.3, 0.5)", nlpar = "logVnd"),
  set_prior("normal(0, 0.5)", nlpar = "logBPp"),
  set_prior("normal(-3, 0.5)", nlpar = "logk4"),
  set_prior("normal(-4.5, 1)", nlpar = "logk5"),
  set_prior("normal(-3, 0.25)", nlpar = "logvB", ub = -2.5), # upper limit
  
  # Genotype differences
  set_prior("normal(-1, 0.5)", nlpar = "logBPpdiff"),
  set_prior("normal(1, 0.5)", nlpar = "logk4diff"),
  set_prior("normal(-1, 0.5)", nlpar = "logk5diff"),
  
  set_prior("normal(0, 0.3)", nlpar = "logK1", class = "sd", group="sub"),
  set_prior("normal(0, 0.1)", nlpar = "logVnd", class = "sd", group="sub"),
  set_prior("normal(0, 0.5)", nlpar = "logBPp", class = "sd", group="sub"),
  set_prior("normal(0, 0.1)", nlpar = "logk4", class = "sd", group="sub"),
  set_prior("normal(0, 0.5)", nlpar = "logk5", class = "sd", group="sub"), # increased here
  set_prior("normal(0, 0.2)", nlpar = "logvB", class = "sd", group="sub"),
  
  set_prior("normal(0, 0.05)", nlpar = "logK1", class = "sd", group="pet:region"),
  set_prior("normal(0, 0.05)", nlpar = "logVnd", class = "sd", group="pet:region"),
  set_prior("normal(0, 0.05)", nlpar = "logBPp", class = "sd", group="pet:region"),
  set_prior("normal(0, 0.05)", nlpar = "logk4", class = "sd", group="pet:region"),
  set_prior("normal(0, 0.05)", nlpar = "logk5", class = "sd", group="pet:region"),
  
  set_prior("normal(0, 0.1)", nlpar = "logVnd", class = "sd", group="region"),
  set_prior("normal(0, 0.1)", nlpar = "logk4", class = "sd", group="region"),
  set_prior("normal(0, 0.1)", nlpar = "logk5", class = "sd", group="region"),
  set_prior("normal(0, 0.1)", nlpar = "logvB", class = "sd", group="region"),
  
  set_prior("normal(0, 0.2)", nlpar = "logvB", class = "sd", group="pet"),
  
  set_prior("normal(0, 0.3)", coef="regionAccumbens",    nlpar="logK1"),
  set_prior("normal(0, 0.3)", coef="regionAmygdala",     nlpar="logK1"),
  set_prior("normal(0, 0.3)", coef="regionCaudate",      nlpar="logK1"),
  set_prior("normal(0, 0.3)", coef="regionCerebellum",   nlpar="logK1"),
  set_prior("normal(0, 0.3)", coef="regionFrontal",      nlpar="logK1"),
  set_prior("normal(0, 0.3)", coef="regionHippocampus",  nlpar="logK1"),
  set_prior("normal(0, 0.3)", coef="regionInsula",       nlpar="logK1"),
  set_prior("normal(0, 0.3)", coef="regionPCC",          nlpar="logK1"),
  set_prior("normal(0, 0.3)", coef="regionPutamen",      nlpar="logK1"),
  set_prior("normal(0, 0.3)", coef="regionTemporal",     nlpar="logK1"),
  set_prior("normal(0, 0.3)", coef="regionThalamus",     nlpar="logK1"),
  
  set_prior("normal(0, 0.3)", coef="regionAccumbens",    nlpar="logBPp"),
  set_prior("normal(0, 0.3)", coef="regionAmygdala",     nlpar="logBPp"),
  set_prior("normal(0, 0.3)", coef="regionCaudate",      nlpar="logBPp"),
  set_prior("normal(0, 0.3)", coef="regionCerebellum",   nlpar="logBPp"),
  set_prior("normal(0, 0.3)", coef="regionFrontal",      nlpar="logBPp"),
  set_prior("normal(0, 0.3)", coef="regionHippocampus",  nlpar="logBPp"),
  set_prior("normal(0, 0.3)", coef="regionInsula",       nlpar="logBPp"),
  set_prior("normal(0, 0.3)", coef="regionPCC",          nlpar="logBPp"),
  set_prior("normal(0, 0.3)", coef="regionPutamen",      nlpar="logBPp"),
  set_prior("normal(0, 0.3)", coef="regionTemporal",     nlpar="logBPp"),
  set_prior("normal(0, 0.3)", coef="regionThalamus",     nlpar="logBPp"),
  
  set_prior("normal(0, 0.1)", coef="Age_dec_c", nlpar="logK1"),
  set_prior("normal(0, 0.1 )", coef="Age_dec_c", nlpar="logBPp"),
  set_prior("normal(0, 0.1 )", coef="Age_dec_c", nlpar="logVnd"),
  set_prior("normal(0, 0.1 )", coef="Age_dec_c", nlpar="logk5"),
  
  # set_prior("normal(0, 0.5 )", coef="GenotypeHAB", nlpar="logBPnd"),
  # set_prior("normal(0, 0.5 )", coef="GenotypeLAB", nlpar="logBPnd"),
  # 
  # set_prior("normal(0, 0.5 )", coef="GenotypeHAB", nlpar="logk4"),
  # set_prior("normal(0, 0.5 )", coef="GenotypeLAB", nlpar="logk4"),
  # 
  # set_prior("normal(0, 0.3 )", coef="GenotypeHAB", nlpar="logKb"),
  # set_prior("normal(0, 0.3 )", coef="GenotypeLAB", nlpar="logKb"),
  # 
  # set_prior("normal(0, 0.05)",  coef="SexMale", nlpar="logK1"),
  # set_prior("normal(0, 0.05 )", coef="SexMale", nlpar="logBPnd"),
  # set_prior("normal(0, 0.05 )", coef="SexMale", nlpar="logVnd"),

  set_prior("normal(-1, 0.2)", dpar = "sigma"),
  set_prior("normal(0, 0.3)", dpar = "sigma", class="sd", group="pet"),
  set_prior("normal(0, 0.1)", dpar = "sigma", class="sd", group="region"),
  
  set_prior("normal(0, 0.3)", coef="logRegSize_c", dpar = "sigma", class="b"),
  set_prior("normal(0, 0.5)", coef="logInjRad_c", dpar = "sigma", class="b"),
  set_prior("normal(0, 0.3)", coef="logdur_c", dpar = "sigma", class="b"),
  
  set_prior("student_t(3, 0, 4)", coef="sframe_mid_1", dpar = "sigma", class="b"),
  set_prior("student_t(3, 0, 2.5)", dpar = "sigma", class="sds")#,
  
  #set_prior("lkj(1)", class="cor", group = "sub"),
  #set_prior("lkj(2)", class="cor", group = "region"),
  #set_prior("lkj(2)", class="cor", group = "pet:region")
  )
```


### 5.2 ND 

#### 5.2.1 NLS

###### Function

```{r}
Model_FengConv_3TC5kND <- function(time, t0, A, B, C, alpha, beta, gamma, ti, 
                               bloodval, 
                               logK1, logVnd, logBPp, logk4,logk5, logvB) {
  
  
  K1 = exp(logK1)
  Vnd = exp(logVnd)
  BPp = exp(logBPp)
  k4 = exp(logk4)
  k5 = exp(logk5)
  vB = exp(logvB)
  
  k2 = K1 / Vnd -k5
  k3 = BPp * k4 * (k2 + k5)/K1
  
  th1 <- ((k2 + k3 + k4 + k5) - sqrt((k2 + k3 + k4 + k5)^2 - 4 * k4 * (k2 + k5))) / 2

  th2 <- ((k2 + k3 + k4 + k5) + sqrt((k2 + k3 + k4 + k5)^2 - 4 * k4 * (k2 + k5))) / 2
  
  ph1 <- (K1 * (k3 + k4 + k5 - th1) - th2 * K1 * k5 / (k2 + k5))/(th2 - th1)
  
  ph2 <- (K1 * (th2 - k3 - k4 - k5) + th1 * K1 * k5 / (k2 + k5))/(th2 - th1)
  
  ph3 <- K1 * k5 / (k2 + k5)
  
  tcorr <- time - t0
  
  # 2TC contribution
  (1-vB) * (
    (tcorr > 0) * (             # Before t0 equal to 0
      
      # Before t0+ti
      (tcorr < ti)*(1/ti)*(     
        Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma, 
                         th1, th2, ph1, ph2, ph3)
      ) +
        
      # After t0+ti 
      (tcorr >= ti)*(1/ti)* (   
        Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma, 
                         th1, th2, ph1, ph2, ph3) -
          Integral_Feng_3TC5K(tcorr - ti, A, B, C, alpha, beta, gamma, 
                         th1, th2, ph1, ph2, ph3)
      )
    )
  ) +
  # Blood contribution
  vB*bloodval
  
}
```


###### Fitting

```{r, eval=FALSE}
plan(multisession, workers = 12) # Run this in parallel across 6 cores.

modeldat_nested <- simba_modeldata %>% 
  group_by(pet, region) %>% 
  nest() %>%  
  ungroup() %>% # We need to ungroup before running the parallel functions with future_map
    mutate(fit = future_map(data, ~nls.multstart::nls_multstart(
      TAC ~ Model_FengConv_3TC5kND(frame_mid, t0, A, B, C, alpha, beta, gamma, ti,  #t_tac, t0
                               meanblood, 
                               logK1, logVnd, logBPp, logk4, logk5, logvB), data = .x,
      start_lower = c(logK1=-3.5, logVnd=0, logBPp=0, logk4=-5, logk5=-7.5, logvB=-3.5),
      start_upper = c(logK1=0, logVnd=3, logBPp=4, logk4=-1, logk5=-1, logvB=-2.5),
      lower = c(logK1=-3.5, logVnd=-2.5, logBPp=-2, logk4=-5, logk5=-7.5, logvB=-3.5),
      upper = c(logK1=0, logVnd=1, logBPp=4, logk4=-1, logk5=-1, logvB=-2.5),
      modelweights = weights, iter=40, supp_errors = "Y")))


saveRDS(modeldat_nested, "../DerivedData/nlsfitsND.rds")
```

counting the param values for all genotypes together:

```{r}
modeldat_pars <- readRDS("../DerivedData/nlsfitsND.rds") %>% 
  mutate(par = map(fit, ~as.data.frame(as.list(coef(.x))))) %>% 
  unnest(data) %>%
  select(pet, region, par,genotype) %>% 
  unnest(par)

nls <- modeldat_pars %>%
  gather(Parameter, Value, -pet, -region, -genotype) %>% 
  ggplot(aes(x=Value, fill=Parameter)) + 
  geom_histogram(colour="black") +
  facet_wrap(~Parameter, scales="free")

ggsave("nls3tc5kND.pdf", plot = nls, width = 10, height = 7, dpi = 300)
nls

```

counting param values for each genotype separately:

```{r}
nls <- modeldat_pars %>% 
  mutate(genotype = factor(genotype, levels = c("HAB", "MAB", "LAB"))) %>% 
  pivot_longer(
    cols = -c(pet, region, genotype),
    names_to = "Parameter",
    values_to = "Value"
  ) %>% 
  ggplot(aes(x = Value, fill=Parameter)) + 
  geom_histogram(colour = "black") +
  facet_grid(genotype ~ Parameter, scales = "free")

ggsave("nlsgenotype3tc5kND.pdf", plot = nls, width = 10, height = 7, dpi = 300)
nls
```

```{r}
plotdat <- readRDS("../DerivedData/nlsfitsND.rds") %>%
  slice(sample(1:nrow(.), size = 20)) 

pmap(list(plotdat$pet, plotdat$region, plotdat$data, plotdat$fit),
     plot_fit)
  
```

#### 5.2.2 One Tac Bayesian

```{r, eval=TRUE}
set.seed(1337)

threetc5kND_prior <- c(
  set_prior("normal(-2, 0.5)", nlpar = "logK1"),
  set_prior("normal(-0.3, 0.5)", nlpar = "logVnd"),
  set_prior("normal(0.7, 0.5)", nlpar = "logBPp"),
  set_prior("normal(-3, 0.5)", nlpar = "logk4"),
  set_prior("normal(-4, 1)", nlpar = "logk5"),
  set_prior("normal(-3, 0.25)", nlpar = "logvB"),
  
  set_prior("normal(0, 1)", dpar = "sigma", coef="sqrtinvw"))


threetc5kND_fit_formula <- bf( TAC ~ threetc5kND_log_stan(logK1, logVnd, logBPp, logk4,
                                                  logk5, logvB, 
                                                  frame_mid, 
                                    t0, 
                                    A, B, C, 
                                    alpha, beta, gamma, 
                                    ti, meanblood),
     sigma ~ 0 + sqrtinvw,
     # Nonlinear variables
     logK1 + logVnd + logBPp + logk4 + logk5 + logvB ~ 1,
     # Nonlinear fit
     nl = TRUE)

get_prior(threetc5kND_fit_formula, data=dat_i, family = gaussian())

make_stancode(threetc5kND_fit_formula,
  family=gaussian(), 
  data = dat_i,
  prior = threetc5kND_prior,
  stanvars = stanvar(scode = three_compartment_5k_fengconv_stan, 
                     block="functions"))


# get_prior(twotcm1k_fit_formula,
#   family=gaussian(), 
#   data = modeldat)


    
threetc5kND_fit <- brm(
  threetc5kND_fit_formula,
  family=gaussian(),
  data = dat_i,
  prior = threetc5kND_prior,
  stanvars = stanvar(scode = three_compartment_5k_fengconv_stan,
             block="functions"),
  control = list(adapt_delta=0.90),
  chains = 2,
  cores = 2,
  iter = 1000,
  backend = "rstan", init = 0)

  

#summary(threetc5kND_fit)


```


```{r, message=FALSE, warning=FALSE, results="hide", eval=TRUE}
brms::expose_functions(threetc5kND_fit, vectorize=TRUE, verbose = F, 
                       show_compiler_warnings = F)
```

```{r, eval=TRUE}
pred <- predict(threetc5kND_fit) %>% 
  as_tibble() %>% 
  select(P_L95 = "Q2.5",
         P_U95 = "Q97.5")

fitted <- fitted(threetc5kND_fit) %>% 
  as_tibble() %>% 
  select(Estimate, 
         F_L95 = "Q2.5",
         F_U95 = "Q97.5")

dat_i_fitted <- dat_i %>% 
  bind_cols(pred) %>% 
  bind_cols(fitted)

ggplot(dat_i_fitted, aes(x=frame_mid, y=TAC)) +
  geom_point() +
  geom_ribbon(aes(ymin=P_L95, ymax=P_U95), alpha=0.1) +
  geom_ribbon(aes(ymin=F_L95, ymax=F_U95), alpha=0.2) +
  geom_line(aes(y=Estimate)) 


```

#### 5.2.3 Fixed genotype levels

```{r} #univariate
# Nonlinear variables
                              logK1 ~ 1 + region + Age_dec_c + (1|sub) + 
                                  (1|pet:region),
                              logBPp ~  1 + region + Age_dec_c + genotype + 
                                         (1|sub) + (1|pet:region),
                              logVnd ~ 1 + Age_dec_c + (1|region) + (1|sub) +
                                (1|pet:region),
                              logk4 ~ 1 + genotype + (1|region) + (1|sub) +
                                (1|pet:region),
                              logk5 ~ 1 + genotype + Age_dec_c + (1|sub) + 
                              (1|region) + (1|pet:region),
                              logvB ~ 1 + (1|sub) + (1|region) + (1|pet),
                              # Nonlinear fit
                              nl = TRUE, center = TRUE)
```


##### Prep

```{r}
simba_fit_formula_3tc5kND_fixed <- bf( TAC ~ threetc5kND_log_stan_BPp(logK1, logVnd, logBPp, logk4,
                                                  logk5, logvB, 
                                                  frame_mid, 
                                    t0, 
                                    A, B, C, 
                                    alpha, beta, gamma, 
                                    ti, meanblood),
                              lf(sigma ~ 1 + s(frame_mid) + logRegSize_c + 
                                   logInjRad_c + logdur_c +
                                 (1 | region) + (1 | pet), center = FALSE),
                              

                              # Nonlinear variables
# univariate
                              # logK1 ~ 1 + region + Age_dec_c + (1|sub) +
                              #     (1|pet:region),
                              # logBPp ~  1 + region + Age_dec_c + genotype +
                              #            (1|sub) + (1|pet:region),
                              # logVnd ~ 1 + Age_dec_c + (1|region) + (1|sub) +
                              #   (1|pet:region),
                              # logk4 ~ 1 + genotype + (1|region) + (1|sub) +
                              #   (1|pet:region),
                              # logk5 ~ 1 + genotype + Age_dec_c + (1|sub) +
                              # (1|region) + (1|pet:region),
                              # logvB ~ 1 + (1|sub) + (1|region) + (1|pet),
                              # # Nonlinear fit
                              # nl = TRUE, center = TRUE)

# multivariate
#                               logK1 ~ 1 + region + Age_dec_c + (1|k|sub) + 
#                                   (1|l|pet:region),
#                               logBPp ~  1 + region + Age_dec_c + genotype +
#                                          (1|k|sub) + (1|l|pet:region),
#                               logVnd ~ 1 + Age_dec_c + (1|m|region) + (1|k|sub) +
#                                 (1|l|pet:region),
#                               logk4 ~ 1 + genotype + (1|m|region) + (1|k|sub) +
#                                 (1|l|pet:region),
#                               logk5 ~ 1 + genotype + Age_dec_c + (1|k|sub) + 
#                               (1|m|region) + (1|l|pet:region),
#                               logvB ~ 1 + (1|sub) + (1|region) + (1|pet),
#                               # Nonlinear fit
#                               nl = TRUE, center = TRUE)

# univariate with LPS
                              logK1 ~ 1 + region + Age_dec_c + (1|sub) + LPS +
                                  (1|pet:region),
                              logBPp ~  1 + region + Age_dec_c + genotype + LPS +
                                         (1|sub) + (1|pet:region),
                              logVnd ~ 1 + Age_dec_c + (1|region) + (1|sub) +
                                (1|pet:region),
                              logk4 ~ 1 + genotype + (1|region) + (1|sub) + 
                                (1|pet:region),
                              logk5 ~ 1 + genotype + Age_dec_c + (1|sub) + LPS +
                              (1|region) + (1|pet:region),
                              logvB ~ 1 + (1|sub) + (1|region) + (1|pet),
                              # Nonlinear fit
                              nl = TRUE, center = TRUE)

# multivariate with LPS for BPp and k4
#                               logK1 ~ 1 + region + Age_dec_c + (1|k|sub) + 
#                                   (1|l|pet:region),
#                               logBPp ~  1 + region + Age_dec_c + genotype + LPS +
#                                          (1|k|sub) + (1|l|pet:region),
#                               logVnd ~ 1 + Age_dec_c + (1|m|region) + (1|k|sub) +
#                                 (1|l|pet:region),
#                               logk4 ~ 1 + genotype + (1|m|region) + (1|k|sub) + LPS +
#                                 (1|l|pet:region),
#                               logk5 ~ 1 + genotype + Age_dec_c + (1|k|sub) + 
#                               (1|m|region) + (1|l|pet:region),
#                               logvB ~ 1 + (1|sub) + (1|region) + (1|pet),
#                               # Nonlinear fit
#                               nl = TRUE, center = TRUE)
  

sc <- make_stancode(simba_fit_formula_3tc5kND_fixed,
  family=gaussian(),
  data = simba_modeldata,
  prior = simba_prior_threetc5k_fixed,
  stanvars = stanvar(scode = three_compartment_5k_fengconv_stan,
                     block="functions"))

# writeLines(sc, "stancode_unmod_LL_2.stan")

stand <- brms::make_standata(simba_fit_formula_3tc5kND_fixed, 
                          data = simba_modeldata, 
                          family=gaussian(), 
                          prior = simba_prior_threetc5k_fixed)

stand_list <- list()
for (t in names(stand)) {
  stand_list[[t]] <- stand[[t]]
}
```

##### Fit

```{r}
rm(fit_3tc5kND_fixed)
job::job({
  fit_3tc5kND_fixed <- brm(
    simba_fit_formula_3tc5kND_fixed,
    family=gaussian(), 
    data = simba_modeldata, 
    prior = simba_prior_threetc5k_fixed,
    stanvars = stanvar(scode = three_compartment_5k_fengconv_stan, 
               block="functions"),
    backend = "cmdstanr", init = 0, iter = 1000, warmup = 300,
    chains=2, cores=2, threads = threading(5), seed =  765)
  
  saveRDS(fit_3tc5kND_fixed, "../DerivedData/3tc5kND_fit_fixed.rds")
})
```

```{r}
fit_3tc5kND_fixed <- readRDS("../DerivedData/3tc5kND_fit_fixed.rds")
#fit_3tc5kND_fixed <- readRDS("../DerivedData/3tc5kND_fit_sub_fixed.rds")
#fit_3tc5kND_fixed <- readRDS("../DerivedData/3tc5kND_fit_sub_fixed_multivariate.rds")
#fit_3tc5kND_fixed <- readRDS("../DerivedData/3tc5kND_fit_sub_fixed_multivariate_LPS.rds")
#fit_3tc5kND_fixed <- readRDS("../DerivedData/3tc5kND_fit_LPSpairs_fixed_multivariate_LPS.rds")
print(summary(fit_3tc5kND_fixed, digits=3))
```

```{r}
#duration one chain for 15 data points, with fixed genotype levels
as.integer(fit_3tc5kND_fixed$fit@metadata$metadata$time$total[1])/60/60
#duration one chain for 15 data points, with mixed genotype levels
as.integer(fit4_threetc5kND$fit@metadata$metadata$time$total[1])/60/60
```


##### Plot genotype difs

```{r, fig.height=6, fig.width=6}
fit <- fit_3tc5kND_fixed
fe3_3tc5kND_fixed_genotype <- fixef(fit) %>% 
  as_tibble(rownames="Parameter") %>% 
  filter(str_detect(Parameter, "genotype")) %>% 
  mutate(PK_Parameter = str_match(Parameter, "log(\\w*)_")[,2]) %>% 
  mutate(Genotype_Comparison = str_match(Parameter, "_genotype(\\w*)")[,2],
         Genotype_Comparison = paste0("HAB - ", Genotype_Comparison)) %>% 
  mutate(across(c(`Q2.5`, `Q97.5`, Estimate), ~100*(exp(.x)-1)))

ggplot(fe3_3tc5kND_fixed_genotype, aes(x=Estimate, y=Genotype_Comparison)) +
  geom_point() +
  geom_errorbar(aes(xmin=`Q2.5`, xmax=`Q97.5`), height = 0.1, orientation = "y") +
  geom_vline(xintercept = 0, linetype="dashed") +
  facet_wrap(~PK_Parameter, ncol=1, scales="free_y") +
  labs(y="", x = "Difference (%)")
```


##### Plot genotype difs: epred sub

```{r}
fit <- fit_3tc5kND_fixed
# Create subject-level prediction data
# Note: Using 'sub' instead of 'ID', 'region' instead of 'Region', 'pet' instead of 'ID:Region'
modelmat_sub <- fit$data %>% 
  as_tibble() %>% 
  mutate(region = NA,
         `pet:region` = NA) %>% 
  group_by(sub) %>% 
  dplyr::slice(1) %>% 
  ungroup()

# Extract logBPnd at subject level
BPp_sub_epred <- posterior_epred(fit, 
                                   newdata = modelmat_sub %>% as.data.frame(), 
                                   re_formula = ~ (1|sub), 
                                   nlpar = "logBPp") %>% 
  as_tibble() %>%
  gather(sub_n, logBPp) %>% 
  group_by(sub_n) %>% 
  mutate(sample_n = 1:n()) %>% 
  mutate(sub_n = str_remove(sub_n, "V"),
         sub_n = as.numeric(sub_n)) %>% 
  arrange(sub_n) %>% 
  group_by(sub_n) %>% 
  summarise(logBPp_mean = mean(logBPp),
            logBPp_q2.5 = quantile(logBPp, 0.025),
            logBPp_q97.5 = quantile(logBPp, 0.975)) %>% 
  mutate(sub = modelmat_sub$sub) %>% 
  left_join(modelmat_sub %>% select(sub, genotype, Age_dec_c)) %>% 
  mutate(genotype = factor(genotype, levels = c("HAB", "MAB", "LAB")))

# Extract logk5 at subject level
k5_sub_epred <- posterior_epred(fit, 
                                 newdata = modelmat_sub %>% as.data.frame(), 
                                 re_formula = ~ (1|sub), 
                                 nlpar = "logk5") %>% 
  as_tibble() %>%
  gather(sub_n, logk5) %>% 
  group_by(sub_n) %>% 
  mutate(sample_n = 1:n()) %>% 
  mutate(sub_n = str_remove(sub_n, "V"),
         sub_n = as.numeric(sub_n)) %>% 
  arrange(sub_n) %>% 
  group_by(sub_n) %>% 
  summarise(logk5_mean = mean(logk5),
            logk5_q2.5 = quantile(logk5, 0.025),
            logk5_q97.5 = quantile(logk5, 0.975)) %>% 
  mutate(sub = modelmat_sub$sub) %>% 
  left_join(modelmat_sub %>% select(sub, genotype, Age_dec_c)) %>% 
  mutate(genotype = factor(genotype, levels = c("HAB", "MAB", "LAB")))

# Extract logVnd at subject level
Vnd_sub_epred <- posterior_epred(fit, 
                                  newdata = modelmat_sub %>% as.data.frame(), 
                                  re_formula = ~ (1|sub), 
                                  nlpar = "logVnd") %>% 
  as_tibble() %>%
  gather(sub_n, logVnd) %>% 
  group_by(sub_n) %>% 
  mutate(sample_n = 1:n()) %>% 
  mutate(sub_n = str_remove(sub_n, "V"),
         sub_n = as.numeric(sub_n)) %>% 
  arrange(sub_n) %>% 
  group_by(sub_n) %>% 
  summarise(logVnd_mean = mean(logVnd),
            logVnd_q2.5 = quantile(logVnd, 0.025),
            logVnd_q97.5 = quantile(logVnd, 0.975)) %>% 
  mutate(sub = modelmat_sub$sub) %>% 
  left_join(modelmat_sub %>% select(sub, genotype, Age_dec_c)) %>% 
  mutate(genotype = factor(genotype, levels = c("HAB", "MAB", "LAB")))

# Extract logk4 at subject level
k4_sub_epred <- posterior_epred(fit, 
                                 newdata = modelmat_sub %>% as.data.frame(), 
                                 re_formula = ~ (1|sub), 
                                 nlpar = "logk4") %>% 
  as_tibble() %>%
  gather(sub_n, logk4) %>% 
  group_by(sub_n) %>% 
  mutate(sample_n = 1:n()) %>% 
  mutate(sub_n = str_remove(sub_n, "V"),
         sub_n = as.numeric(sub_n)) %>% 
  arrange(sub_n) %>% 
  group_by(sub_n) %>% 
  summarise(logk4_mean = mean(logk4),
            logk4_q2.5 = quantile(logk4, 0.025),
            logk4_q97.5 = quantile(logk4, 0.975)) %>% 
  mutate(sub = modelmat_sub$sub) %>% 
  left_join(modelmat_sub %>% select(sub, genotype, Age_dec_c)) %>% 
  mutate(genotype = factor(genotype, levels = c("HAB", "MAB", "LAB")))

# Extract logK1 at subject level
K1_sub_epred <- posterior_epred(fit, 
                                 newdata = modelmat_sub %>% as.data.frame(), 
                                 re_formula = ~ (1|sub), 
                                 nlpar = "logK1") %>% 
  as_tibble() %>%
  gather(sub_n, logK1) %>% 
  group_by(sub_n) %>% 
  mutate(sample_n = 1:n()) %>% 
  mutate(sub_n = str_remove(sub_n, "V"),
         sub_n = as.numeric(sub_n)) %>% 
  arrange(sub_n) %>% 
  group_by(sub_n) %>% 
  summarise(logK1_mean = mean(logK1),
            logK1_q2.5 = quantile(logK1, 0.025),
            logK1_q97.5 = quantile(logK1, 0.975)) %>% 
  mutate(sub = modelmat_sub$sub) %>% 
  left_join(modelmat_sub %>% select(sub, genotype, Age_dec_c)) %>% 
  mutate(genotype = factor(genotype, levels = c("HAB", "MAB", "LAB")))

# Plotting
ggplot(Vnd_sub_epred, aes(x = genotype, y = exp(logVnd_mean))) +
  ggbeeswarm::geom_beeswarm(cex = 3) +
  scale_y_log10() +
  labs(y = "Vnd", title = "Subject-level Vnd by Genotype")

ggplot(BPp_sub_epred, aes(x = genotype, y = exp(logBPp_mean))) +
  ggbeeswarm::geom_beeswarm(cex = 3) +
  scale_y_log10() +
  labs(y = "BPp", title = "Subject-level BPp by Genotype")

ggplot(k5_sub_epred, aes(x = genotype, y = exp(logk5_mean))) +
  ggbeeswarm::geom_beeswarm(cex = 3) +
  scale_y_log10() +
  labs(y = "k5", title = "Subject-level k5 by Genotype")

ggplot(k4_sub_epred, aes(x = genotype, y = exp(logk4_mean))) +
  ggbeeswarm::geom_beeswarm(cex = 3) +
  scale_y_log10() +
  labs(y = "k4", title = "Subject-level k4 by Genotype")

ggplot(K1_sub_epred, aes(x = genotype, y = exp(logK1_mean))) +
  ggbeeswarm::geom_beeswarm(cex = 3) +
  scale_y_log10() +
  labs(y = "K1", title = "Subject-level K1 by Genotype")


# Combine all subject-level estimates
sub_params_epred <- BPp_sub_epred %>% 
  select(sub, genotype, starts_with("logBPp")) %>% 
  left_join(k5_sub_epred %>% select(sub, starts_with("logk5"))) %>% 
  left_join(Vnd_sub_epred %>% select(sub, starts_with("logVnd"))) %>% 
  left_join(k4_sub_epred %>% select(sub, starts_with("logk4"))) %>% 
  left_join(K1_sub_epred %>% select(sub, starts_with("logK1")))

#write_csv(sub_params_epred, "../DerivedData/sub_params_epred_fit_3tc5kND_fixed.csv")
```


##### Plot genotype difs: epred PET

Here we have to average across regions because the pet effects are in pet:region

```{r}
fit <- fit_3tc5kND_fixed
# Create PET x Region prediction data (keeping region information)
modelmat_pet_region <- fit$data %>% 
  as_tibble() %>% 
  group_by(pet, region) %>% 
  dplyr::slice(1) %>% 
  ungroup() %>% 
  mutate(row_n = 1:n())

# Helper function to extract PET-level estimates (averaging over regions)
extract_pet_param <- function(fit, newdata, re_formula, nlpar, param_name) {
  
  posterior_epred(fit, 
                  newdata = newdata %>% as.data.frame(), 
                  re_formula = re_formula, 
                  nlpar = nlpar) %>% 
    as_tibble() %>%
    mutate(sample_n = 1:n()) %>% 
    pivot_longer(-sample_n, names_to = "row_n", values_to = "value") %>% 
    mutate(row_n = as.numeric(str_remove(row_n, "V"))) %>% 
    left_join(newdata %>% 
                select(row_n, pet, sub, region, genotype, Age_dec_c), 
              by = "row_n") %>% 
    # Average across regions within each PET and posterior sample
    group_by(sample_n, pet, sub, genotype, Age_dec_c) %>% 
    summarise(value = mean(value), .groups = "drop") %>% 
    # Summarise across posterior samples
    group_by(pet, sub, genotype, Age_dec_c) %>% 
    summarise("{param_name}_mean" := mean(value),
              "{param_name}_q2.5" := quantile(value, 0.025),
              "{param_name}_q97.5" := quantile(value, 0.975),
              .groups = "drop") %>% 
    mutate(genotype = factor(genotype, levels = c("HAB", "MAB", "LAB")))
}

# Extract all parameters
BPp_pet_epred <- extract_pet_param(fit, modelmat_pet_region,
                                     re_formula = ~ (1|sub) + (1|region) + (1|pet:region),
                                     nlpar = "logBPp", param_name = "logBPp")

k5_pet_epred <- extract_pet_param(fit, modelmat_pet_region,
                                   re_formula = ~ (1|sub) + (1|region) + (1|pet:region),
                                   nlpar = "logk5", param_name = "logk5")

Vnd_pet_epred <- extract_pet_param(fit, modelmat_pet_region,
                                    re_formula = ~ (1|sub) + (1|region) + (1|pet:region),
                                    nlpar = "logVnd", param_name = "logVnd")

k4_pet_epred <- extract_pet_param(fit, modelmat_pet_region,
                                   re_formula = ~ (1|sub) + (1|region) + (1|pet:region),
                                   nlpar = "logk4", param_name = "logk4")

K1_pet_epred <- extract_pet_param(fit, modelmat_pet_region,
                                   re_formula = ~ (1|sub) + (1|pet:region),
                                   nlpar = "logK1", param_name = "logK1")

Vb_pet_epred <- extract_pet_param(fit, modelmat_pet_region,
                                   re_formula = ~ (1|sub) + (1|region) + (1|pet),
                                   nlpar = "logvB", param_name = "logvB")

# Plotting with lines connecting repeated measurements within subjects
ggplot(Vnd_pet_epred, aes(x = genotype, y = exp(logVnd_mean))) +
  # geom_line(aes(group = sub), alpha = 0.3, linewidth = 0.5) +
  ggbeeswarm::geom_beeswarm(cex = 3) +
  scale_y_log10() +
  labs(y = "Vnd", title = "PET-level Vnd by Genotype")

ggplot(BPp_pet_epred, aes(x = genotype, y = exp(logBPp_mean))) +
  geom_line(aes(group = sub), alpha = 0.3, linewidth = 0.5) +
  ggbeeswarm::geom_beeswarm(cex = 3) +
  scale_y_log10() +
  labs(y = "BPp", title = "PET-level BPp by Genotype")

ggplot(k5_pet_epred, aes(x = genotype, y = exp(logk5_mean))) +
  # geom_line(aes(group = sub), alpha = 0.3, linewidth = 0.5) +
  ggbeeswarm::geom_beeswarm(cex = 3) +
  scale_y_log10() +
  labs(y = "k5", title = "PET-level k5 by Genotype")

ggplot(k4_pet_epred, aes(x = genotype, y = exp(logk4_mean))) +
  # geom_line(aes(group = sub), alpha = 0.3, linewidth = 0.5) +
  ggbeeswarm::geom_beeswarm(cex = 3) +
  scale_y_log10() +
  labs(y = "k4", title = "PET-level k4 by Genotype")

ggplot(K1_pet_epred, aes(x = genotype, y = exp(logK1_mean))) +
  # geom_line(aes(group = sub), alpha = 0.3, linewidth = 0.5) +
  ggbeeswarm::geom_beeswarm(cex = 3) +
  scale_y_log10() +
  labs(y = "K1", title = "PET-level K1 by Genotype")

# Combine all PET-level estimates
pet_params_epred <- BPp_pet_epred %>% 
  select(pet, sub, genotype, starts_with("logBPp")) %>% 
  left_join(k5_pet_epred %>% select(pet, starts_with("logk5"))) %>% 
  left_join(Vnd_pet_epred %>% select(pet, starts_with("logVnd"))) %>% 
  left_join(k4_pet_epred %>% select(pet, starts_with("logk4"))) %>% 
  left_join(K1_pet_epred %>% select(pet, starts_with("logK1")))

# write_csv(pet_params_epred, "../DerivedData/pet_params_epred_fit3_1k.csv")
```


```{r, fig.width=8, fig.height=12}
# Identify subjects with repeated measurements
repeated_subs <- pet_params_epred %>% 
  count(sub) %>% 
  filter(n > 1) %>% 
  pull(sub)

# Create PET order (1, 2) for repeated subjects
pet_params_repeated <- pet_params_epred %>% 
  filter(sub %in% repeated_subs) %>% 
  arrange(sub, pet) %>% 
  group_by(sub) %>% 
  mutate(
    scan_num = row_number(),
    pair = ceiling(scan_num / 2),           # pair 1 = scans 1&2, pair 2 = scans 3&4
    pet_num = case_when(
      scan_num %% 2 == 1 ~ "pre",           # odd scans = pre
      scan_num %% 2 == 0 ~ "post"           # even scans = post
    ),
    # Create a unique subject ID per pair so lines connect within pairs
    sub_pair = ifelse(pair == 1, sub, paste0(sub, "_pair", pair))
  ) %>%
  filter(!is.na(pet_num)) %>%               # drops unpaired 5th scan if present
  ungroup()

pet_params_repeated_long <- pet_params_repeated %>% 
  pivot_longer(
    cols = ends_with("_mean"),
    names_to = "parameter",
    values_to = "value"
  ) %>% 
  mutate(parameter = str_remove(parameter, "_mean"),
         parameter = str_remove(parameter, "log"),
         group = pet_num) %>% 
  select(pet, sub, sub_pair, genotype, parameter, value, group)

# Reshape to long format for faceting
pet_params_long <- pet_params_epred %>% 
  pivot_longer(
    cols = ends_with("_mean"),
    names_to = "parameter",
    values_to = "value"
  ) %>% 
  mutate(parameter = str_remove(parameter, "_mean"),
         parameter = str_remove(parameter, "log"),
         group = "All PETs",
         sub_pair = sub) %>% 
  select(pet, sub, sub_pair, genotype, parameter, value, group)

# Combine for plotting
plot_data <- bind_rows(pet_params_long, pet_params_repeated_long) %>% 
  mutate(group = factor(group, levels = c("All PETs", "pre", "post")),
         parameter = factor(parameter, levels = c("K1", "Vnd", "BPp", "k4", "k5"))) %>% 
  filter()

library(ggh4x)

plot <- ggplot(plot_data %>% 
         filter(sub != "C32"), aes(x = group, y = exp(value))) +
 geom_line(data = plot_data %>% 
              filter(sub != "C32") %>%
              filter(group != "All PETs") %>%
              select(sub, sub_pair, genotype, parameter, value, group) %>%
              summarise(value = mean(value),
                        .by = c(sub, sub_pair, genotype, parameter, group)) %>%
              pivot_wider(names_from = group, values_from = value) %>%
              filter(!is.na(pre), !is.na(post)) %>%
              pivot_longer(cols = c(pre, post), names_to = "group", values_to = "value") %>%
              mutate(group = factor(group, levels = c("All PETs", "pre", "post"))),
          aes(group = sub_pair), alpha = 0.3, linewidth = 0.5) +
  ggbeeswarm::geom_beeswarm(cex = 2, size = 1.5) +
  scale_y_log10() +
  facet_grid2(parameter ~ genotype, scales = "free", independent = "x") +
  labs(x = NULL, y = "Parameter value (natural scale)", 
       title = "All PETs vs pre/post-LPS by genotype") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
plot
ggsave("3tc5kND_prepostLPS.pdf", plot = plot, width = 10, height = 7, dpi = 300)
```


##### Predict

```{r}
job::job({
  priorfit <- brm(
    simba_fit_formula_3tc5kND_fixed,
    family=gaussian(),
    data = simba_modeldata,
    prior = simba_prior_threetc5k_fixed,
    stanvars = stanvar(scode = three_compartment_5k_fengconv_stan,
               block="functions"),
    backend = "rstan", init = 0, iter = 100,
    chains=2, cores=2, seed = 753273, sample_prior = "only")

brms::expose_functions(priorfit, vectorize=TRUE, verbose = F,
                       show_compiler_warnings = F)
  
  preds <- predict(fit_3tc5kND_fixed)
  fitted <- fitted(fit_3tc5kND_fixed)
  looic <- loo(fit_3tc5kND_fixed)

  saveRDS(preds, "../DerivedData/3tc5kND_preds_fixed.rds")
  saveRDS(fitted, "../DerivedData/3tc5kND_fitted_fixed.rds")
  saveRDS(looic, "../DerivedData/3tc5kND_looic_fixed.rds")
})
```

```{r}
preds <- readRDS("../DerivedData/3tc5kND_preds_fixed.rds")
fitted <- readRDS("../DerivedData/3tc5kND_fitted_fixed.rds")
#ps_loo <- readRDS("../DerivedData/fit4_loo.rds")

simba_modeldata$P_L95 <- preds[,3]
simba_modeldata$P_U95 <- preds[,4]
simba_modeldata$F_L95 <- fitted[,3]
simba_modeldata$F_U95 <- fitted[,4]
simba_modeldata$Estimate <- fitted[,1]
```

```{r, fig.height=7, fig.width=8}
library(ggsci)

check_some_fits <- function(modeldat, sampleid) {

    checkdat <- modeldat %>%
        filter(pet == sampleid)

    ggplot(checkdat, aes(x=frame_mid, y=TAC, colour=region, fill=region)) +
        geom_point(colour="black", size=2) +
        geom_point(size=1.5) +
        geom_ribbon(aes(ymin=P_L95, ymax=P_U95), alpha=0.2, colour=NA) +
        geom_ribbon(aes(ymin=F_L95, ymax=F_U95), alpha=0.4, colour=NA) +
        geom_line(aes(y=Estimate)) +
        facet_wrap(~region, scales="free", ncol=3) +
        scale_colour_manual(values=pal_futurama()(12)) +
        scale_fill_manual(values=pal_futurama(alpha = 0.3)(12)) +
        labs(y=expression(paste("Radioactivity (kBq/cc)", sep="")),
             x="Time (min)",
             title = paste(sampleid, ":", checkdat$genotype[1],":",checkdat$LPS[1],":",checkdat$LPSpair[1]))

}

ids <- unique(simba_modeldata$pet) #sample(unique(simba_modeldata$pet), 5)

map(ids, ~check_some_fits(simba_modeldata, .x))
```

### 5.3 S 

#### 5.3.1 NLS

##### Function

```{r}
Model_FengConv_3TC5kS <- function(time, t0, A, B, C, alpha, beta, gamma, ti, 
                               bloodval, 
                               logK1, logVnd, logBPp, logk4,logk5, logvB) {
  
  
  K1 = exp(logK1)
  Vnd = exp(logVnd)
  BPp = exp(logBPp)
  k4 = exp(logk4)
  k5 = exp(logk5)
  vB = exp(logvB)
  
  k2 = (K1 - k5 * BPp) / Vnd
  k3 = BPp * (k4 + k5)/ Vnd
  
  th1 <- ((k2 + k3 + k4 + k5) + sqrt((k2 + k3 + k4 + k5)^2 - 4 * (k2 * k4 + k2 * k5 + k3 *k5))) / 2

  th2 <- ((k2 + k3 + k4 + k5) - sqrt((k2 + k3 + k4 + k5)^2 - 4 * (k2 * k4 + k2 * k5 + k3 *k5))) / 2
  
  ph1 <- (K1 * (k3 + k4 + k5 - th1) - th2 * K1 * k5 / (k2 + k5))/(th2 - th1)
  
  ph2 <- (K1 * (th2 - k3 - k4 - k5) - th1 * K1 * k5 / (k2 + k5))/(th2 - th1)
  
  ph3 <- K1 * k3 * k5/ (k2*k4 + k2*k5 + k3*k5)
  
  tcorr <- time - t0
  
  # 2TC contribution
  (1-vB) * (
    (tcorr > 0) * (             # Before t0 equal to 0
      
      # Before t0+ti
      (tcorr < ti)*(1/ti)*(     
        Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma, 
                         th1, th2, ph1, ph2, ph3)
      ) +
        
      # After t0+ti 
      (tcorr >= ti)*(1/ti)* (   
        Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma, 
                         th1, th2, ph1, ph2, ph3) -
          Integral_Feng_3TC5K(tcorr - ti, A, B, C, alpha, beta, gamma, 
                         th1, th2, ph1, ph2, ph3)
      )
    )
  ) +
  # Blood contribution
  vB*bloodval
  
}
```


##### Fitting

```{r, eval=FALSE}
plan(multisession, workers = 3) # Run this in parallel across 6 cores.

modeldat_nested <- simba_modeldata %>% 
  group_by(pet, region) %>% 
  nest() %>%  
  ungroup() %>% # We need to ungroup before running the parallel functions with future_map
    mutate(fit = future_map(data, ~nls.multstart::nls_multstart(
      TAC ~ Model_FengConv_3TC5kS(frame_mid, t0, A, B, C, alpha, beta, gamma, ti,  #t_tac, t0
                               meanblood, 
                               logK1, logVnd, logBPp, logk4, logk5, logvB), data = .x,
      start_lower = c(logK1=-3.5, logVnd=-3, logBPp=0, logk4=-9, logk5=-9, logvB=-3.5),
      start_upper = c(logK1=0, logVnd=0.5, logBPp=6, logk4=-1, logk5=-1, logvB=-2.5),
      lower = c(logK1=-3.5, logVnd=-3, logBPp=-2, logk4=-9, logk5=-9, logvB=-3.5),
      upper = c(logK1=0, logVnd=0.5, logBPp=6, logk4=-1, logk5=-1, logvB=-2.5),
      modelweights = weights, iter=20, supp_errors = "Y")))


saveRDS(modeldat_nested, "../DerivedData/nlsfitsS.rds")
```

counting the param values for all genotypes together:

```{r}
modeldat_pars <- readRDS("../DerivedData/nlsfitsS.rds") %>% 
  mutate(par = map(fit, ~as.data.frame(as.list(coef(.x))))) %>% 
  unnest(data) %>%
  select(pet, region, par,genotype) %>% 
  unnest(par)

nls <- modeldat_pars %>%
  gather(Parameter, Value, -pet, -region, -genotype) %>% 
  ggplot(aes(x=Value, fill=Parameter)) + 
  geom_histogram(colour="black") +
  facet_wrap(~Parameter, scales="free")

ggsave("nls3tc5kS.pdf", plot = nls, width = 10, height = 7, dpi = 300)
```

counting param values for each genotype separately:

```{r}
nls <- modeldat_pars %>% 
  mutate(genotype = factor(genotype, levels = c("HAB", "MAB", "LAB"))) %>% 
  pivot_longer(
    cols = -c(pet, region, genotype),
    names_to = "Parameter",
    values_to = "Value"
  ) %>% 
  ggplot(aes(x = Value, fill=Parameter)) + 
  geom_histogram(colour = "black") +
  facet_grid(genotype ~ Parameter, scales = "free")

ggsave("nlsgenotype3tc5kS.pdf", plot = nls, width = 10, height = 7, dpi = 300)

```

```{r}
plotdat <- readRDS("../DerivedData/nlsfitsS.rds") %>%
  slice(sample(1:nrow(.), size = 20)) 

pmap(list(plotdat$pet, plotdat$region, plotdat$data, plotdat$fit),
     plot_fit)
  
```

#### 5.4.2 One TAC Bayesian

```{r, eval=TRUE}
set.seed(1337)

threetc5kS_prior <- c(
  set_prior("normal(-2, 0.5)", nlpar = "logK1"),
  set_prior("normal(-0.3, 0.5)", nlpar = "logVnd"),
  set_prior("normal(0.7, 0.5)", nlpar = "logBPnd"),
  set_prior("normal(-3, 0.5)", nlpar = "logk4"),
  set_prior("normal(-4, 1)", nlpar = "logk5"),
  set_prior("normal(-3, 0.25)", nlpar = "logvB"),
  
  set_prior("normal(0, 1)", dpar = "sigma", coef="sqrtinvw"))


threetc5kS_fit_formula <- bf( TAC ~ threetc5kS_log_stan(logK1, logVnd, logBPnd, logk4,
                                                  logk5, logvB, 
                                                  frame_mid, 
                                    t0, 
                                    A, B, C, 
                                    alpha, beta, gamma, 
                                    ti, meanblood),
     sigma ~ 0 + sqrtinvw,
     # Nonlinear variables
     logK1 + logVnd + logBPnd + logk4 + logk5 + logvB ~ 1,
     # Nonlinear fit
     nl = TRUE)

get_prior(threetc5kS_fit_formula, data=dat_i, family = gaussian())

make_stancode(threetc5kS_fit_formula,
  family=gaussian(), 
  data = dat_i,
  prior = threetc5kS_prior,
  stanvars = stanvar(scode = three_compartment_5k_fengconv_stan, 
                     block="functions"))


# get_prior(twotcm1k_fit_formula,
#   family=gaussian(), 
#   data = modeldat)


    
threetc5kS_fit <- brm(
  threetc5kS_fit_formula,
  family=gaussian(),
  data = dat_i,
  prior = threetc5kS_prior,
  stanvars = stanvar(scode = three_compartment_5k_fengconv_stan,
             block="functions"),
  control = list(adapt_delta=0.90),
  chains = 2,
  cores = 2,
  iter = 1000,
  backend = "rstan", init = 0)

  

#summary(threetc5kS_fit)


```


```{r, message=FALSE, warning=FALSE, results="hide", eval=TRUE}
brms::expose_functions(threetc5kS_fit, vectorize=TRUE, verbose = F, 
                       show_compiler_warnings = F)
```

```{r, eval=TRUE}
pred <- predict(threetc5kS_fit) %>% 
  as_tibble() %>% 
  select(P_L95 = "Q2.5",
         P_U95 = "Q97.5")

fitted <- fitted(threetc5kS_fit) %>% 
  as_tibble() %>% 
  select(Estimate, 
         F_L95 = "Q2.5",
         F_U95 = "Q97.5")

dat_i_fitted <- dat_i %>% 
  bind_cols(pred) %>% 
  bind_cols(fitted)

ggplot(dat_i_fitted, aes(x=frame_mid, y=TAC)) +
  geom_point() +
  geom_ribbon(aes(ymin=P_L95, ymax=P_U95), alpha=0.1) +
  geom_ribbon(aes(ymin=F_L95, ymax=F_U95), alpha=0.2) +
  geom_line(aes(y=Estimate)) 


```

#### 5.3.3 Fixed genotype levels

##### Prep

```{r}
simba_fit_formula_3tc5kS_fixed <- bf( TAC ~ threetc5kS_log_stan_BPp(logK1, logVnd, logBPp, logk4,
                                                  logk5, logvB, 
                                                  frame_mid, 
                                    t0, 
                                    A, B, C, 
                                    alpha, beta, gamma, 
                                    ti, meanblood),
                              lf(sigma ~ 1 + s(frame_mid) + logRegSize_c + 
                                   logInjRad_c + logdur_c +
                                 (1 | region) + (1 | pet), center = FALSE),
                              # Nonlinear variables
# univariate with LPS
                              logK1 ~ 1 + region + Age_dec_c + (1|sub) + LPS +
                                  (1|pet:region),
                              logBPp ~  1 + region + Age_dec_c + genotype + LPS +
                                         (1|sub) + (1|pet:region),
                              logVnd ~ 1 + Age_dec_c + (1|region) + (1|sub) +
                                (1|pet:region),
                              logk4 ~ 1 + genotype + (1|region) + (1|sub) + 
                                (1|pet:region),
                              logk5 ~ 1 + genotype + Age_dec_c + (1|sub) + LPS +
                              (1|region) + (1|pet:region),
                              logvB ~ 1 + (1|sub) + (1|region) + (1|pet),
                              # Nonlinear fit
                              nl = TRUE, center = TRUE)
  

sc <- make_stancode(simba_fit_formula_3tc5kS_fixed,
  family=gaussian(),
  data = simba_modeldata,
  prior = simba_prior_threetc5k_fixed,
  stanvars = stanvar(scode = three_compartment_5k_fengconv_stan,
                     block="functions"))

# writeLines(sc, "stancode_unmod_LL_2.stan")

stand <- brms::make_standata(simba_fit_formula_3tc5kS_fixed, 
                          data = simba_modeldata, 
                          family=gaussian(), 
                          prior = simba_prior_threetc5k_fixed)

stand_list <- list()
for (t in names(stand)) {
  stand_list[[t]] <- stand[[t]]
}
```

##### Fit

```{r}
rm(fit_3tc5kS_fixed)
job::job({
  fit_3tc5kS_fixed <- brm(
    simba_fit_formula_3tc5kS_fixed,
    family=gaussian(), 
    data = simba_modeldata,
    prior = simba_prior_threetc5k_fixed,
    stanvars = stanvar(scode = three_compartment_5k_fengconv_stan, 
               block="functions"),
    backend = "cmdstanr", init = 0, iter = 1000, warmup = 300,
    chains=2, cores=2, threads = threading(6), seed =  765)
  
  saveRDS(fit_3tc5kS_fixed, "../DerivedData/3tc5kS_fit_fixed.rds")
})
```

```{r}
fit_3tc5kS_fixed <- readRDS("../DerivedData/3tc5kS_fit_fixed.rds")
print(summary(fit_3tc5kS_fixed, digits=3))
```

##### Plot genotype difs

```{r, fig.height=6, fig.width=6}
fit <- fit_3tc5kS_fixed
fe3_3tc5kS_fixed_genotype <- fixef(fit) %>% 
  as_tibble(rownames="Parameter") %>% 
  filter(str_detect(Parameter, "genotype")) %>% 
  mutate(PK_Parameter = str_match(Parameter, "log(\\w*)_")[,2]) %>% 
  mutate(Genotype_Comparison = str_match(Parameter, "_genotype(\\w*)")[,2],
         Genotype_Comparison = paste0("HAB - ", Genotype_Comparison)) %>% 
  mutate(across(c(`Q2.5`, `Q97.5`, Estimate), ~100*(exp(.x)-1)))

ggplot(fe3_3tc5kS_fixed_genotype, aes(x=Estimate, y=Genotype_Comparison)) +
  geom_point() +
  geom_errorbar(aes(xmin=`Q2.5`, xmax=`Q97.5`), height = 0.1, orientation = "y") +
  geom_vline(xintercept = 0, linetype="dashed") +
  facet_wrap(~PK_Parameter, ncol=1, scales="free_y") +
  labs(y="", x = "Difference (%)")
  
```

##### Plot genotype difs: epred sub

```{r}
fit <- fit_3tc5kS_fixed
# Create subject-level prediction data
# Note: Using 'sub' instead of 'ID', 'region' instead of 'Region', 'pet' instead of 'ID:Region'
modelmat_sub <- fit$data %>% 
  as_tibble() %>% 
  mutate(region = NA,
         `pet:region` = NA) %>% 
  group_by(sub) %>% 
  dplyr::slice(1) %>% 
  ungroup()

# Extract logBPnd at subject level
BPnd_sub_epred <- posterior_epred(fit, 
                                   newdata = modelmat_sub %>% as.data.frame(), 
                                   re_formula = ~ (1|sub), 
                                   nlpar = "logBPnd") %>% 
  as_tibble() %>%
  gather(sub_n, logBPnd) %>% 
  group_by(sub_n) %>% 
  mutate(sample_n = 1:n()) %>% 
  mutate(sub_n = str_remove(sub_n, "V"),
         sub_n = as.numeric(sub_n)) %>% 
  arrange(sub_n) %>% 
  group_by(sub_n) %>% 
  summarise(logBPnd_mean = mean(logBPnd),
            logBPnd_q2.5 = quantile(logBPnd, 0.025),
            logBPnd_q97.5 = quantile(logBPnd, 0.975)) %>% 
  mutate(sub = modelmat_sub$sub) %>% 
  left_join(modelmat_sub %>% select(sub, genotype, Age_dec_c)) %>% 
  mutate(genotype = factor(genotype, levels = c("HAB", "MAB", "LAB")))

# Extract logk5 at subject level
k5_sub_epred <- posterior_epred(fit, 
                                 newdata = modelmat_sub %>% as.data.frame(), 
                                 re_formula = ~ (1|sub), 
                                 nlpar = "logk5") %>% 
  as_tibble() %>%
  gather(sub_n, logk5) %>% 
  group_by(sub_n) %>% 
  mutate(sample_n = 1:n()) %>% 
  mutate(sub_n = str_remove(sub_n, "V"),
         sub_n = as.numeric(sub_n)) %>% 
  arrange(sub_n) %>% 
  group_by(sub_n) %>% 
  summarise(logk5_mean = mean(logk5),
            logk5_q2.5 = quantile(logk5, 0.025),
            logk5_q97.5 = quantile(logk5, 0.975)) %>% 
  mutate(sub = modelmat_sub$sub) %>% 
  left_join(modelmat_sub %>% select(sub, genotype, Age_dec_c)) %>% 
  mutate(genotype = factor(genotype, levels = c("HAB", "MAB", "LAB")))

# Extract logVnd at subject level
Vnd_sub_epred <- posterior_epred(fit, 
                                  newdata = modelmat_sub %>% as.data.frame(), 
                                  re_formula = ~ (1|sub), 
                                  nlpar = "logVnd") %>% 
  as_tibble() %>%
  gather(sub_n, logVnd) %>% 
  group_by(sub_n) %>% 
  mutate(sample_n = 1:n()) %>% 
  mutate(sub_n = str_remove(sub_n, "V"),
         sub_n = as.numeric(sub_n)) %>% 
  arrange(sub_n) %>% 
  group_by(sub_n) %>% 
  summarise(logVnd_mean = mean(logVnd),
            logVnd_q2.5 = quantile(logVnd, 0.025),
            logVnd_q97.5 = quantile(logVnd, 0.975)) %>% 
  mutate(sub = modelmat_sub$sub) %>% 
  left_join(modelmat_sub %>% select(sub, genotype, Age_dec_c)) %>% 
  mutate(genotype = factor(genotype, levels = c("HAB", "MAB", "LAB")))

# Extract logk4 at subject level
k4_sub_epred <- posterior_epred(fit, 
                                 newdata = modelmat_sub %>% as.data.frame(), 
                                 re_formula = ~ (1|sub), 
                                 nlpar = "logk4") %>% 
  as_tibble() %>%
  gather(sub_n, logk4) %>% 
  group_by(sub_n) %>% 
  mutate(sample_n = 1:n()) %>% 
  mutate(sub_n = str_remove(sub_n, "V"),
         sub_n = as.numeric(sub_n)) %>% 
  arrange(sub_n) %>% 
  group_by(sub_n) %>% 
  summarise(logk4_mean = mean(logk4),
            logk4_q2.5 = quantile(logk4, 0.025),
            logk4_q97.5 = quantile(logk4, 0.975)) %>% 
  mutate(sub = modelmat_sub$sub) %>% 
  left_join(modelmat_sub %>% select(sub, genotype, Age_dec_c)) %>% 
  mutate(genotype = factor(genotype, levels = c("HAB", "MAB", "LAB")))

# Extract logK1 at subject level
K1_sub_epred <- posterior_epred(fit, 
                                 newdata = modelmat_sub %>% as.data.frame(), 
                                 re_formula = ~ (1|sub), 
                                 nlpar = "logK1") %>% 
  as_tibble() %>%
  gather(sub_n, logK1) %>% 
  group_by(sub_n) %>% 
  mutate(sample_n = 1:n()) %>% 
  mutate(sub_n = str_remove(sub_n, "V"),
         sub_n = as.numeric(sub_n)) %>% 
  arrange(sub_n) %>% 
  group_by(sub_n) %>% 
  summarise(logK1_mean = mean(logK1),
            logK1_q2.5 = quantile(logK1, 0.025),
            logK1_q97.5 = quantile(logK1, 0.975)) %>% 
  mutate(sub = modelmat_sub$sub) %>% 
  left_join(modelmat_sub %>% select(sub, genotype, Age_dec_c)) %>% 
  mutate(genotype = factor(genotype, levels = c("HAB", "MAB", "LAB")))

# Plotting
ggplot(Vnd_sub_epred, aes(x = genotype, y = exp(logVnd_mean))) +
  ggbeeswarm::geom_beeswarm(cex = 3) +
  scale_y_log10() +
  labs(y = "Vnd", title = "Subject-level Vnd by Genotype")

ggplot(BPnd_sub_epred, aes(x = genotype, y = exp(logBPnd_mean))) +
  ggbeeswarm::geom_beeswarm(cex = 3) +
  scale_y_log10() +
  labs(y = "BPnd", title = "Subject-level BPnd by Genotype")

ggplot(k5_sub_epred, aes(x = genotype, y = exp(logk5_mean))) +
  ggbeeswarm::geom_beeswarm(cex = 3) +
  scale_y_log10() +
  labs(y = "Kb", title = "Subject-level k5 by Genotype")

ggplot(k4_sub_epred, aes(x = genotype, y = exp(logk4_mean))) +
  ggbeeswarm::geom_beeswarm(cex = 3) +
  scale_y_log10() +
  labs(y = "k4", title = "Subject-level k4 by Genotype")

ggplot(K1_sub_epred, aes(x = genotype, y = exp(logK1_mean))) +
  ggbeeswarm::geom_beeswarm(cex = 3) +
  scale_y_log10() +
  labs(y = "K1", title = "Subject-level K1 by Genotype")


# Combine all subject-level estimates
sub_params_epred <- BPnd_sub_epred %>% 
  select(sub, genotype, starts_with("logBPnd")) %>% 
  left_join(k5_sub_epred %>% select(sub, starts_with("logk5"))) %>% 
  left_join(Vnd_sub_epred %>% select(sub, starts_with("logVnd"))) %>% 
  left_join(k4_sub_epred %>% select(sub, starts_with("logk4"))) %>% 
  left_join(K1_sub_epred %>% select(sub, starts_with("logK1")))

write_csv(sub_params_epred, "../DerivedData/sub_params_epred_fit_3tc5kS_fixed.csv")
```

##### Plot genotype difs: epred PET

Here we have to average across regions because the pet effects are in pet:region

```{r}
fit <- fit_3tc5kS_fixed
# Create PET x Region prediction data (keeping region information)
modelmat_pet_region <- fit$data %>% 
  as_tibble() %>% 
  group_by(pet, region) %>% 
  dplyr::slice(1) %>% 
  ungroup() %>% 
  mutate(row_n = 1:n())

# Helper function to extract PET-level estimates (averaging over regions)
extract_pet_param <- function(fit, newdata, re_formula, nlpar, param_name) {
  
  posterior_epred(fit, 
                  newdata = newdata %>% as.data.frame(), 
                  re_formula = re_formula, 
                  nlpar = nlpar) %>% 
    as_tibble() %>%
    mutate(sample_n = 1:n()) %>% 
    pivot_longer(-sample_n, names_to = "row_n", values_to = "value") %>% 
    mutate(row_n = as.numeric(str_remove(row_n, "V"))) %>% 
    left_join(newdata %>% 
                select(row_n, pet, sub, region, genotype, Age_dec_c), 
              by = "row_n") %>% 
    # Average across regions within each PET and posterior sample
    group_by(sample_n, pet, sub, genotype, Age_dec_c) %>% 
    summarise(value = mean(value), .groups = "drop") %>% 
    # Summarise across posterior samples
    group_by(pet, sub, genotype, Age_dec_c) %>% 
    summarise("{param_name}_mean" := mean(value),
              "{param_name}_q2.5" := quantile(value, 0.025),
              "{param_name}_q97.5" := quantile(value, 0.975),
              .groups = "drop") %>% 
    mutate(genotype = factor(genotype, levels = c("HAB", "MAB", "LAB")))
}

# Extract all parameters
BPnd_pet_epred <- extract_pet_param(fit, modelmat_pet_region,
                                     re_formula = ~ (1|sub) + (1|region) + (1|pet:region),
                                     nlpar = "logBPnd", param_name = "logBPnd")

k5_pet_epred <- extract_pet_param(fit, modelmat_pet_region,
                                   re_formula = ~ (1|sub) + (1|region) + (1|pet:region),
                                   nlpar = "logk5", param_name = "logk5")

Vnd_pet_epred <- extract_pet_param(fit, modelmat_pet_region,
                                    re_formula = ~ (1|sub) + (1|region) + (1|pet:region),
                                    nlpar = "logVnd", param_name = "logVnd")

k4_pet_epred <- extract_pet_param(fit, modelmat_pet_region,
                                   re_formula = ~ (1|sub) + (1|region) + (1|pet:region),
                                   nlpar = "logk4", param_name = "logk4")

K1_pet_epred <- extract_pet_param(fit, modelmat_pet_region,
                                   re_formula = ~ (1|sub) + (1|pet:region),
                                   nlpar = "logK1", param_name = "logK1")

Vb_pet_epred <- extract_pet_param(fit, modelmat_pet_region,
                                   re_formula = ~ (1|sub) + (1|region) + (1|pet),
                                   nlpar = "logvB", param_name = "logvB")

# Plotting with lines connecting repeated measurements within subjects
ggplot(Vnd_pet_epred, aes(x = genotype, y = exp(logVnd_mean))) +
  # geom_line(aes(group = sub), alpha = 0.3, linewidth = 0.5) +
  ggbeeswarm::geom_beeswarm(cex = 3) +
  scale_y_log10() +
  labs(y = "Vnd", title = "PET-level Vnd by Genotype")

ggplot(BPnd_pet_epred, aes(x = genotype, y = exp(logBPnd_mean))) +
  geom_line(aes(group = sub), alpha = 0.3, linewidth = 0.5) +
  ggbeeswarm::geom_beeswarm(cex = 3) +
  scale_y_log10() +
  labs(y = "BPnd", title = "PET-level BPnd by Genotype")

ggplot(k5_pet_epred, aes(x = genotype, y = exp(logk5_mean))) +
  # geom_line(aes(group = sub), alpha = 0.3, linewidth = 0.5) +
  ggbeeswarm::geom_beeswarm(cex = 3) +
  scale_y_log10() +
  labs(y = "k5", title = "PET-level k5 by Genotype")

ggplot(k4_pet_epred, aes(x = genotype, y = exp(logk4_mean))) +
  # geom_line(aes(group = sub), alpha = 0.3, linewidth = 0.5) +
  ggbeeswarm::geom_beeswarm(cex = 3) +
  scale_y_log10() +
  labs(y = "k4", title = "PET-level k4 by Genotype")

ggplot(K1_pet_epred, aes(x = genotype, y = exp(logK1_mean))) +
  # geom_line(aes(group = sub), alpha = 0.3, linewidth = 0.5) +
  ggbeeswarm::geom_beeswarm(cex = 3) +
  scale_y_log10() +
  labs(y = "K1", title = "PET-level K1 by Genotype")

# Combine all PET-level estimates
pet_params_epred <- BPnd_pet_epred %>% 
  select(pet, sub, genotype, starts_with("logBPnd")) %>% 
  left_join(k5_pet_epred %>% select(pet, starts_with("logk5"))) %>% 
  left_join(Vnd_pet_epred %>% select(pet, starts_with("logVnd"))) %>% 
  left_join(k4_pet_epred %>% select(pet, starts_with("logk4"))) %>% 
  left_join(K1_pet_epred %>% select(pet, starts_with("logK1")))

# write_csv(pet_params_epred, "../DerivedData/pet_params_epred_fit3_1k.csv")
```

```{r, fig.width=8, fig.height=12}
# Identify subjects with repeated measurements
repeated_subs <- pet_params_epred %>% 
  count(sub) %>% 
  filter(n > 1) %>% 
  pull(sub)

# Create PET order (1, 2) for repeated subjects
pet_params_repeated <- pet_params_epred %>% 
  filter(sub %in% repeated_subs) %>% 
  arrange(sub, pet) %>% 
  group_by(sub) %>% 
  mutate(pet_num = paste0("PET", row_number())) %>% 
  ungroup()

# Reshape to long format for faceting
pet_params_long <- pet_params_epred %>% 
  pivot_longer(
    cols = ends_with("_mean"),
    names_to = "parameter",
    values_to = "value"
  ) %>% 
  mutate(parameter = str_remove(parameter, "_mean"),
         parameter = str_remove(parameter, "log"),
         group = "All PETs") %>% 
  select(pet, sub, genotype, parameter, value, group)

pet_params_repeated_long <- pet_params_repeated %>% 
  pivot_longer(
    cols = ends_with("_mean"),
    names_to = "parameter",
    values_to = "value"
  ) %>% 
  mutate(parameter = str_remove(parameter, "_mean"),
         parameter = str_remove(parameter, "log"),
         group = pet_num) %>% 
  select(pet, sub, genotype, parameter, value, group)

# Combine for plotting
plot_data <- bind_rows(pet_params_long, pet_params_repeated_long) %>% 
  mutate(group = factor(group, levels = c("All PETs", "PET1", "PET2")),
         parameter = factor(parameter, levels = c("K1", "Vnd", "BPnd", "k4", "k5"))) %>% 
  filter()

library(ggh4x)

ggplot(plot_data %>% 
         filter(sub != "C32"), aes(x = group, y = exp(value))) +
  geom_line(data = plot_data %>% 
              filter(group != "All PETs") %>%
              select(sub, genotype, parameter, value, group) %>%
              pivot_wider(names_from = group, values_from = value) %>%
              pivot_longer(cols = c(PET1, PET2), names_to = "group", values_to = "value") %>%
              mutate(group = factor(group, levels = c("All PETs", "PET1", "PET2"))),
            aes(group = sub), alpha = 0.3, linewidth = 0.5) +
  ggbeeswarm::geom_beeswarm(cex = 2, size = 1.5) +
  scale_y_log10() +
  facet_grid2(parameter ~ genotype, scales = "free", independent = "x") +
  labs(x = NULL, y = "Parameter value (natural scale)", 
       title = "All PETs vs repeated measurements by genotype") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

##### Predict

```{r}
job::job({
  priorfit <- brm(
    simba_fit_formula_3tc5kS_fixed,
    family=gaussian(),
    data = simba_modeldata_sub,
    prior = simba_prior_threetc5k_fixed,
    stanvars = stanvar(scode = three_compartment_5k_fengconv_stan,
               block="functions"),
    backend = "rstan", init = 0, iter = 100,
    chains=2, cores=5, seed = 753273, sample_prior = "only")

brms::expose_functions(priorfit, vectorize=TRUE, verbose = F,
                       show_compiler_warnings = F)
  
  preds <- predict(fit_3tc5kS_fixed)
  fitted <- fitted(fit_3tc5kS_fixed)
  looic <- loo(fit_3tc5kS_fixed)
  
  saveRDS(preds, "../DerivedData/fit4_preds_threetc5kS_fixed.rds")
  saveRDS(fitted, "../DerivedData/fit4_fitted_threetc5kS_fixed.rds")
  saveRDS(looic, "../DerivedData/fit4_looic_threetc5kS_fixed.rds")
})
```

```{r}
preds <- readRDS("../DerivedData/fit4_preds_threetc5kS_fixed.rds")
fitted <- readRDS("../DerivedData/fit4_fitted_threetc5kS_fixed.rds")
#ps_loo <- readRDS("../DerivedData/fit4_loo.rds")

simba_modeldata_sub$P_L95 <- preds[,3]
simba_modeldata_sub$P_U95 <- preds[,4]
simba_modeldata_sub$F_L95 <- fitted[,3]
simba_modeldata_sub$F_U95 <- fitted[,4]
simba_modeldata_sub$Estimate <- fitted[,1]
```

```{r, fig.height=7, fig.width=8}
library(ggsci)

check_some_fits <- function(modeldat, sampleid) {

    checkdat <- modeldat %>%
        filter(pet == sampleid)

    ggplot(checkdat, aes(x=frame_mid, y=TAC, colour=region, fill=region)) +
        geom_point(colour="black", size=2) +
        geom_point(size=1.5) +
        geom_ribbon(aes(ymin=P_L95, ymax=P_U95), alpha=0.2, colour=NA) +
        geom_ribbon(aes(ymin=F_L95, ymax=F_U95), alpha=0.4, colour=NA) +
        geom_line(aes(y=Estimate)) +
        facet_wrap(~region, scales="free", ncol=3) +
        scale_colour_manual(values=pal_futurama()(12)) +
        scale_fill_manual(values=pal_futurama(alpha = 0.3)(12)) +
        labs(y=expression(paste("Radioactivity (kBq/cc)", sep="")),
             x="Time (min)",
             title = paste(sampleid, ":", checkdat$genotype[1]))

}

ids <- unique(simba_modeldata_sub$pet) #sample(unique(simba_modeldata$pet), 5)

map(ids, ~check_some_fits(simba_modeldata_sub, .x))
```

### 5.4 P 

#### 5.4.1 NLS

##### Function

```{r}
Model_FengConv_3TC5kP <- function(time, t0, A, B, C, alpha, beta, gamma, ti, 
                               bloodval, 
                               logK1, logVnd, logBPnd, logk4,logk5, logvB) {
  
  
  K1 = exp(logK1)
  Vnd = exp(logVnd)
  BPnd = exp(logBPnd)
  k4 = exp(logk4)
  k5 = exp(logk5)
  vB = exp(logvB)
  
  k2 = K1 / Vnd
  k3 = BPnd * k4
  
  th1 <- ((k2 + k3 + k4) - sqrt((k2 + k3 + k4)^2 - 4 * k2 * k4)) / 2

  th2 <- ((k2 + k3 + k4) + sqrt((k2 + k3 + k4)^2 - 4 * k2 * k4)) / 2
  
  ph1 <- (K1 * (k3 + k4 - th1))/(th2 - th1)
  
  ph2 <- (K1 * (th2 - k3 - k4))/(th2 - th1)
  
  ph3 <- k5
  
  tcorr <- time - t0
  
  # 2TC contribution
  (1-vB) * (
    (tcorr > 0) * (             # Before t0 equal to 0
      
      # Before t0+ti
      (tcorr < ti)*(1/ti)*(     
        Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma, 
                         th1, th2, ph1, ph2, ph3)
      ) +
        
      # After t0+ti 
      (tcorr >= ti)*(1/ti)* (   
        Integral_Feng_3TC5K(tcorr, A, B, C, alpha, beta, gamma, 
                         th1, th2, ph1, ph2, ph3) -
          Integral_Feng_3TC5K(tcorr - ti, A, B, C, alpha, beta, gamma, 
                         th1, th2, ph1, ph2, ph3)
      )
    )
  ) +
  # Blood contribution
  vB*bloodval
  
}
```


##### Fitting

```{r, eval=FALSE}
plan(multisession, workers = 6) # Run this in parallel across 6 cores.

modeldat_nested <- simba_modeldata %>% 
  group_by(pet, region) %>% 
  nest() %>%  
  ungroup() %>% # We need to ungroup before running the parallel functions with future_map
    mutate(fit = future_map(data, ~nls.multstart::nls_multstart(
      TAC ~ Model_FengConv_3TC5kP(frame_mid, t0, A, B, C, alpha, beta, gamma, ti,  #t_tac, t0
                               meanblood, 
                               logK1, logVnd, logBPnd, logk4, logk5, logvB), data = .x,
      start_lower = c(logK1=-3.5, logVnd=-3, logBPnd=0, logk4=-9, logk5=-9, logvB=-3.5),
      start_upper = c(logK1=0, logVnd=0.5, logBPnd=6, logk4=-1, logk5=-1, logvB=-2.5),
      lower = c(logK1=-3.5, logVnd=-3, logBPnd=-2, logk4=-9, logk5=-9, logvB=-3.5),
      upper = c(logK1=0, logVnd=0.5, logBPnd=6, logk4=-1, logk5=-1, logvB=-2.5),
      modelweights = weights, iter=20, supp_errors = "Y")))


saveRDS(modeldat_nested, "../DerivedData/nlsfits_P.rds")
```

```{r}
modeldat_pars <- readRDS("../DerivedData/nlsfits_P.rds") %>% 
  mutate(par = map(fit, ~as.data.frame(as.list(coef(.x))))) %>% 
  unnest(data) %>%
  select(pet, region, par,genotype) %>% 
  unnest(par)

nls <- modeldat_pars %>%
  gather(Parameter, Value, -pet, -region, -genotype) %>% 
  ggplot(aes(x=Value, fill=Parameter)) + 
  geom_histogram(colour="black") +
  facet_wrap(~Parameter, scales="free")

ggsave("nls3tc5kP.pdf", plot = nls, width = 10, height = 7, dpi = 300)
```

```{r}
nls <- modeldat_pars %>% 
  mutate(genotype = factor(genotype, levels = c("HAB", "MAB", "LAB"))) %>% 
  pivot_longer(
    cols = -c(pet, region, genotype),
    names_to = "Parameter",
    values_to = "Value"
  ) %>% 
  ggplot(aes(x = Value, fill=Parameter)) + 
  geom_histogram(colour = "black") +
  facet_grid(genotype ~ Parameter, scales = "free")

ggsave("nlsgenotype3tc5kP.pdf", plot = nls, width = 10, height = 7, dpi = 300)

```




```{r}
plotdat <- readRDS("../DerivedData/nlsfits_P.rds") %>%
  slice(sample(1:nrow(.), size = 20)) 

pmap(list(plotdat$pet, plotdat$region, plotdat$data, plotdat$fit),
     plot_fit)
```

#### 5.4.2 One TAC Bayesian

```{r, eval=TRUE}
set.seed(1337)

threetc5kP_prior <- c(
  set_prior("normal(-2, 0.5)", nlpar = "logK1"),
  set_prior("normal(-0.3, 0.5)", nlpar = "logVnd"),
  set_prior("normal(0.7, 0.5)", nlpar = "logBPnd"),
  set_prior("normal(-3, 0.5)", nlpar = "logk4"),
  set_prior("normal(-4, 1)", nlpar = "logk5"),
  set_prior("normal(-3, 0.25)", nlpar = "logvB"),
  
  set_prior("normal(0, 1)", dpar = "sigma", coef="sqrtinvw"))


threetc5kP_fit_formula <- bf( TAC ~ threetc5kP_log_stan(logK1, logVnd, logBPnd, logk4,
                                                  logk5, logvB, 
                                                  frame_mid, 
                                    t0, 
                                    A, B, C, 
                                    alpha, beta, gamma, 
                                    ti, meanblood),
     sigma ~ 0 + sqrtinvw,
     # Nonlinear variables
     logK1 + logVnd + logBPnd + logk4 + logk5 + logvB ~ 1,
     # Nonlinear fit
     nl = TRUE)

get_prior(threetc5kP_fit_formula, data=dat_i, family = gaussian())

make_stancode(threetc5kP_fit_formula,
  family=gaussian(), 
  data = dat_i,
  prior = threetc5kP_prior,
  stanvars = stanvar(scode = three_compartment_5k_fengconv_stan, 
                     block="functions"))


# get_prior(twotcm1k_fit_formula,
#   family=gaussian(), 
#   data = modeldat)


    
threetc5kP_fit <- brm(
  threetc5kP_fit_formula,
  family=gaussian(),
  data = dat_i,
  prior = threetc5kP_prior,
  stanvars = stanvar(scode = three_compartment_5k_fengconv_stan,
             block="functions"),
  control = list(adapt_delta=0.90),
  chains = 2,
  cores = 2,
  iter = 1000,
  backend = "rstan", init = 0)

  

summary(threetc5kP_fit)


```


```{r, message=FALSE, warning=FALSE, results="hide", eval=TRUE}
brms::expose_functions(threetc5kP_fit, vectorize=TRUE, verbose = F, 
                       show_compiler_warnings = F)
```

```{r, eval=TRUE}
pred <- predict(threetc5kP_fit) %>% 
  as_tibble() %>% 
  select(P_L95 = "Q2.5",
         P_U95 = "Q97.5")

fitted <- fitted(threetc5kP_fit) %>% 
  as_tibble() %>% 
  select(Estimate, 
         F_L95 = "Q2.5",
         F_U95 = "Q97.5")

dat_i_fitted <- dat_i %>% 
  bind_cols(pred) %>% 
  bind_cols(fitted)

ggplot(dat_i_fitted, aes(x=frame_mid, y=TAC)) +
  geom_point() +
  geom_ribbon(aes(ymin=P_L95, ymax=P_U95), alpha=0.1) +
  geom_ribbon(aes(ymin=F_L95, ymax=F_U95), alpha=0.2) +
  geom_line(aes(y=Estimate)) 


```

#### 5.4.3 Fixed genotype levels

##### Prep

```{r}
simba_fit_formula_3tc5kP_fixed <- bf( TAC ~ threetc5kP_log_stan(logK1, logVnd, logBPnd, logk4,
                                                  logk5, logvB, 
                                                  frame_mid, 
                                    t0, 
                                    A, B, C, 
                                    alpha, beta, gamma, 
                                    ti, meanblood),
                              lf(sigma ~ 1 + s(frame_mid) + logRegSize_c + 
                                   logInjRad_c + logdur_c +
                                 (1 | region) + (1 | pet), center = FALSE),
                              # Nonlinear variables
# univariate with LPS
                              logK1 ~ 1 + region + Age_dec_c + (1|sub) + LPS +
                                  (1|pet:region),
                              logBPp ~  1 + region + Age_dec_c + genotype + LPS +
                                         (1|sub) + (1|pet:region),
                              logVnd ~ 1 + Age_dec_c + (1|region) + (1|sub) +
                                (1|pet:region),
                              logk4 ~ 1 + genotype + (1|region) + (1|sub) + 
                                (1|pet:region),
                              logk5 ~ 1 + genotype + Age_dec_c + (1|sub) + LPS +
                              (1|region) + (1|pet:region),
                              logvB ~ 1 + (1|sub) + (1|region) + (1|pet),
                              # Nonlinear fit
                              nl = TRUE, center = TRUE)
  

sc <- make_stancode(simba_fit_formula_3tc5kP_fixed,
  family=gaussian(),
  data = simba_modeldata,
  prior = simba_prior_threetc5k_fixed,
  stanvars = stanvar(scode = three_compartment_5k_fengconv_stan,
                     block="functions"))

# writeLines(sc, "stancode_unmod_LL_2.stan")

stand <- brms::make_standata(simba_fit_formula_3tc5kP_fixed, 
                          data = simba_modeldata, 
                          family=gaussian(), 
                          prior = simba_prior_threetc5k_fixed)

stand_list <- list()
for (t in names(stand)) {
  stand_list[[t]] <- stand[[t]]
}
```

##### Fit

```{r}
rm(fit_3tc5kP_fixed)
job::job({
  fit_3tc5kP_fixed <- brm(
    simba_fit_formula_3tc5kP_fixed,
    family=gaussian(), 
    data = simba_modeldata,
    prior = simba_prior_threetc5k_fixed,
    stanvars = stanvar(scode = three_compartment_5k_fengconv_stan, 
               block="functions"),
    backend = "cmdstanr", init = 0, iter = 1000, warmup = 300,
    chains=2, cores=2, threads = threading(5), seed =  765)
  
  saveRDS(fit_3tc5kP_fixed, "../DerivedData/pbr_3tc5kP_fit_fixed.rds")
})
```

```{r}
fit_3tc5kP_fixed <- readRDS("../DerivedData/pbr_3tc5kP_fit_fixed.rds")
print(summary(fit_3tc5kP_fixed, digits=3))
```

##### Plot genotype difs

```{r, fig.height=6, fig.width=6}
fit <- fit_3tc5kP_fixed
fe3_3tc5kP_fixed_genotype <- fixef(fit) %>% 
  as_tibble(rownames="Parameter") %>% 
  filter(str_detect(Parameter, "genotype")) %>% 
  mutate(PK_Parameter = str_match(Parameter, "log(\\w*)_")[,2]) %>% 
  mutate(Genotype_Comparison = str_match(Parameter, "_genotype(\\w*)")[,2],
         Genotype_Comparison = paste0("HAB - ", Genotype_Comparison)) %>% 
  mutate(across(c(`Q2.5`, `Q97.5`, Estimate), ~100*(exp(.x)-1)))

ggplot(fe3_3tc5kP_fixed_genotype, aes(x=Estimate, y=Genotype_Comparison)) +
  geom_point() +
  geom_errorbar(aes(xmin=`Q2.5`, xmax=`Q97.5`), height = 0.1, orientation = "y") +
  geom_vline(xintercept = 0, linetype="dashed") +
  facet_wrap(~PK_Parameter, ncol=1, scales="free_y") +
  labs(y="", x = "Difference (%)")
  
```

##### Plot genotype difs: epred sub

```{r}
fit <- fit_3tc5kP_fixed
# Create subject-level prediction data
# Note: Using 'sub' instead of 'ID', 'region' instead of 'Region', 'pet' instead of 'ID:Region'
modelmat_sub <- fit$data %>% 
  as_tibble() %>% 
  mutate(region = NA,
         `pet:region` = NA) %>% 
  group_by(sub) %>% 
  dplyr::slice(1) %>% 
  ungroup()

# Extract logBPnd at subject level
BPnd_sub_epred <- posterior_epred(fit, 
                                   newdata = modelmat_sub %>% as.data.frame(), 
                                   re_formula = ~ (1|sub), 
                                   nlpar = "logBPnd") %>% 
  as_tibble() %>%
  gather(sub_n, logBPnd) %>% 
  group_by(sub_n) %>% 
  mutate(sample_n = 1:n()) %>% 
  mutate(sub_n = str_remove(sub_n, "V"),
         sub_n = as.numeric(sub_n)) %>% 
  arrange(sub_n) %>% 
  group_by(sub_n) %>% 
  summarise(logBPnd_mean = mean(logBPnd),
            logBPnd_q2.5 = quantile(logBPnd, 0.025),
            logBPnd_q97.5 = quantile(logBPnd, 0.975)) %>% 
  mutate(sub = modelmat_sub$sub) %>% 
  left_join(modelmat_sub %>% select(sub, genotype, Age_dec_c)) %>% 
  mutate(genotype = factor(genotype, levels = c("HAB", "MAB", "LAB")))

# Extract logk5 at subject level
k5_sub_epred <- posterior_epred(fit, 
                                 newdata = modelmat_sub %>% as.data.frame(), 
                                 re_formula = ~ (1|sub), 
                                 nlpar = "logk5") %>% 
  as_tibble() %>%
  gather(sub_n, logk5) %>% 
  group_by(sub_n) %>% 
  mutate(sample_n = 1:n()) %>% 
  mutate(sub_n = str_remove(sub_n, "V"),
         sub_n = as.numeric(sub_n)) %>% 
  arrange(sub_n) %>% 
  group_by(sub_n) %>% 
  summarise(logk5_mean = mean(logk5),
            logk5_q2.5 = quantile(logk5, 0.025),
            logk5_q97.5 = quantile(logk5, 0.975)) %>% 
  mutate(sub = modelmat_sub$sub) %>% 
  left_join(modelmat_sub %>% select(sub, genotype, Age_dec_c)) %>% 
  mutate(genotype = factor(genotype, levels = c("HAB", "MAB", "LAB")))

# Extract logVnd at subject level
Vnd_sub_epred <- posterior_epred(fit, 
                                  newdata = modelmat_sub %>% as.data.frame(), 
                                  re_formula = ~ (1|sub), 
                                  nlpar = "logVnd") %>% 
  as_tibble() %>%
  gather(sub_n, logVnd) %>% 
  group_by(sub_n) %>% 
  mutate(sample_n = 1:n()) %>% 
  mutate(sub_n = str_remove(sub_n, "V"),
         sub_n = as.numeric(sub_n)) %>% 
  arrange(sub_n) %>% 
  group_by(sub_n) %>% 
  summarise(logVnd_mean = mean(logVnd),
            logVnd_q2.5 = quantile(logVnd, 0.025),
            logVnd_q97.5 = quantile(logVnd, 0.975)) %>% 
  mutate(sub = modelmat_sub$sub) %>% 
  left_join(modelmat_sub %>% select(sub, genotype, Age_dec_c)) %>% 
  mutate(genotype = factor(genotype, levels = c("HAB", "MAB", "LAB")))

# Extract logk4 at subject level
k4_sub_epred <- posterior_epred(fit, 
                                 newdata = modelmat_sub %>% as.data.frame(), 
                                 re_formula = ~ (1|sub), 
                                 nlpar = "logk4") %>% 
  as_tibble() %>%
  gather(sub_n, logk4) %>% 
  group_by(sub_n) %>% 
  mutate(sample_n = 1:n()) %>% 
  mutate(sub_n = str_remove(sub_n, "V"),
         sub_n = as.numeric(sub_n)) %>% 
  arrange(sub_n) %>% 
  group_by(sub_n) %>% 
  summarise(logk4_mean = mean(logk4),
            logk4_q2.5 = quantile(logk4, 0.025),
            logk4_q97.5 = quantile(logk4, 0.975)) %>% 
  mutate(sub = modelmat_sub$sub) %>% 
  left_join(modelmat_sub %>% select(sub, genotype, Age_dec_c)) %>% 
  mutate(genotype = factor(genotype, levels = c("HAB", "MAB", "LAB")))

# Extract logK1 at subject level
K1_sub_epred <- posterior_epred(fit, 
                                 newdata = modelmat_sub %>% as.data.frame(), 
                                 re_formula = ~ (1|sub), 
                                 nlpar = "logK1") %>% 
  as_tibble() %>%
  gather(sub_n, logK1) %>% 
  group_by(sub_n) %>% 
  mutate(sample_n = 1:n()) %>% 
  mutate(sub_n = str_remove(sub_n, "V"),
         sub_n = as.numeric(sub_n)) %>% 
  arrange(sub_n) %>% 
  group_by(sub_n) %>% 
  summarise(logK1_mean = mean(logK1),
            logK1_q2.5 = quantile(logK1, 0.025),
            logK1_q97.5 = quantile(logK1, 0.975)) %>% 
  mutate(sub = modelmat_sub$sub) %>% 
  left_join(modelmat_sub %>% select(sub, genotype, Age_dec_c)) %>% 
  mutate(genotype = factor(genotype, levels = c("HAB", "MAB", "LAB")))

# Plotting
ggplot(Vnd_sub_epred, aes(x = genotype, y = exp(logVnd_mean))) +
  ggbeeswarm::geom_beeswarm(cex = 3) +
  scale_y_log10() +
  labs(y = "Vnd", title = "Subject-level Vnd by Genotype")

ggplot(BPnd_sub_epred, aes(x = genotype, y = exp(logBPnd_mean))) +
  ggbeeswarm::geom_beeswarm(cex = 3) +
  scale_y_log10() +
  labs(y = "BPnd", title = "Subject-level BPnd by Genotype")

ggplot(k5_sub_epred, aes(x = genotype, y = exp(logk5_mean))) +
  ggbeeswarm::geom_beeswarm(cex = 3) +
  scale_y_log10() +
  labs(y = "k5", title = "Subject-level k5 by Genotype")

ggplot(k4_sub_epred, aes(x = genotype, y = exp(logk4_mean))) +
  ggbeeswarm::geom_beeswarm(cex = 3) +
  scale_y_log10() +
  labs(y = "k4", title = "Subject-level k4 by Genotype")

ggplot(K1_sub_epred, aes(x = genotype, y = exp(logK1_mean))) +
  ggbeeswarm::geom_beeswarm(cex = 3) +
  scale_y_log10() +
  labs(y = "k4", title = "Subject-level K1 by Genotype")


# Combine all subject-level estimates
sub_params_epred <- BPnd_sub_epred %>% 
  select(sub, genotype, starts_with("logBPnd")) %>% 
  left_join(k5_sub_epred %>% select(sub, starts_with("logk5"))) %>% 
  left_join(Vnd_sub_epred %>% select(sub, starts_with("logVnd"))) %>% 
  left_join(k4_sub_epred %>% select(sub, starts_with("logk4"))) %>% 
  left_join(K1_sub_epred %>% select(sub, starts_with("logK1")))

write_csv(sub_params_epred, "../DerivedData/sub_params_epred_fit_3tc5kP_fixed.csv")
```

##### Plot genotype difs: epred PET

Here we have to average across regions because the pet effects are in pet:region

```{r}
fit <- fit_3tc5kP_fixed
# Create PET x Region prediction data (keeping region information)
modelmat_pet_region <- fit$data %>% 
  as_tibble() %>% 
  group_by(pet, region) %>% 
  dplyr::slice(1) %>% 
  ungroup() %>% 
  mutate(row_n = 1:n())

# Helper function to extract PET-level estimates (averaging over regions)
extract_pet_param <- function(fit, newdata, re_formula, nlpar, param_name) {
  
  posterior_epred(fit, 
                  newdata = newdata %>% as.data.frame(), 
                  re_formula = re_formula, 
                  nlpar = nlpar) %>% 
    as_tibble() %>%
    mutate(sample_n = 1:n()) %>% 
    pivot_longer(-sample_n, names_to = "row_n", values_to = "value") %>% 
    mutate(row_n = as.numeric(str_remove(row_n, "V"))) %>% 
    left_join(newdata %>% 
                select(row_n, pet, sub, region, genotype, Age_dec_c), 
              by = "row_n") %>% 
    # Average across regions within each PET and posterior sample
    group_by(sample_n, pet, sub, genotype, Age_dec_c) %>% 
    summarise(value = mean(value), .groups = "drop") %>% 
    # Summarise across posterior samples
    group_by(pet, sub, genotype, Age_dec_c) %>% 
    summarise("{param_name}_mean" := mean(value),
              "{param_name}_q2.5" := quantile(value, 0.025),
              "{param_name}_q97.5" := quantile(value, 0.975),
              .groups = "drop") %>% 
    mutate(genotype = factor(genotype, levels = c("HAB", "MAB", "LAB")))
}

# Extract all parameters
BPnd_pet_epred <- extract_pet_param(fit, modelmat_pet_region,
                                     re_formula = ~ (1|sub) + (1|region) + (1|pet:region),
                                     nlpar = "logBPnd", param_name = "logBPnd")

k5_pet_epred <- extract_pet_param(fit, modelmat_pet_region,
                                   re_formula = ~ (1|sub) + (1|region) + (1|pet:region),
                                   nlpar = "logk5", param_name = "logk5")

Vnd_pet_epred <- extract_pet_param(fit, modelmat_pet_region,
                                    re_formula = ~ (1|sub) + (1|region) + (1|pet:region),
                                    nlpar = "logVnd", param_name = "logVnd")

k4_pet_epred <- extract_pet_param(fit, modelmat_pet_region,
                                   re_formula = ~ (1|sub) + (1|region) + (1|pet:region),
                                   nlpar = "logk4", param_name = "logk4")

K1_pet_epred <- extract_pet_param(fit, modelmat_pet_region,
                                   re_formula = ~ (1|sub) + (1|pet:region),
                                   nlpar = "logK1", param_name = "logK1")

Vb_pet_epred <- extract_pet_param(fit, modelmat_pet_region,
                                   re_formula = ~ (1|sub) + (1|region) + (1|pet),
                                   nlpar = "logvB", param_name = "logvB")

# Plotting with lines connecting repeated measurements within subjects
ggplot(Vnd_pet_epred, aes(x = genotype, y = exp(logVnd_mean))) +
  # geom_line(aes(group = sub), alpha = 0.3, linewidth = 0.5) +
  ggbeeswarm::geom_beeswarm(cex = 3) +
  scale_y_log10() +
  labs(y = "Vnd", title = "PET-level Vnd by Genotype")

ggplot(BPnd_pet_epred, aes(x = genotype, y = exp(logBPnd_mean))) +
  geom_line(aes(group = sub), alpha = 0.3, linewidth = 0.5) +
  ggbeeswarm::geom_beeswarm(cex = 3) +
  scale_y_log10() +
  labs(y = "BPnd", title = "PET-level BPnd by Genotype")

ggplot(k5_pet_epred, aes(x = genotype, y = exp(logk5_mean))) +
  # geom_line(aes(group = sub), alpha = 0.3, linewidth = 0.5) +
  ggbeeswarm::geom_beeswarm(cex = 3) +
  scale_y_log10() +
  labs(y = "k5", title = "PET-level k5 by Genotype")

ggplot(k4_pet_epred, aes(x = genotype, y = exp(logk4_mean))) +
  # geom_line(aes(group = sub), alpha = 0.3, linewidth = 0.5) +
  ggbeeswarm::geom_beeswarm(cex = 3) +
  scale_y_log10() +
  labs(y = "k4", title = "PET-level k4 by Genotype")

ggplot(K1_pet_epred, aes(x = genotype, y = exp(logK1_mean))) +
  # geom_line(aes(group = sub), alpha = 0.3, linewidth = 0.5) +
  ggbeeswarm::geom_beeswarm(cex = 3) +
  scale_y_log10() +
  labs(y = "K1", title = "PET-level K1 by Genotype")

# Combine all PET-level estimates
pet_params_epred <- BPnd_pet_epred %>% 
  select(pet, sub, genotype, starts_with("logBPnd")) %>% 
  left_join(k5_pet_epred %>% select(pet, starts_with("logk5"))) %>% 
  left_join(Vnd_pet_epred %>% select(pet, starts_with("logVnd"))) %>% 
  left_join(k4_pet_epred %>% select(pet, starts_with("logk4"))) %>% 
  left_join(K1_pet_epred %>% select(pet, starts_with("logK1")))

# write_csv(pet_params_epred, "../DerivedData/pet_params_epred_fit3_1k.csv")
```

```{r, fig.width=8, fig.height=12}
# Identify subjects with repeated measurements
repeated_subs <- pet_params_epred %>% 
  count(sub) %>% 
  filter(n > 1) %>% 
  pull(sub)

# Create PET order (1, 2) for repeated subjects
pet_params_repeated <- pet_params_epred %>% 
  filter(sub %in% repeated_subs) %>% 
  arrange(sub, pet) %>% 
  group_by(sub) %>% 
  mutate(pet_num = paste0("PET", row_number())) %>% 
  ungroup()

# Reshape to long format for faceting
pet_params_long <- pet_params_epred %>% 
  pivot_longer(
    cols = ends_with("_mean"),
    names_to = "parameter",
    values_to = "value"
  ) %>% 
  mutate(parameter = str_remove(parameter, "_mean"),
         parameter = str_remove(parameter, "log"),
         group = "All PETs") %>% 
  select(pet, sub, genotype, parameter, value, group)

pet_params_repeated_long <- pet_params_repeated %>% 
  pivot_longer(
    cols = ends_with("_mean"),
    names_to = "parameter",
    values_to = "value"
  ) %>% 
  mutate(parameter = str_remove(parameter, "_mean"),
         parameter = str_remove(parameter, "log"),
         group = pet_num) %>% 
  select(pet, sub, genotype, parameter, value, group)

# Combine for plotting
plot_data <- bind_rows(pet_params_long, pet_params_repeated_long) %>% 
  mutate(group = factor(group, levels = c("All PETs", "PET1", "PET2")),
         parameter = factor(parameter, levels = c("K1", "Vnd", "BPnd", "k4", "k5"))) %>% 
  filter()

library(ggh4x)

ggplot(plot_data %>% 
         filter(sub != "C32"), aes(x = group, y = exp(value))) +
  geom_line(data = plot_data %>% 
              filter(group != "All PETs") %>%
              select(sub, genotype, parameter, value, group) %>%
              pivot_wider(names_from = group, values_from = value) %>%
              pivot_longer(cols = c(PET1, PET2), names_to = "group", values_to = "value") %>%
              mutate(group = factor(group, levels = c("All PETs", "PET1", "PET2"))),
            aes(group = sub), alpha = 0.3, linewidth = 0.5) +
  ggbeeswarm::geom_beeswarm(cex = 2, size = 1.5) +
  scale_y_log10() +
  facet_grid2(parameter ~ genotype, scales = "free", independent = "x") +
  labs(x = NULL, y = "Parameter value (natural scale)", 
       title = "All PETs vs repeated measurements by genotype") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

##### Predict

```{r}
job::job({
  priorfit <- brm(
    simba_fit_formula_3tc5kP_fixed,
    family=gaussian(),
    data = simba_modeldata_sub,
    prior = simba_prior_threetc5k_fixed,
    stanvars = stanvar(scode = three_compartment_5k_fengconv_stan,
               block="functions"),
    backend = "rstan", init = 0, iter = 100,
    chains=2, cores=2, seed = 753273, sample_prior = "only")

brms::expose_functions(priorfit, vectorize=TRUE, verbose = F,
                       show_compiler_warnings = F)
  
  preds <- predict(fit_3tc5kP_fixed)
  fitted <- fitted(fit_3tc5kP_fixed)
  looic <- loo(fit_3tc5kP_fixed)
  
  saveRDS(preds, "../DerivedData/fit4_preds_threetc5kP_fixed.rds")
  saveRDS(fitted, "../DerivedData/fit4_fitted_threetc5kP_fixed.rds")
  saveRDS(looic, "../DerivedData/fit4_looic_threetc5kP_fixed.rds")
})
```

```{r}
preds <- readRDS("../DerivedData/fit4_preds_threetc5kP_fixed.rds")
fitted <- readRDS("../DerivedData/fit4_fitted_threetc5kP_fixed.rds")
#ps_loo <- readRDS("../DerivedData/fit4_loo.rds")

simba_modeldata_sub$P_L95 <- preds[,3]
simba_modeldata_sub$P_U95 <- preds[,4]
simba_modeldata_sub$F_L95 <- fitted[,3]
simba_modeldata_sub$F_U95 <- fitted[,4]
simba_modeldata_sub$Estimate <- fitted[,1]
```

```{r, fig.height=7, fig.width=8}
library(ggsci)

check_some_fits <- function(modeldat, sampleid) {

    checkdat <- modeldat %>%
        filter(pet == sampleid)

    ggplot(checkdat, aes(x=frame_mid, y=TAC, colour=region, fill=region)) +
        geom_point(colour="black", size=2) +
        geom_point(size=1.5) +
        geom_ribbon(aes(ymin=P_L95, ymax=P_U95), alpha=0.2, colour=NA) +
        geom_ribbon(aes(ymin=F_L95, ymax=F_U95), alpha=0.4, colour=NA) +
        geom_line(aes(y=Estimate)) +
        facet_wrap(~region, scales="free", ncol=3) +
        scale_colour_manual(values=pal_futurama()(12)) +
        scale_fill_manual(values=pal_futurama(alpha = 0.3)(12)) +
        labs(y=expression(paste("Radioactivity (kBq/cc)", sep="")),
             x="Time (min)",
             title = paste(sampleid, ":", checkdat$genotype[1]))

}

ids <- unique(simba_modeldata_sub$pet) #sample(unique(simba_modeldata$pet), 5)

map(ids, ~check_some_fits(simba_modeldata_sub, .x))
```


# Model comparison

Here we will do model comparison using the pareto smoothed importance sampling using the leave-one out criterion.
This is embedded in the loo package:

## Fixed genotype levels

```{r}
loo_3tc5kND_fixed <- readRDS("../DerivedData/3tc5kND_looic_fixed.rds")
loo_3tc5kS_fixed <- readRDS("../DerivedData/fit4_looic_threetc5kS_fixed.rds")
loo_3tc5kP_fixed <- readRDS("../DerivedData/fit4_looic_threetc5kP_fixed.rds")
#checks predictive performance
loo_compare(list("3tc5kND_fixed" =loo_3tc5kND_mixed, "3tc5kS_fixed"=loo_3tc5kS_mixed,"3tc5kP_fixed"=loo_3tc5kP_fixed))
```

other things that can be checked for modelfit criteria:

```{r}
plot <- plot(loo_3tc5kND_mixed)
ggsave("loo3tc5kND.pdf", plot = plot, width = 10, height = 7, dpi = 300)
```

```{r}
#used to check R_hats  and effective sample size, posterior predictive checks
plot <- pp_check(fit4_threetc5kND, ndraws = 100)
ggsave("loondraws3tc5kND.pdf", plot = plot, width = 10, height = 7, dpi = 300)
```

```{r}
plot <- pp_check(fit4_threetc5kND, type = "intervals", x = "frame_mid")
ggsave("looint3tc5kND.pdf", plot = plot, width = 10, height = 7, dpi = 300)
```

```{r}
plot <- pp_check(fit4_threetc5kND, type = "error_scatter_avg_vs_x", group = "frame_mid")
ggsave("looerrsc3tc5kND.pdf", plot = plot, width = 10, height = 7, dpi = 300)
```

```{r}
plot <- pp_check(fit4_threetc5kND, type = "intervals_grouped", group = "proplow")
ggsave("loointgroup3tc5kND.pdf", plot = plot, width = 10, height = 7, dpi = 300)
```

```{r}
pp_check(fit4_threetc5kS, type = "error_hist")
pp_check(fit4_threetc5kS, type = "scatter_avg")
pp_check(fit4_threetc5kS,type = "stat_2d")
pp_check(fit4_threetc5kS, type="loo_pit_overlay")
pp_check(fit4_threetc5kS, type = "loo_intervals")
```

