---
title: "Munge"
output: html_notebook
---

# Aims

Let's extract the data from the datasheets for the first set of Yale UCB-J data.

# Libraries

```{r}
library(tidyverse)
library(readxl)
library(kinfitr)
library(naniar)
library(lubridate)
library(mgcv)
library(gratia)
library(glue)
library(cowplot)
library(stringr)

#for SiMBA prep
library(bloodstream)
library(brms)
library(rstan)
library(furrr)
library(ggcorrplot2)
#remotes::install_github("caijun/ggcorrplot2")
#devtools::install_github("mathesong/relfeas")
#library(relfeas)
#library(devtools)
library(readxl)
```

# Demographics

Should i include tracer, diagnosis and secondary diagnosis, patient state (pre, post, test)
```{r}
demog <- read_excel("/home/lisatjarks/Repositories/Yale_data/RawData/InjectionInfo/PETInjectionInformation.xlsx",
                    sheet = "all_protocols_combined") %>% 
  select(ID = PatientID,
         PET = InjectionID,
         Age = age,
         Sex = sex,
         Weight = weight,
         InjRad = dose_MBq,
         fP = free_fraction_number) %>% 
  mutate(InjRad_SUV = InjRad / Weight)

saveRDS(demog, "/home/lisatjarks/Repositories/Yale_data/DerivedData/Data1_demographics.rds")
```

```{r}
demog <- readRDS("/home/lisatjarks/Repositories/Yale_data/DerivedData/Data1_demographics.rds") %>%
  mutate(IDPET = paste(ID,PET,sep="_"))%>%
  group_by(IDPET) %>%
  nest(.key="demog")
```


# Data Sheets

```{r}
dat <- tibble(
  filename = list.files("/home/lisatjarks/Repositories/Yale_data/RawData/all_data/", pattern="csv",
                        full.names = T)) %>% 
  mutate(Type = case_when(
    str_detect(filename, "All_TACs_all") ~ "TAC",
    str_detect(filename, "InputFunction") ~ "AIF",
    str_detect(filename, "WholeBlood") ~ "WB",
    str_detect(filename, "Plasma") ~"PLASMA",
    str_detect(filename,"FittedParentFraction") ~"PARENT"))
```

## Plasma (after 3min)
the the last columns did not have a header anymore, so finding the actual amount of headers that we need (amount , in the last col +1)
pasting the values in the next col
same header structure as before, starting with v14

```{r}
plasmadat <- dat %>%
  filter(Type=="PLASMA") %>%
  mutate(plasma = map(filename, read_csv, show_col_types = FALSE))%>%
  mutate(plasma = map(plasma, ~{
  last_col_name <- names(.x)[ncol(.x)]
  
  # count max splits needed
  max_splits <- max(str_count(.x[[last_col_name]], ","), na.rm = TRUE) + 1
  
  .x %>%
    separate(last_col_name,
             into = paste0("v", (14):(13 + max_splits)),
             sep = ",",
             fill = "right",
             extra = "drop")
}))
  
```

```{r}
plasmadat_final <- plasmadat %>%
  filter(Type=="PLASMA") %>%
  mutate(plasma = map(plasma, ~{
  minutes_pos <- which(names(.x) == "Unit")
  .x %>%
    mutate(across((minutes_pos + 1):ncol(.x), as.character)) %>%
    pivot_longer(
      cols = (minutes_pos + 1):ncol(.x),  # all columns after 'Unit'
      names_to = "col",
      values_to = "value"
    ) %>%
    pivot_wider(id_cols = c(PATIENTID, INJECTIONID, PSTATE,PROTOCOL, col),
                names_from = Variable,
                values_from = value) %>%
    rename (Time = t, PLASMA = y1)%>%
    mutate(Time = as.numeric(Time),
           PLASMA = as.numeric(PLASMA)/1000) %>%
    mutate(Time= ifelse(Time>=120,120,Time)) %>% 
    select(-col)
})) %>%
  unnest(plasma) %>%
  filter(!is.na(PLASMA) & PLASMA != "") %>%
  mutate(IDPET=paste(PATIENTID,INJECTIONID,sep="_")) %>%
  select(-Type, -filename,-PATIENTID,-INJECTIONID) %>%
  group_by(IDPET,PROTOCOL) %>%
  nest(.key="plasma")
```

## Parent (fitted)

```{r}
parentdat <- dat %>%
  filter(Type=="PARENT") %>%
  mutate(parent = map(filename, read_csv, show_col_types = FALSE))%>%
  mutate(parent = map(parent, ~{
  minutes_pos <- which(names(.x) == "minutes")
  .x %>%
    pivot_longer(
      cols = (minutes_pos + 1):ncol(.x),  # all columns after 'minutes'
      names_to = "Time",
      values_to = "PARENT"
    ) %>%
    mutate(Time = as.numeric(Time))
})) %>%
    unnest(parent) %>%
    mutate(IDPET=paste(PATIENTID,INJECTIONID,sep="_")) %>%
    select(IDPET,Time, PARENT) %>%
    group_by(IDPET) %>% 
    nest(.key="parent")
```

just double checking that we do not have several AnalysisIDs for the same PET/ID. if empty, id say its uniquely identifiable

```{r}
# check <- parentdat %>%
#   unnest(parent) %>%
#   ungroup() %>%
#   #group_by(PET, ID) %>%
#   summarise(n_distinct_col3 = n_distinct(ANALYSISID), .by = c(PET,ID)) %>%
#   filter(n_distinct_col3 > 1)
```

## AIF
### AIF_calc (after 3min)
AIF_calc=Parent*Plasma
Goal is to calculate the AIF myself since it looks interpolated after around 5-10 minutes

just a little note:
- ANALYSISID in plasmadat and parentdat do not match which is why i excluded it 

```{r}
data_parentplasma <- parentdat %>%
  inner_join(plasmadat_final) %>%
  mutate(combined = map2(plasma, parent, ~{
    parent_interp <- approx(
      x = .y$Time,
      y = .y$PARENT,
      xout = .x$Time,
      method = "linear"
    )
    
    # combine with plasma data
    .x %>%
      mutate(PARENT = parent_interp$y)
  })) %>%
  select(IDPET,PROTOCOL,combined) %>%
  unnest(combined) %>%
  mutate(PLASMA =as.numeric(PLASMA),
         PARENT =as.numeric(PARENT),
         AIF_calc=PLASMA*PARENT) %>%
  filter(!is.na(AIF_calc)) %>% 
  group_by(IDPET,PROTOCOL) %>%
  nest(.key="aif_calc")
```



### AIF ("fitted" that look raw)

Here I'll take the fitted AIF, and convert it to MBq.

```{r}
aifdat <- dat %>% 
  filter(Type=="AIF") %>% 
  mutate(aif = map(filename, read_csv, show_col_types = FALSE)) %>% 
  mutate(aif = map(aif, ~{
  minutes_pos <- which(names(.x) == "minutes")
  .x %>%
    pivot_longer(
      cols = (minutes_pos + 1):ncol(.x),  # all columns after 'minutes'
      names_to = "Time",
      values_to = "AIF"
    ) %>%
    mutate(Time = as.numeric(Time),
           AIF = ifelse(is.na(AIF),0,AIF / 1000))
})) %>%
    unnest(aif) %>%
    mutate(IDPET = paste(PATIENTID,INJECTIONID,sep="_")) %>%
    select(-PATIENTID, -INJECTIONID) %>%
    group_by(IDPET) %>% 
    nest(.key="aif")
```


Let's plot a couple to be sure

```{r}
  
aifdat %>% filter(ID == "DD191", PET=="12227") %>% 
  unnest(aif) %>%
  ggplot(aes(x=Time, y=AIF)) +
  geom_point() +
  geom_line() +
  xlim(0,10)


ggplot(aifdat$aif[[2]], aes(x=Time, y=AIF)) +
  geom_point() +
  geom_line() +
  xlim(0,10) + 
  scale_x_log10()
```

note: since it looks kind of fitted after 3 minutes, and we have the data for all plasma and parent after 3 minutes, we start there to calculate our own AIF



### Join (/10min)

joining aif and self calculated aif to get the best out of all worlds

```{r}
data_aif_combined <- data_parentplasma %>%
  inner_join(aifdat, by = join_by(IDPET)) %>%
  mutate(aif=map(aif, ~.x %>% filter(as.numeric(Time)<10) %>%
                   select(Time, AIF))) %>%
  mutate(aif_calc=map(aif_calc, ~.x %>% filter(as.numeric(Time)>10) %>%
                        rename(AIF = AIF_calc) %>%
                    select(Time, AIF))) %>% #, PARENT, PLASMA
  mutate(combined = map2(aif, aif_calc, ~bind_rows(.x, .y))) %>%
  select(-aif, -aif_calc) %>%
  unnest(combined) %>%
  mutate(AIF = as.numeric(AIF),
         Time = as.numeric(Time)) %>%
  arrange(IDPET, Time) %>%
  group_by(IDPET,PROTOCOL) %>%
  nest(.key="aif") %>%
  ungroup()
  
```

### FengConv -> aif_data


```{r}
# Extract Data
aif_data <- data_aif_combined %>%
  ungroup() %>% 
  select(IDPET, aif) %>% 
  mutate(aif = map(aif, ~.x %>% 
                     rename(time= Time,
                            aif = AIF) %>%
                     ungroup() %>% 
                     mutate(Method = "Discrete"))) 

aif_data <- aif_data %>%
  mutate(aif_fit = map(aif, ~blmod_fengconv(time = .x$time, activity = .x$aif)))

# Make Predictions
mintime <- 0
maxtime <- max(map_dbl(aif_data$aif, ~max(.x$time)))
predtimes <- seq(from=mintime, to=maxtime, length.out=6000)

aif_data <- aif_data %>%
  mutate(preds = map(aif_fit, ~tibble(
    time = predtimes) %>%
      mutate(aif = predict(.x, newdata=list(time=time)))))

# Plot
pmap(list(aif_data$aif, aif_data$preds, aif_data$IDPET), plot_aif_preds)

```

### Feng

```{r}
aif_data_feng <- data_aif_combined %>%
  ungroup() %>% 
  select(IDPET, aif) %>% 
  mutate(aif = map(aif, ~.x %>% 
                     rename(time= Time,
                            aif = AIF) %>%
                     ungroup() %>% 
                     mutate(Method = "Discrete"))) 

aif_data_feng <- aif_data_feng %>%
  mutate(aif_fit = map(aif, ~blmod_feng(time = .x$time, activity = .x$aif)))

# Make Predictions
mintime <- 0
maxtime <- max(map_dbl(aif_data_feng$aif, ~max(.x$time)))
predtimes <- seq(from=mintime, to=maxtime, length.out=6000)

aif_data_feng <- aif_data_feng %>%
  mutate(preds = map(aif_fit, ~tibble(
    time = predtimes) %>%
      mutate(aif = predict(.x, newdata=list(time=time)))))

# Plot
pmap(list(aif_data_feng$aif, aif_data_feng$preds, aif_data_feng$IDPET), plot_aif_preds)
```

### Plot AIF, Feng, FengConv

```{r}
aif_data_plot <- aif_data %>% 
  slice(5) %>% 
  rename(preds_FC = preds) %>% 
  select(preds_FC, IDPET, aif) %>% 
  left_join(aif_data_feng)
```

```{r}
plot_aif_intro <- ggplot() +
  geom_point(data = aif_data_plot %>% ungroup() %>% select(aif) %>% unnest(aif) %>% ungroup(), 
             aes(x = time, y = aif, colour = "Arterial blood samples")) +
  geom_line(data = aif_data_plot %>% ungroup() %>% select(preds_FC) %>% unnest(preds_FC) %>% ungroup(), 
            aes(x = time, y = aif, colour = "AIF with FengConv")) +
  geom_line(data = aif_data_plot %>% ungroup() %>% select(preds) %>% unnest(preds) %>% ungroup(), 
            aes(x = time, y = aif, colour = "AIF with Feng")) +
  scale_color_manual(
    values = c(
      "Arterial blood samples" = "black",
      "AIF using FengConv"      = "blue",
      "AIF using Feng"          = "red"
    )
  ) +
  xlim(0, 10) + 
  labs(title = "Arterial input functions (for one subject)",
       colour = "",
       x = "Time (in minutes)",
       y = "Radioligand concentration (in MBq)")

plot_aif_intro
ggsave("aifIntro.pdf", plot = plot_aif_intro, width = 10, height = 7, dpi = 300)
```

## WB (after 3 min)

Here I'll take the WB, and convert it to MBq.

```{r}
wbdat <- dat %>% 
  filter(Type=="WB") %>% 
  mutate(wb = map(filename, read_csv, show_col_types = FALSE)) %>% 
  mutate(wb = map(wb, ~{
  minutes_pos <- which(names(.x) == "Unit")
  .x %>%
    mutate(across((minutes_pos + 1):ncol(.x), as.character)) %>%
    pivot_longer(
      cols = (minutes_pos + 1):ncol(.x),  # all columns after 'Unit'
      names_to = "col",
      values_to = "value"
    ) %>%
    pivot_wider(id_cols = c(PATIENTID, INJECTIONID, PSTATE, col),
                names_from = Variable,
                values_from = value) %>%
    rename (Time = t, WB = y1)%>%
    mutate(Time = as.numeric(Time),
           WB = as.numeric(WB) / 1000) %>%
    select(-col)
})) %>%
    unnest(wb) %>%
    ungroup() %>%
    mutate(IDPET = paste(PATIENTID,INJECTIONID, sep="_")) %>%
    select(-Type, -filename,-PATIENTID,-INJECTIONID) %>%
    filter(!is.na(Time) & !is.na(WB)) %>%
    group_by(IDPET,PSTATE) %>% 
    nest(.key="wb") %>%
    mutate(wb = map(wb, ~{
      .x %>%
        group_by(Time) %>%
        summarise(WB = mean(WB, na.rm = TRUE)) %>%
        ungroup()
    })) %>%
    unnest(wb) %>%
    ungroup() %>%
    group_by(IDPET,PSTATE) %>% 
    nest(.key="wb") %>%
    ungroup()
```

Let's plot a couple to be sure

```{r}
ggplot(wbdat$wb[[1]], aes(x=Time, y=WB)) +
  geom_point() +
  geom_line()

ggplot(wbdat$wb[[2]], aes(x=Time, y=WB)) +
  geom_point() +
  geom_line()
```

## BPR

### calc (after 3 min)

```{r}
data_BPR <- wbdat %>%
  inner_join(data_parentplasma) %>% 
  mutate(aif_calc=map(aif_calc, ~.x %>%
                    select(Time, PLASMA))) %>%
  mutate(combined = map2(aif_calc, wb, ~left_join(.x, .y, by = "Time"))) %>%
  select(IDPET,combined) %>%
  unnest(combined) %>%
  ungroup() %>%
  rename(time=Time) %>%
  mutate(bpr=WB/PLASMA) %>%
  mutate(across(where(is.character), as.factor))
```

### Fitted (after 3 min)

```{r}
# Fit Model

bpr_hgam_fit <- mgcv::gam(
  formula = as.formula(bpr ~ s(time, k=8) + s(time, IDPET, bs='fs', k=5)),
  data    = data_BPR,
  method  = "REML",
  family  = scat()
)

# Diagnostics
k.check(bpr_hgam_fit)
```

```{r}
appraise(bpr_hgam_fit)
```

```{r}
data_BPR_nested <- data_BPR %>%
  group_by(IDPET) %>%
  nest(.key="bpr")
```

### Preds

```{r}
# Make Predictions
mintime <- 0
maxtime <- max(map_dbl(data_BPR_nested$bpr, ~max(.x$time)))
predtimes <- seq(from=mintime, to=maxtime, length.out=1000)

# hgam_preds <- tidyr::expand_grid(data_BPR_nested,
#                                  time = predtimes)
hgam_preds <- tidyr::expand_grid(
  data_aif_combined %>% select(IDPET),
  time = predtimes
)

hgam_preds <- gratia::fitted_values(bpr_hgam_fit, data=hgam_preds) %>% 
  rename(bpr = .fitted) 

bpr_data <- inner_join(data_BPR_nested,
                      hgam_preds %>% 
                      group_by(IDPET) %>% 
                      nest(preds = -IDPET))

# Plot
pmap(list(bpr_data$bpr, bpr_data$preds, bpr_data$IDPET), plot_bpr_preds)
```

## Plasma, Blood 

### calc

```{r}
# Plasma = AIF / ParentFraction
# Blood = Plasma * BPR
input_calc <- data_aif_combined %>% 
  inner_join(parentdat) %>%
  mutate(parent = map2(aif, parent, ~{
    parent_interp <- approx(
      x = .y$Time,
      y = .y$PARENT,
      xout = .x$Time,
      method = "linear"
    )
    .x %>%
      mutate(PARENT = parent_interp$y) %>%
      select(Time,PARENT)
  })) %>%
  inner_join(bpr_data) %>%
  mutate(bpr = map2(aif, preds, ~{
    bpr_interp <- approx(
      x = .y$time,
      y = .y$bpr,
      xout = .x$Time,
      method = "linear"
    )
    .x %>%
      mutate(BPR = bpr_interp$y) %>%
      select(Time,BPR)
  })) %>%
  select(-preds) %>% 
  mutate(plasma_calc = map2(aif,parent, ~{
    left_join(.x, .y, by = "Time") %>%
      mutate(PLASMA = AIF/PARENT) %>%
      select(Time, PLASMA)
  })) %>%
  mutate(blood_calc = pmap(list(aif,parent,bpr), ~{
    left_join(..1, ..2, by = "Time") %>%
      left_join(..3, by = "Time") %>%
      mutate(WB = AIF/PARENT*BPR) %>%
      select(Time, WB)
  }))
  
```

### Join (/~3 min)

```{r}
plasma_blood_combined <- input_calc %>%
  select(-PROTOCOL) %>% 
  inner_join(plasmadat_final, by = join_by(IDPET)) %>%
  select(-PROTOCOL) %>% 
  mutate(plasma_comb = map2(plasma_calc, plasma, ~{
    smallest_time_raw_data <- min(.y$Time)
    bind_rows(.y %>% select(Time,PLASMA), .x %>% 
      filter(as.numeric(Time)<smallest_time_raw_data) %>% 
        select(Time,PLASMA)) %>% 
      arrange(Time)
  })) %>% 
  inner_join(wbdat, by = join_by(IDPET)) %>%
  mutate(blood_comb = map2(blood_calc, wb, ~{
    smallest_time_raw_data <- min(.y$Time)
    bind_rows(.y %>% select(Time,WB), .x %>% 
      filter(as.numeric(Time)<smallest_time_raw_data) %>% 
        select(Time,WB)) %>% 
      arrange(Time)
  })) %>%
  select(IDPET,plasma_comb,blood_comb) %>%
  rename(plasma = plasma_comb,
         blood = blood_comb)
```

## input (blood_interp)

```{r}
input <- plasma_blood_combined %>%
  inner_join(aif_data) %>%
  inner_join(parentdat) %>%
  select(-aif, -aif_fit) %>%
  rename(aif = preds) 

df_input <- input %>%
  mutate(input_wrong = pmap(list(aif, parent, plasma, blood), ~{
    
    blood_interp(
      t_blood      = ..4$Time,
      blood        = ..4$WB,
      t_plasma     = ..3$Time,
      plasma       = ..3$PLASMA,
      t_parentfrac = ..2$Time,
      parentfrac   = ..2$PARENT#,
      #t_aif        = aif_trimmed$time,
      #aif          = aif_trimmed$aif
    )
  })) %>% 
  mutate(aif=map(aif, ~.x %>% 
                   rename(Time=time))) %>% 
  mutate(input = map2(input_wrong, aif, ~{
    left_join(.x, .y, by = "Time") %>%
      mutate(AIF_new= ifelse(is.na(aif),AIF,aif)) %>% 
      select(-AIF, -aif) %>% 
      rename(AIF=AIF_new)
  })) %>% 
  select(-input_wrong)

saveRDS(df_input, "/home/lisatjarks/Repositories/Yale_data/DerivedData/input.rds")

```

```{r}
input <- readRDS("../DerivedData/input.rds")
```



## TACs

Here I'll extract the TACs, and convert to MBq.

```{r}
tac <- dat %>% 
  filter(Type=="TAC") %>% 
  mutate(tac = map(filename, read_csv, show_col_types = FALSE)) %>% 
  mutate(tac = map(tac, ~{
  minutes_pos <- which(names(.x) == "Unit")
  .x %>%
    mutate(ROIsize = case_when(
      !is.na(as.numeric(FINAL_ROI_VOLUME)) ~ as.numeric(FINAL_ROI_VOLUME),  # ROIsize is already numeric
      !is.na(as.numeric(VARIABLEUNITS)) ~ as.numeric(VARIABLEUNITS),  # ROIsize value in wrong column
      TRUE ~ NA_real_ )) %>%
    mutate(across((minutes_pos + 1):ncol(.x), as.character)) %>%
    pivot_longer(
      cols = (minutes_pos + 1):ncol(.x),  # all columns after 'Unit'
      names_to = "col",
      values_to = "value"
    ) %>%
    pivot_wider(id_cols = c(PATIENTID, INJECTIONID,CURVENAME, ANALYSISID, ROIsize,PSTATE, PROTOCOL, SECONDARY_DIAGNOSIS, Seriesdescription, SERIESID, col),
                names_from = Variable,
                values_from = value) %>%
    rename (frame_mid = t, TAC = y1) %>%
    mutate(frame_mid = as.numeric(frame_mid),
           TAC = as.numeric(TAC) / 1000) %>%
    filter(!is.na(frame_mid)) %>% 
    select(-col)
})) %>%
    unnest(tac) %>%
    mutate(IDPET = paste(PATIENTID,INJECTIONID, sep="_")) %>%
    mutate(frame_mid = ifelse(
      IDPET == "LC224_12839" & abs(frame_mid - round(frame_mid, 2)) < 1e-4,
      round(frame_mid, 2),
      frame_mid
    )) %>%
    rename(Region = CURVENAME) %>%
    select(-Type, -filename,-PATIENTID,-INJECTIONID) %>%
    group_by(IDPET, PSTATE, SECONDARY_DIAGNOSIS,PROTOCOL) %>% 
    nest(.key="tac") %>%
    mutate(tac =map(tac, ~.x %>%
                    group_by(Region, ANALYSISID,ROIsize,Seriesdescription,SERIESID) %>%
                    nest(.key="tac_inside")))
```

### Genotypes (Nakul)

```{r}
genotypes <- tac %>% 
  ungroup() %>% 
  select(IDPET, SECONDARY_DIAGNOSIS) %>%
  mutate(ID = str_extract(IDPET, "^[^_]+")) %>%
  select(ID, SECONDARY_DIAGNOSIS) %>%
  ungroup() %>% 
  rename(Genotype = SECONDARY_DIAGNOSIS) %>%
  mutate(Genotype= ifelse(str_detect(Genotype, "N/A")| str_detect(Genotype,"Major"),NA,Genotype)) %>% 
  arrange(Genotype,ID) %>% 
  distinct()
```



```{r}
genotype_comb <- aifdat %>% 
  ungroup() %>% 
  mutate(ID = str_extract(IDPET, "^[^_]+")) %>%
  select(ID) %>% 
  inner_join(genotypes) %>%
  mutate(Genotype= ifelse(str_detect(Genotype, "N/A")| str_detect(Genotype,"Major"),NA,Genotype)) %>% 
  arrange(Genotype,ID) %>% 
  select(Genotype,ID) %>% 
  distinct() %>% 
  rename(PATIENTID = ID)

write.csv(genotype_comb, "Genotype.csv")
```


### durations
preparing for SiMBA
we need to check that the duration is not too far apart

```{r}

manual_ceiling(30.65, -5)  
```


```{r}
#general structure of dataset tac:
#we have here the data, with ID,PET,ANALYSISID,PSTATE,nest="tac" 
    #nest="tac" including Region,ANALYSISID,ROIsize,nest="tac"
      #nest="tac" including frame_mid, TAC

manual_ceiling <- function(value, significance){
  val <- ceiling(value / significance) * significance
  return(val)
}


#this function gets data within one ID,one PET, but several regions
#general idea: do that only for the first region within every PET/ID, 
#this funtion: first region of this PET/ID, and then map this function to each PET/ID-pair
calc_dur <- function(nested_tac){
  
  data <- nested_tac %>%
    ungroup() %>%
    slice(1) %>% #selecting first data point (calculating only for the first region)
    unnest(tac_inside) %>%
    mutate(frame_mid,
           frame_start=0,
           frame_end =120,
           dur=NA)
  
  regular <- TRUE  # check flag
  
  # first frame
  data$frame_start[1] <- data$frame_mid[1]-0.25
  data$frame_end[1] <- data$frame_mid[1]+0.25
  data$dur[1] <- 0.5
  
  for (i in 2:length(data$frame_mid)){
    
    # calculating dur, start and end 
    calc_start <- case_when(
      data$frame_mid[i] < 3  ~ manual_ceiling(data$frame_mid[i], -0.5),
      data$frame_mid[i] < 6  ~ manual_ceiling(data$frame_mid[i], -1),
      data$frame_mid[i] < 10 ~ manual_ceiling(data$frame_mid[i], -2),
      TRUE                   ~ manual_ceiling(data$frame_mid[i], -5)
    )
    
    calc_end <- case_when(
      data$frame_mid[i] < 3  ~ manual_ceiling(data$frame_mid[i], 0.5),
      data$frame_mid[i] < 6  ~ manual_ceiling(data$frame_mid[i], 1),
      data$frame_mid[i] < 10 ~ manual_ceiling(data$frame_mid[i], 2),
      TRUE                   ~ manual_ceiling(data$frame_mid[i], 5)
    )
    
    # should just flag if the end[i-1] was different; meaning here we correct the start after an irregular frame
    if (!(calc_start == data$frame_end[i-1]) | !(data$frame_mid[i] %% 0.25 == 0)){
      regular <- FALSE
    }
    
    data$frame_start[i] <- calc_start
    data$frame_end[i] <- min(c(data$frame_start[i] + (data$frame_mid[i]-data$frame_start[i])*2 ,calc_end))
    data$dur[i] <- data$frame_end[i] - data$frame_start[i]
    
    if (is.na(data$frame_mid[i+1])) break 
  }
  data <- data %>% 
    filter(!is.na(dur)) %>%
    ungroup() %>%
    select(frame_mid,frame_start,frame_end,dur)
  
  if(any(data$dur == 0, na.rm = TRUE)) regular <- FALSE
  
  return(list(tacs_dur = data, regular = regular))
}

#apply that function for all the ID,PET pairs
tac_dur <- tac %>%
    mutate(result = map(tac, calc_dur),
           tacs_dur = map(result, "tacs_dur"),
           regular = map_lgl(result, "regular")) %>%
    select(-result)
```

and then copy to other regions of same PET/ID
  copy the duration also into the nests of the other regions

```{r}
tac_dur_final <- tac_dur %>%
  mutate(tac = map2(tac, tacs_dur, ~ {
    .x %>%
      mutate(tac_inside = map(tac_inside, function(inner) {
        left_join(inner, .y, by = "frame_mid")
      }))
  })) %>%
  select(-tacs_dur)
```

filtering for the TACs where everything went fine

```{r}
tac_regular <- tac_dur_final %>%
  filter(regular)
tac_irregular <- tac_dur_final %>%
  filter(!regular)
```


### Region
#### cleaning

```{r}
data_roi <- tac_dur_final %>%
  unnest(tac) %>%
  ungroup() %>%
  #select(ID,PET,ANALYSISID, ROIsize, Region) %>%
  mutate(Region_spec =Region,
         Region_spec = paste0(toupper(substr(Region_spec, 1, 1)), substr(Region_spec, 2, nchar(Region_spec))),
         Region = ifelse(str_detect(Region, "semiovale"), "C_semiovale", ifelse(str_detect(Region, "insula"),"Insula", str_extract(Region_spec, "^[^_]+"))),
         Region = paste0(toupper(substr(Region, 1, 1)), substr(Region, 2, nchar(Region))),
         variant_PVC = ifelse(str_detect(Region_spec,"PVC")|str_detect(Region_spec,"pvc"),TRUE,FALSE),
         variant_WM = ifelse(str_detect(Region_spec,"WM")|str_detect(Region_spec,"wm"),TRUE,FALSE),
         variant_GM = ifelse(str_detect(Region_spec,"GM")|str_detect(Region_spec,"gm"),TRUE,FALSE),
         variant_PET = ifelse(str_detect(Region_spec,"PET")|str_detect(Region_spec,"pet"),TRUE,FALSE),
         variant_SPM = ifelse(str_detect(Region_spec,"SPM")|str_detect(Region_spec,"spm"),TRUE,FALSE),
         variant_ANT = ifelse(str_detect(Region_spec,"ANT")|str_detect(Region_spec,"ant")|str_detect(Region_spec,"Ant"),TRUE,FALSE),
         variant_CAT = ifelse(str_detect(Region_spec,"CAT")|str_detect(Region_spec,"cat"),TRUE,FALSE),
         variant_POST = ifelse(str_detect(Region_spec,"Post"),TRUE,FALSE)
         )  %>%
  mutate(Region = ifelse(variant_ANT,paste(Region,"Ant", sep = "_"),Region),
         Region = ifelse(variant_POST,paste(Region,"Post", sep = "_"),Region)) %>%
  select(-variant_ANT,-variant_POST) %>%
  mutate(variant_regular = !if_any(variant_PVC:variant_CAT, ~ .))

# table(data_roi$Region_spec)
# table(data_roi$Region)
```

#### Analysis
##### counts per Region

```{r}
data_roi_no_duplicates <- data_roi[!duplicated(data_roi[, c("IDPET", "Region_spec")]), ]

long_data <-  data_roi_no_duplicates %>%
  pivot_longer(
    cols = starts_with("variant_"),
    names_to = "variant",
    values_to = "flag"
  ) 

data_counts <- long_data %>%
  filter(flag) %>%                         # keeps true, which shoudl not change things here
  group_by(variant, Region) %>%
  summarise(n = n_distinct(IDPET), .groups = "drop")

data_counts_wide <- data_counts %>%
  pivot_wider(names_from = Region, values_from = n, values_fill = 0)
data_counts_wide
```

##### no regular PET

```{r}
no_regular <- data_roi_no_duplicates %>%
  group_by(IDPET, Region) %>%
  filter(!any(variant_regular)) %>%
  ungroup() %>%
  group_by(Region) %>%
  nest(.key = "missing")
no_regular
```

##### regular

```{r}
regular <- data_roi %>%
  group_by(IDPET, Region) %>%
  filter(any(variant_regular)) %>%
  filter(Region==Region_spec) %>%
  mutate(count=n()) %>%
  filter(count >= 2) %>%
  ungroup() %>% 
  group_by(IDPET,Region, Seriesdescription, SERIESID) %>%
  nest(.key = "regular") %>%
  ungroup() %>% 
  filter(!str_detect(Seriesdescription, "pvc")) %>%
  group_by(IDPET,Region) %>% 
  mutate(count=n()) %>% 
  filter(!count==1)
```

##### without pvc

```{r}
regular_new <- data_roi %>%
  group_by(IDPET, Region) %>%
  filter(any(variant_regular)) %>%
  filter(Region==Region_spec) %>%
  mutate(count=n()) %>%
  filter(count >= 2) %>%
  ungroup() %>% 
  filter(!str_detect(Seriesdescription, "pvc")) %>%
  group_by(IDPET,Region) %>% 
  filter(!any(variant_regular)) %>%
  ungroup() %>%
  group_by(Region) %>%
  nest(.key = "missing")
regular_new
```

```{r}
no_regular_new <- data_roi %>%
  filter(!str_detect(Seriesdescription, "pvc")) %>%
  group_by(IDPET, Region) %>%
  filter(!any(variant_regular)) %>%
  ungroup() %>%
  group_by(Region) %>%
  nest(.key = "missing")
no_regular_new
```

##### doubled

```{r}
doubled <- data_roi %>%
  group_by(IDPET, Region) %>%
  filter(sum(variant_regular) >= 2) %>%
  filter(variant_regular) %>%
  ungroup() %>%
  group_by(Region) %>%
  nest(.key = "missing")
doubled
```

#### ROImean

getting a feeling for how big the variation between individuals
```{r}
data_roi %>%
  filter(!str_detect(Region, "semiovale")) %>% 
  filter(!variant_GM) %>% 
  filter(!is.na(ROIsize)) %>%
  group_by(Region_spec) %>%
  summarise(mean_ROIsize = mean(as.numeric(ROIsize)),
            min_val = min(ROIsize),
            max_val = max(ROIsize))
```

 mean roi size onlz calculated on values from the vanilla regions
 
```{r}
 mean_roi <- data_roi %>%
  filter(!str_detect(Seriesdescription, "pvc")) %>% 
  filter(!is.na(ROIsize)) %>%
  filter(Region==Region_spec) %>% 
  group_by(Region) %>%
  summarise(mean_ROIsize = mean(ROIsize))
```

join the mean roi to the data 

```{r}
data_roi_final <- data_roi %>% 
  left_join(mean_roi, by = "Region") %>%
  ungroup()
```

#### SUV for Region_spec

```{r}
# assuming data_roi_final already to be unnested
data_SUV <- data_roi_final %>%
  inner_join(demog) %>%
  unnest(demog) %>%
  select(IDPET, ANALYSISID, Region, Region_spec, InjRad_SUV, tac_inside) %>%
  unnest(tac_inside)

for (i in unique(data_SUV$Region)){
   plot <- data_SUV %>% filter(Region==i) %>%
  ggplot(aes(x = frame_mid, y = TAC/InjRad_SUV, colour = Region_spec)) +
  geom_point() +
  geom_line() +
    labs(title = i)
   
   print(plot)
}

for (i in unique(data_SUV$Region)){
  plot <- data_SUV %>% 
    filter(Region == i) %>%
    ggplot(aes(x = frame_mid, y = TAC/InjRad_SUV, 
               colour = Region_spec, group = interaction(IDPET,ANALYSISID, Region_spec))) +
    geom_point(alpha = 0.3, size = 0.8) +
    geom_line(alpha = 0.5) +
    labs(title = i) +
    theme_minimal()
  
  print(plot)
}
```

```{r}
# assuming data_roi_final already to be unnested
data_SUV_main_regions <- data_roi_final %>%
  inner_join(demog) %>%
  unnest(demog) %>%
  select(IDPET, ANALYSISID, Region, Region_spec, InjRad_SUV, tac_inside) %>%
  filter(Region==Region_spec) %>% 
  group_by(IDPET,Region) %>%
  mutate(count=n()) %>%
  filter(count >= 2) %>%
  ungroup() %>% 
  slice(1:100) %>% 
  unnest(tac_inside)

for (i in unique(data_SUV$Region)){
  plot <- data_SUV_main_regions %>% 
    filter(Region == i) %>%
    ggplot(aes(x = frame_mid, y = TAC/InjRad_SUV, 
               colour = IDPET, group = interaction(IDPET,ANALYSISID))) +
    geom_point(alpha = 0.3, size = 0.8) +
    geom_line(alpha = 0.5) +
    labs(title = i) +
    theme_minimal()
  
  print(plot)
}
```

#### final 9 Regions

```{r}
data_roi_final_regions <- data_roi_final %>% 
  #choosing that i dont have duplicated Regions_specs
  filter(!str_detect(Seriesdescription, "pvc")) %>% 
  filter(!(IDPET=="LC224_12839" & Seriesdescription=="pbr28_motcor_mc")) %>% 
  filter(!(IDPET=="PM790_15603" & Seriesdescription=="pbr28_2_motcor_mc")) %>% 
  filter(!(IDPET=="LV675_6899" & Seriesdescription=="pbr28_vc2_mc")) %>% 
  # just vanilla regions
  filter(Region==Region_spec) %>% 
  #choose only the ROIs of interest
  filter(!Region=="Orbitofrontal", !Region=="Insula", !Region=="C_semiovale", !Region=="Caudate", !Region=="Hypothalamus",
         !Region=="Cingulum_Ant")
```

```{r}
table(data_roi_final_regions$Region)
```

joined with input that i know which data complete i have

```{r}
joined <- data_roi_final_regions %>% 
  inner_join(input) %>% 
  ungroup() %>% 
  group_by(IDPET) %>% 
  filter(!any(Region=="Amygdala"))
table(joined$Region)
```

### plot tac

```{r}
tac_plot <- data_roi_final_regions %>% 
  ungroup() %>% 
  group_by(IDPET) %>% 
  nest() %>% 
  ungroup() %>% 
  slice(5) %>% 
  unnest(data) %>% 
  unnest(tac_inside) %>% 
  ggplot(aes(x = frame_mid, y = TAC, colour = Region)) + 
   geom_point() +
   geom_line() + 
     labs(title = "Time Activity Curve (for one subject)",
          colour = "Region of interest",
          x= "Time (in minutes)",
          y = "Radioligand concentration (in MBq)") 
tac_plot
ggsave("tacIntro.pdf", plot = tac_plot, width = 10, height = 7, dpi = 300)
```

### Weights

```{r}
tac_dur_weights <- data_roi_final_regions %>% 
  mutate(tac_inside = map(tac_inside, ~.x %>%
              mutate(TAC = as.numeric(TAC),
                     frame_mid = as.numeric(frame_mid),
                     weights = weights_create(tac = TAC,
                                              t_start = frame_start,
                                              t_end = frame_end,
                                              radioisotope = "C11",
                                              minweight = 0.3,
                                              weight_checkn = 5)))) %>%
  group_by(IDPET) %>%
  nest(.key= "tac")

#i think this is the same but not sure
# tac_dur_weights <- data_roi_final %>% 
#   unnest(tac_inside) %>%
#   ungroup() %>%
#   mutate(TAC = as.numeric(TAC),
#          frame_mid = as.numeric(frame_mid)) %>%
#   group_by(IDPET) %>% 
#   nest(.key="tac") %>%
#   ungroup() %>%
#   mutate(tac = map(tac, ~.x %>% 
#                                   mutate(weights = weights_create(tac = TAC,
#                                                                   t_start = frame_start,
#                                                                   t_end = frame_end,
#                                                                   radioisotope = "C11",
#                                                                   minweight = 0.3,
#                                                                   weight_checkn = 5)))) %>%
#   ungroup() %>%
#   mutate(tac =map(tac, ~.x %>%
#                     group_by(Region, Region_spec, ANALYSISID,ROIsize) %>%
#                     nest(.key="tac_inside")))
```

```{r}
# check_weights that they are non-neg, in the ranges that we want them to be in
tac_dur_weights %>%
  unnest(tac) %>%
  unnest(tac_inside) %>%
  ungroup() %>%
  summarise(min = min(weights),
            max= max(weights))
```



# Join -> modeldat

```{r}
modeldat <- tac_dur_weights %>%
  inner_join(df_input) %>%
  ungroup() #%>%
#  mutate(tac = map(tac, ~.x %>%
#                     ungroup() %>%
#                     group_by(ANALYSISID) %>%
#                     nest(.key="tac_inside") %>%
#                     ungroup()))
saveRDS(modeldat, "/home/lisatjarks/Repositories/Yale_data/DerivedData/modeldat.rds")
```

```{r}
modeldat <- readRDS("../DerivedData/modeldat.rds")
```


## delay fitting

### one tac

```{r}
test_tac <- modeldat %>%
  ungroup() %>%
  slice(1) %>%
  mutate(tac = map(tac, ~.x %>%
                     slice(1) %>%
                     unnest(tac_inside) %>%
                     ungroup())) %>%
  select(tac) %>%
  unnest(tac) %>%
  ungroup()
test_input <- modeldat %>%
  ungroup() %>%
  slice(1) %>%
  select(input_df) %>%
  unnest(input_df) %>%
  ungroup()
```

```{r}
test <- onetcm(
  t_tac  = as.numeric(test_tac$frame_mid),
  tac    = as.numeric(test_tac$TAC),
  input  = test_input,
  vB     = 0.05,
  multstart_iter = 10,
  inpshift.lower = -1,
  timeStartEnd = c(0,5)
)
```

### all tacs

we fit for the Regions 

```{r}
plan(multicore, workers = 3)

delay_fits <- modeldat %>% 
  ungroup() %>% 
  mutate(tac = map(tac, ~.x %>% 
                     unnest(tac_inside) %>% 
                     filter(Region=="Frontal" | Region== "Putamen" |Region== "Cerebellum" | Region== "Hippocampus" |Region== "Temporal"| Region== "Amygdala" ) %>% 
                     ungroup())) %>% 
  mutate(delayFit = map2(tac, input, ~onetcm(.x$frame_mid, .x$TAC, .y, 
                                                     vB = 0.05, 
                                                     multstart_iter = 10,
                                                     inpshift.lower = -1,
                                                     #weights=.x$weights,
                                                     timeStartEnd = c(0,5)))) #%>% 
  #mutate(inpshift = map_dbl(delayFit, c("par", "inpshift")))

saveRDS(delay_fits, "/home/lisatjarks/Repositories/Yale_data/DerivedData/delay_fits.rds")
```


```{r, warning=FALSE, eval=TRUE}
plan(multicore, workers = 3)

delay_fits <- modeldat %>%
  ungroup() %>%
  mutate(delayFit = map2(tac, input, ~{
    input <- .y
    .x %>%
      filter(Region=="Frontal" | Region== "Putamen" |Region== "Cerebellum" | Region== "Hippocampus" |Region== "Temporal"| Region== "Amygdala" )%>%  
      #Regions that i want to fit the regions to. maybe i have to unnest then and fit the delay within teh whole/all regions together
      mutate(fit = map(tac_inside, function(analysisID){
        #analysisID_clean <- analysisID %>%
         # filter(!is.na(frame_mid), frame_mid != 0, !is.na(TAC))
        onetcm(
          t_tac  = analysisID$frame_mid,
          tac    = analysisID$TAC,
          input  = input,
          vB             = 0.05,
          multstart_iter = 10,
          inpshift.lower = -1,
          timeStartEnd = c(0,5)
        )
      })) #%>%
      #mutate(inpshift = map_dbl(fit, ~.x$par$inpshift))
  })) #%>%
  # mutate(inpshift = map(delayFit, ~{
  #   map_dbl(.x$fit, ~.x$par$inpshift)
  # }))

saveRDS(delay_fits, "/home/lisatjarks/Repositories/Yale_data/DerivedData/delay_fits.rds")
```


##### checking


```{r, fig.width=8, fig.height=8}
delay_fits <- readRDS("/home/lisatjarks/Repositories/Yale_data/DerivedData/delay_fits.rds") %>% 
  select(IDPET, delayFit) %>%
  unnest(delayFit) %>%
  #mutate(IDPETID = paste(IDPET, ANALYSISID, sep="_")) %>%
  #select(-ANALYSISID,-IDPET) %>%
  mutate(inpshift = map_dbl(fit, ~.x$par$inpshift)) 

ggplot(delay_fits, aes(x=inpshift)) +
  geom_histogram(fill="grey", colour="black") +
  facet_wrap(~IDPET)
```


##### refit with inpshift_median and get Regions,input

```{r}
delay_fits_median <- delay_fits %>%
  group_by(IDPET) %>% 
  mutate(inpshift_median = median(inpshift)) %>%
  ungroup() %>%
  inner_join(input) %>%
  select(IDPET, SERIESID, Seriesdescription, Region, inpshift, inpshift_median, tac_inside,input)
```

```{r, warning=FALSE, eval=TRUE}
# plan(multisession, workers = 8)
# 
# fit_delayPlot <- function(tacdata, input, inpshift) {
#   onetcm(tacdata$frame_mid, tacdata$TAC, input = input, 
#              inpshift = inpshift,
#              frameStartEnd = c(1,8))#,
#              #weights=tacdata$weights)
# }
# 
# 
# delay_fitplots <- delay_fits_median %>% 
#   filter(Region=="Frontal") %>% 
#   ungroup() %>% 
#   mutate(delayPlotFit = future_pmap(list(tac_inside, input_df, inpshift_median), 
#                                     fit_delayPlot))
```

```{r}
delay_fitplots <- delay_fits_median %>% 
  filter(Region=="Frontal") %>% 
  ungroup() %>% 
  mutate(delayPlotFit = pmap(list(tac_inside, input, inpshift_median), 
                             function(tacdata, input, inpshift){
                                 onetcm(tacdata$frame_mid, tacdata$TAC, 
                                        input    = input, 
                                        inpshift = inpshift,
                                        multstart_iter = 10,
                                        vB=0.05,
                                        frameStartEnd = c(1,8),
                                        weights = tacdata$weights)
                             }))


```


Now let's see how they look.

```{r}
map(delay_fitplots$delayPlotFit, plot)
```


Happy with that!  Let's attach that to the modeldat object

```{r}
modeldata_final <- delay_fits_median %>% 
  select(IDPET,inpshift_median) %>%
  distinct() %>%
  inner_join(modeldat)
```

## add genotype

```{r}
genotype <- read_excel("/home/lisatjarks/Repositories/Yale_data/RawData/Genotype_NRR.xlsx") %>%
  mutate(Genotype = ifelse(Genotype=="C/C", "HAB",ifelse(Genotype=="C/T","MAB",Genotype))) 
diagnosis <- dat %>% 
  filter(Type=="TAC") %>% 
  mutate(tac = map(filename, read_csv, show_col_types = FALSE)) %>%
  unnest(tac) %>% 
  select(PATIENTID, DIAGNOSIS, SECONDARY_DIAGNOSIS) %>% 
  distinct() %>%
  inner_join(genotype) %>% 
  mutate(DIAGNOSIS= ifelse(str_detect(SECONDARY_DIAGNOSIS, "Major"),paste(DIAGNOSIS, "2nd_MDD", sep = "_"),DIAGNOSIS)) %>% 
  select(PATIENTID, DIAGNOSIS, Genotype) %>% 
  filter(!(PATIENTID=="AS525" & DIAGNOSIS=="Healthy Control")) %>% #this one was doubled, with healthy nonsmoker and control
  mutate(DIAGNOSIS = ifelse(str_detect(DIAGNOSIS, "lcohol"),"ALC",
                            ifelse(str_detect(DIAGNOSIS, "epress"), "MDD",
                                   ifelse(str_detect(DIAGNOSIS, "ealth"),"HC",DIAGNOSIS)))) %>% 
  arrange(PATIENTID, DIAGNOSIS, Genotype) 

fengconv_vals <- aif_data %>% 
  select(IDPET,aif_fit) %>% 
  #unnest(aif_fit) %>% 
  mutate(A = map_dbl(aif_fit, ~.x$par$A),
         alpha = map_dbl(aif_fit, ~.x$par$alpha),
         B = map_dbl(aif_fit, ~.x$par$B),
         beta = map_dbl(aif_fit, ~.x$par$beta),
         C = map_dbl(aif_fit, ~.x$par$C),
         gamma = map_dbl(aif_fit, ~.x$par$gamma),
         t0 = map_dbl(aif_fit, ~.x$par$t0),
         ti = map_dbl(aif_fit, ~.x$par$ti)
         ) %>% 
  select(-aif_fit)

modeldata_genotype <- modeldata_final %>% 
  mutate(PATIENTID = str_extract(IDPET, "^[^_]+")) %>%
  inner_join(diagnosis) %>% 
  select(-aif,-plasma,-parent,-blood, -PATIENTID) %>%
  unnest(tac) %>% 
  ungroup() %>% 
  select(IDPET, inpshift_median, Genotype, DIAGNOSIS, input, PSTATE, PROTOCOL, Region, Seriesdescription, SERIESID, tac_inside,mean_ROIsize) %>% 
  inner_join(fengconv_vals)

```

## clean diagnosis

```{r}
cleaned_modeldat <- modeldata_genotype %>% 
  mutate(DIAGNOSIS = ifelse(is.na(DIAGNOSIS) & str_detect(PROTOCOL,"alc"), "ALC",
                            ifelse(is.na(DIAGNOSIS) & str_detect(PROTOCOL, "ptsd"),"PTSD",DIAGNOSIS)))
table(cleaned_modeldat$DIAGNOSIS)
```




## save

```{r}
saveRDS(cleaned_modeldat, "/home/lisatjarks/Repositories/Yale_data/DerivedData/modeldata.rds")
```

###plots to check
Let's plot one to be sure

```{r}

for(i in 1:10) {
  
  a <- ggplot(tac_dur_final$tac[[i]]$tac_inside[[i]], aes(x=frame_mid_mod, y=TAC)) +
  geom_point() +
  geom_line()
  
  plot(a)
  
}


```

<!-- #### checking the different regions (gm, pvc,...) -->


<!-- ```{r} -->
<!-- data_tacdemog <- tac_new %>% -->
<!--   inner_join(demog) %>% -->
<!--   unnest(tac)%>% -->
<!--   unnest(tac) %>% -->
<!--   mutate(Region_spec =Region, -->
<!--          Region = str_extract(Region_spec, "^[^_]+"), -->
<!--          Region = paste0(toupper(substr(Region, 1, 1)), substr(Region, 2, nchar(Region))), -->
<!--          region_identifiable = paste0(Region_spec, ANALYSISID)) %>% -->
<!--   group_by(IDPET) %>% -->
<!--   nest(.key="data") -->
<!-- ``` -->

<!-- ```{r} -->
<!-- plot_data <- data_tacdemog %>% -->
<!--   filter(ID == "JL926") %>% -->
<!--   unnest(data) -->


<!-- for (i in unique(plot_data$Region)){ -->
<!--    plot <- plot_data %>% filter(Region==i) %>% -->
<!--   ggplot(aes(x = frame_mid, y = TAC, colour = region_identifiable)) + -->
<!--   geom_point() + -->
<!--   geom_line() + -->
<!--     labs(title = i) -->

<!--    print(plot) -->
<!-- } -->

<!-- ``` -->



<!-- ```{r} -->
<!-- plot_data <- data_tacdemog %>% -->
<!--   filter(ID == "AS525", PET=="12519") %>% -->
<!--   unnest(data) -->


<!-- for (i in unique(plot_data$Region)){ -->
<!--    plot <- plot_data %>% filter(Region==i) %>% -->
<!--   ggplot(aes(x = frame_mid, y = TAC, colour = region_identifiable)) + # -->
<!--   geom_point() + -->
<!--   geom_line() + -->
<!--     labs(title = i) -->

<!--    print(plot) -->
<!-- } -->

<!-- ``` -->

<!-- ```{r} -->
<!-- plot_data <- data_tacdemog %>% -->
<!--   filter(ID=="DF153", PET=="21094") %>% -->
<!--   unnest(data) -->


<!-- for (i in unique(plot_data$Region)){ -->
<!--    plot <- plot_data %>% filter(Region==i) %>% -->
<!--   ggplot(aes(x = frame_mid, y = TAC, colour = region_identifiable)) + #/InjRad_SUV -->
<!--   geom_point() + -->
<!--   geom_line() + -->
<!--     labs(title = i) -->

<!--    print(plot) -->
<!-- } -->

<!-- ``` -->



# TAC Fitting

```{r}
modeldat_forfitting <- readRDS("../DerivedData/modeldata.rds")
```

## Two-Tissue Compartment Model

Now let's fit all the TACs using the 2TC and the fitted delay values.

# get here the second map to catch the tac_inside instead of the tac
```{r, eval=TRUE}
fit_2tc <- function(tacdata, input, inpshift) {
  twotcm(tacdata$frame_mid, tacdata$TAC, input = input, 
             inpshift = inpshift,
             multstart_iter = 10,
             weights=tacdata$weights)
}

plan(multicore, workers = 8)

#if Time AIF>120, approx is NA

fits_2tc <- modeldat_forfitting %>% 
  ungroup() %>% 
  mutate(fit = future_pmap(list(tac_inside, input, inpshift_median), fit_2tc))

saveRDS(fits_2tc, "../DerivedData/2tc_fits.rds")
```


```{r}
pars_2tc <- readRDS("../DerivedData/2tc_fits.rds") %>% 
  pull(fit) %>% 
  map("par") %>% 
  bind_rows()

pars_2tc
```

Let's also take a look at the distributions

```{r}
pars_2tc %>% 
  gather("Parameter", "Value", -inpshift, -vB) %>% 
  ggplot(aes(x=Value, fill=Parameter)) +
  geom_histogram(colour="black") +
  facet_wrap(~Parameter, scales="free")

pars_2tc %>% 
  gather("Parameter", "Value", -inpshift, -vB) %>% 
  ggplot(aes(x=Value, fill=Parameter)) +
  geom_histogram(colour="black") +
  facet_wrap(~Parameter, scales="free") +
  scale_x_log10()
```


# Prepare for SiMBA

## Align AIF/TAC

```{r}
aifpars <- modeldat_forfitting %>% 
  mutate(t0_inpshift = t0 + inpshift_median)

aifpars_unnested <- aifpars %>% unnest(tac_inside)

ggplot(aifpars, aes(x=t0_inpshift)) +
  geom_histogram(colour="black", fill="grey") +
  geom_vline(xintercept=0, linetype="dashed")
```


## meanblood

```{r}
meanblood <- aifpars %>% 
  mutate(input = map2(input, inpshift_median, ~mutate(.x, Time = Time + .y)))
```

```{r}
add_meanblood <- function(input, tacs) {
  meanblood_vec <- map2_dbl(tacs$frame_start, tacs$frame_end, 
                             ~input %>% 
                               filter(Time >= .x) %>% 
                               filter(Time < .y) %>% 
                               pull(Blood) %>% 
                               mean())
  
  tacs %>% 
    mutate(meanblood = meanblood_vec)
}

meanblood <- meanblood %>% 
  mutate(tac_inside = map2(input, tac_inside, add_meanblood)) %>% 
  select(IDPET, tac_inside) %>% 
  unnest(tac_inside) %>% 
  filter(!duplicated(paste(IDPET, frame_start, frame_end))) %>% 
  select(IDPET, frame_mid, meanblood)

meanblood
```

Let's take a look at one of the curves

```{r}
meanblood %>% 
  filter(IDPET == IDPET[1]) %>% 
  #mutate(t_tac = frame_start + 0.5*(frame_end-frame_start)) %>% 
  ggplot(aes(x=frame_mid, y=meanblood)) +
  geom_line(colour="red") +
  geom_point()
```


Now let's add these back to the model data

```{r}
simba_modeldat <- aifpars %>% 
  unnest(tac_inside) %>% 
  inner_join(meanblood) %>% 
  select(-inpshift_median, -t0_inpshift)
```


## Region Sizes

The region sizes influence the measurement error, so we should add these to the model.  We calculated them earlier, but let's also log them and centre the logged values for the model.

```{r}
simba_modeldat <- simba_modeldat %>% 
  ungroup() %>% 
  mutate(logRegSize = log(mean_ROIsize),
         logRegSize_c = logRegSize - mean(logRegSize))
```


## Injected Radioactivity

The injected radioactivity is also a predictor of the measurement error.  Let's add this too.

```{r}
injection_info <- demog %>% 
  unnest(demog) %>% 
  ungroup() %>% 
  mutate(IDPET = paste(ID,PET,sep = "_")) %>% 
  select(-ID, -PET) %>% 
  mutate(logInjRad = log(InjRad),
         logInjRad_c = logInjRad - mean(logInjRad)) %>% 
  mutate(Age_dec = Age / 10,
         Age_dec_c = Age_dec - mean(Age_dec))

simba_modeldat <- simba_modeldat %>% 
  left_join(injection_info)
```

## Durations

Lastly, I know we already have the durations, but we want to include the centred log durations in our model, so let's add that here too

```{r}
simba_modeldat <- simba_modeldat %>% 
  mutate(logdur = log(dur),
         logdur_c = logdur - mean(logdur))
```

## clean LPS session

```{r}
LPS_cleaned <- simba_modeldat %>% 
  mutate(PATIENTID = str_extract(IDPET, "^[^_]+")) %>%
  select(PATIENTID, IDPET,PSTATE, SERIESID,Seriesdescription) %>% 
  distinct() %>% 
  group_by(PATIENTID) %>% 
  mutate(count=n()) %>%
  ungroup() %>% 
  arrange(PATIENTID, SERIESID, IDPET, PSTATE) %>% 
  mutate(LPS = ifelse(count>=2 & (str_detect(PSTATE, "pre") | str_detect(PSTATE,"base") | str_detect(PSTATE,"One")),"baseline",
                      ifelse(count>=2 & (str_detect(PSTATE, "ost")  | str_detect(PSTATE,"Two")),"post",
                             ifelse(count %% 2 & count>=2 & is.na(PSTATE), "post", NA)))) %>% 
  mutate(LPSpair = ifelse(is.na(LPS),FALSE,TRUE)) %>% 
  mutate(LPS = ifelse(is.na(LPS),"baseline", LPS)) %>% 
  select(IDPET,LPS,LPSpair)



  # filter(!is.na(LPS)) %>% 
  # group_by(PATIENTID) %>%
  # arrange(SERIESID, .by_group = TRUE) %>%
  # mutate(
  #   pair_id = (row_number() - 1) %/% 2 + 1,
  #   LPS = ifelse(count > 2, paste0(LPS, "_", pair_id), LPS)
  # ) %>%
  # select(-pair_id, -count) %>% 
  # ungroup() %>% 
  # select(IDPET, LPS)

simba_modeldat_new <- simba_modeldat %>% 
  left_join(LPS_cleaned) %>% 
  select(-PSTATE)

```



```{r}
saveRDS(simba_modeldat_new, "../DerivedData/Yale_simba_modeldata.rds")
```


```{r}
nested <- simba_modeldata %>% 
  group_by(genotype,DIAGNOSIS, PROTOCOL, Seriesdescription,SERIESID,Age, Sex,LPS,LPSpair,sub) %>%
  nest() %>% 
  ungroup()

nested %>% 
  group_by(PROTOCOL) %>%
  summarise(meanAGE= mean(Age),
            count = n(),
            n_HABs = sum(genotype == "HAB", na.rm = TRUE),
            n_male = sum(Sex=="M", na.rm = TRUE))
nest <- nested %>% 
  group_by(PROTOCOL, DIAGNOSIS) %>% 
  nest()
```



I decide to bind all of them together to make sure i do not analyse scans i do not have everything given.

# AIF analysis for each Protocol
## plot calc/fitted AIFs together

we want to calculate for each protocol at least one curve where we hopefully see the same to validate, using their data for the first 10 min, and then the own calculation

```{r}
table(alldata$PROTOCOL)
```



```{r}
set.seed(1234)


plot_data <- alldata %>% 
    mutate(aif_calc =map(aif_calc, ~.x %>%
                    rename(AIF = AIF_calc) %>%
                    select(Time,AIF))) %>%
    mutate(aif =map(aif, ~.x %>%
                    select(Time,AIF))) %>%
    mutate(aif_combined =map(aif_combined, ~.x %>%
                    select(Time,AIF))) 

for (i in unique(alldata$PROTOCOL)){
  plotdat <- plot_data %>% 
    filter(PROTOCOL==i)
  
  draw <- sample(length(plotdat$ID),1)
  #print(i)
  #print(draw)
  id <- plotdat$ID[[draw]]
  pet <- plotdat$PET[[draw]]
  # print(id)
  # print(pet)
  plot <- bind_rows(
      plotdat %>%
        filter(ID==id,PET==pet) %>%
        unnest(aif_calc) %>% mutate(source="calculated (PARENT*PLASMA)"),
      plotdat %>%
        filter(ID==id,PET==pet) %>%
        unnest(aif) %>% mutate(source="given"),
      plotdat %>%
        filter(ID==id,PET==pet) %>%
        unnest(aif_combined) %>% mutate(source="combined (calc after 3 min)")
    ) %>%
    ggplot(aes(x = Time, y = AIF, colour = source)) +
    geom_point() +
    geom_line() +
    coord_cartesian(xlim=c(0, 15)) +
    labs(title = paste0("AIFs for ID=", id, ", PET=", pet, ", Protocol=", i))
  
  plot(plot)
}
```

looking at these fits, we decided to use their AIF data for the first 10 minutes, and then we calculate the AIF=PLASMA*PARENT














































# ROI Sizes

```{r}
sum(is.na(tac$ROIsize))
sum(!is.na(tac$ROIsize))
testdata <- tac_new %>%
  filter(is.na(ROIsize))
table(testdata$Region)
```







```{r}
roisizes <- tac_dur_weights %>% 
  unnest(tac) %>%
  ungroup() %>%
  select(ID, PET, ANALYSISID, ROIsize, Region) %>% 
  arrange(ID)

naniar::vis_miss(roisizes)
```
This looks like the missing sizes are all within one individual.

```{r}
roisizes %>% 
  group_by(ID, PET) %>% 
  summarise(all_there = all(!is.na(ROIsize)))
```

Ok, so let's just use average ROI sizes.

```{r}
roisizes <- roisizes %>% 
  group_by(ID) %>% 
  mutate(missing = is.na(mean(ROIsize))) %>% 
  filter(!missing) %>% 
  select(-missing)

naniar::vis_miss(roisizes)

table(roisizes$ID, roisizes$Region)
```

Nice!

Now let's calculate regional means

```{r}
mean_roisizes <- roisizes %>% 
  group_by(Region) %>% 
  summarise(RegSize = mean(ROIsize)) %>% 
  mutate(logRegSize = log(RegSize),
         logRegSize_c = logRegSize - mean(logRegSize))

saveRDS(mean_roisizes, "../../DerivedData/Data2_mean_roisizes.rds")
```





<!-- # Just trying to understand the data -->

<!-- ## Bolus: Baseline + post-dose -->

<!-- ```{r} -->
<!-- demog %>%  -->
<!--   filter(ID=="RG189") -->

<!-- bol_b_p <- modeldat_nested %>%  -->
<!--   filter(ID == "RG189") -->


<!-- bol_b_p %>%  -->
<!--   select(ID, PET, State, tacs) %>%  -->
<!--   unnest(tacs) %>%  -->
<!--   select(ID, PET, State, t_tac, Frontal) %>%  -->
<!--   ggplot(aes(x=t_tac, y=Frontal, colour=State)) +  -->
<!--   geom_point() + -->
<!--   geom_line() -->
<!-- ``` -->



<!-- ## Bolus+infusion: Baseline + post-dose -->

<!-- ```{r} -->
<!-- demog %>%  -->
<!--   filter(ID=="SC392") -->

<!-- bolinf_b_p <- modeldat_nested %>%  -->
<!--   filter(ID == "SC392") -->


<!-- bolinf_b_p %>%  -->
<!--   select(ID, PET, State, tacs) %>%  -->
<!--   unnest(tacs) %>%  -->
<!--   select(ID, PET, State, t_tac, Frontal) %>%  -->
<!--   ggplot(aes(x=t_tac, y=Frontal, colour=State)) +  -->
<!--   geom_point() + -->
<!--   geom_line() -->
<!-- ``` -->


<!-- ## Bolus+infusion: Displacement + post-dose -->

<!-- ```{r} -->
<!-- demog %>%  -->
<!--   filter(ID=="SA746") -->

<!-- bolinf_d_p <- modeldat_nested %>%  -->
<!--   filter(ID == "SA746") -->


<!-- bolinf_d_p %>%  -->
<!--   select(ID, PET, State, tacs) %>%  -->
<!--   unnest(tacs) %>%  -->
<!--   select(ID, PET, State, t_tac, Frontal) %>%  -->
<!--   ggplot(aes(x=t_tac, y=Frontal, colour=State, group=PET)) +  -->
<!--   geom_point() + -->
<!--   geom_line() -->
<!-- ``` -->
